### 2020-03-25 main.tex
Added ICML style files.

%%%%%%%% ICML 2020 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

\documentclass{article}

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2020} with \usepackage[nohyperref]{icml2020} above.
\usepackage{hyperref}

% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Use the following line for the initial blind version submitted for review:
\usepackage{icml2020}

% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2020}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Submission and Formatting Instructions for ICML 2020}

\begin{document}

\twocolumn[
\icmltitle{TUD Datasets: A collection of benchmark datasets for learning with graphs}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2020
% package.

% List of affiliations: The first argument should be a (short)
% identifier you will use later to specify author affiliations
% Academic affiliations should list Department, University, City, Region, Country
% Industry affiliations should list Company, City, Region, Country

% You can specify symbols, otherwise they are numbered in order.
% Ideally, you should not use this facility. Affiliations will be numbered
% in order of appearance and this is the preferred way.
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Aeiau Zzzz}{equal,to}
\icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
\icmlauthor{Cieua Vvvvv}{goo}
\icmlauthor{Iaesut Saoeu}{ed}
\icmlauthor{Fiuea Rrrr}{to}
\end{icmlauthorlist}

\icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
\icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
\icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}

\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
\icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}

\icmlkeywords{Machine Learning, ICML}

\vskip 0.3in
]

% this must go after the closing bracket ] following \twocolumn[ ...

% This command actually creates the footnote in the first column
% listing the affiliations and the copyright notice.
% The command takes one argument, which is text to display at the start of the footnote.
% The \icmlEqualContribution command is standard text for equal contribution.
% Remove it (just {}) if you do not need this facility.

%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.

\begin{abstract}
This document provides a basic paper template and submission guidelines.
Abstracts must be a single paragraph, ideally between 4--6 sentences long.
Gross violations will trigger corrections at the camera-ready phase.
\end{abstract}

\section{Introduction}

\section*{Acknowledgements}
Thank all people you provided datasets. Especially Xavier and Benedek

\bibliography{bibliography}
\bibliographystyle{icml2020}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DELETE THIS PART. DO NOT PLACE CONTENT AFTER THE REFERENCES!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Do \emph{not} have an appendix here}

\end{document}

% This document was modified from the file originally made available by
% Pat Langley and Andrea Danyluk for ICML-2K. This version was created
% by Iain Murray in 2018, and modified by Alexandre Bouchard in
% 2019 and 2020. Previous contributors include Dan Roy, Lise Getoor and Tobias
% Scheffer, which was slightly modified from the 2010 version by
% Thorsten Joachims & Johannes Fuernkranz, slightly modified from the
% 2009 version by Kiri Wagstaff and Sam Roweis's 2008 version, which is
% slightly modified from Prasad Tadepalli's 2007 version which is a
% lightly changed version of the previous year's version by Andrew
% Moore, which was in turn edited from those of Kristian Kersting and
% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2020-03-25 main.tex
MC.

@@
 
-% Recommended, but optional, packages for figures and better typesetting:
-\usepackage{microtype}
 \usepackage{graphicx}
 \usepackage{subfigure}
-\usepackage{booktabs} % for professional tables
-
-% hyperref makes hyperlinks in the resulting PDF.
-% If your build breaks (sometimes temporarily if a hyperlink spans a page)
-% please comment out the following usepackage line and replace
-% \usepackage{icml2020} with \usepackage[nohyperref]{icml2020} above.
+\usepackage{booktabs}
 \usepackage{hyperref}
-
-% Attempt to make hyperref and algorithmic work together better:
 \newcommand{\theHalgorithm}{\arabic{algorithm}}
 
-% Use the following line for the initial blind version submitted for review:
+\usepackage{booktabs}
+\usepackage{url}
+\usepackage{todonotes}
+\usepackage{multirow}
+\usepackage{tikz}
+
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsthm}
+\usepackage{amsfonts}
+\usepackage{thmtools}		
+\usepackage{mleftright}
+
+\theoremstyle{definition}
+\newtheorem{theorem}{Theorem}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{example}[theorem]{Example}
+\newtheorem{observation}[theorem]{Observation}
+\newtheorem{remark}[theorem]{Remark}
+
+\usepackage{thm-restate}
+\usepackage[mathic=true]{mathtools}
+\usepackage{fixmath}
+\usepackage{siunitx}
+
+\usepackage{pifont}
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}%
+
+\usepackage{enumitem}
+\setlist[enumerate]{noitemsep, topsep=0.5\topsep}
+\setlist[description]{noitemsep, topsep=0.5\topsep}
+\setlist[itemize]{noitemsep, topsep=0.5\topsep}
+
+\usepackage{enumitem}
+\setlist[enumerate]{noitemsep, topsep=0.5\topsep}
+\setlist[description]{noitemsep, topsep=0.5\topsep}
+\setlist[itemize]{noitemsep, topsep=0.5\topsep}
+
+\usepackage{setspace}
+\usepackage[protrusion=true,expansion=false, activate={true,nocompatibility},final,kerning=true,spacing=true]{microtype}
+
+\usepackage{ellipsis}
+\usepackage{xspace}
+\usepackage{hfoldsty}
+
+\usepackage{ifthen}
+\newcommand{\CC}[1][]{$\text{C\hspace{-.25ex}}^{_{_{_{++}}}}
+	\ifthenelse{\equal{#1}{}}{}{\text{\hspace{-.625ex}#1}}$}
+
+\newcommand{\win}[1]{$\hspace{-0.3mm}$\textbf{#1}}
+\newcommand{\sd}[1]{\scriptsize{$\pm$#1}}
+
+% Let cleveref and thmtools work together
+\makeatletter
+\def\thmt@refnamewithcomma #1#2#3,#4,#5\@nil{%
+	\@xa\def\csname\thmt@envname #1utorefname\endcsname{#3}%
+	\ifcsname #2refname\endcsname
+	\csname #2refname\expandafter\endcsname\expandafter{\thmt@envname}{#3}{#4}%
+	\fi
+}
+\makeatother
+\usepackage[capitalise,noabbrev]{cleveref}
+
+\newcommand{\new}[1]{\emph{#1}}
+\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
+\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
+
+\newcommand{\cA}{\ensuremath{{\mathcal A}}\xspace}
+\newcommand{\cB}{\ensuremath{{\mathcal B}}\xspace}
+\newcommand{\cC}{\ensuremath{{\mathcal C}}\xspace}
+\newcommand{\cD}{\ensuremath{{\mathcal D}}\xspace}
+\newcommand{\cF}{\ensuremath{{\mathcal F}}\xspace}
+\newcommand{\cH}{\ensuremath{{\mathcal H}}\xspace}
+\newcommand{\cN}{\ensuremath{{\mathcal N}}\xspace}
+\newcommand{\cO}{\ensuremath{{\mathcal O}}\xspace}
+\newcommand{\cP}{\ensuremath{{\mathcal P}}\xspace}
+\newcommand{\cR}{\ensuremath{{\mathcal R}}\xspace}
+\newcommand{\cS}{\ensuremath{{\mathcal S}}\xspace}
+\newcommand{\cU}{\ensuremath{{\mathcal U}}\xspace}
+\newcommand{\cV}{\ensuremath{{\mathcal V}}\xspace}
+\newcommand{\cPn}{\ensuremath{{\mathcal P}_n}\xspace}
+
+\newcommand{\fA}{\ensuremath{\mathfrak{A}}\xspace}
+\newcommand{\fB}{\ensuremath{\mathfrak{B}}\xspace}
+\newcommand{\fC}{\ensuremath{\mathfrak{C}}\xspace}
+
+\newcommand{\fa}{\ensuremath{\mathfrak{a}}\xspace}
+\newcommand{\fb}{\ensuremath{\mathfrak{b}}\xspace}
+\newcommand{\fc}{\ensuremath{\mathfrak{c}}\xspace}
+\newcommand{\fd}{\ensuremath{\mathfrak{d}}\xspace}
+
+\newcommand{\bA}{\ensuremath{{\bf A}}\xspace}
+\newcommand{\bB}{\ensuremath{{\bf B}}\xspace}
+\newcommand{\bK}{\ensuremath{{\bf K}}\xspace}
+\newcommand{\bE}{\ensuremath{{\bf E}}\xspace}
+\newcommand{\bN}{\ensuremath{{\bf N}}\xspace}
+\newcommand{\bG}{\ensuremath{{\bf G}}\xspace}
+
+\newcommand{\ba}{\ensuremath{{\bf a}}\xspace}
+\newcommand{\bb}{\ensuremath{{\bf b}}\xspace}
+\newcommand{\bc}{\ensuremath{{\bf c}}\xspace}
+
+\newcommand{\bbE}{\ensuremath{\mathbb{E}}}
+\newcommand{\bbR}{\ensuremath{\mathbb{R}}}
+\newcommand{\bbQ}{\ensuremath{\mathbb{Q}}}
+\newcommand{\bbP}{\ensuremath{\mathbb{P}}}
+\newcommand{\bbZ}{\ensuremath{\mathbb{Z}}}
+\newcommand{\bbN}{\ensuremath{\mathbb{N}}}
+\newcommand{\bbNn}{\ensuremath{\mathbb{N}_0}}
+
+\newcommand{\bbRnp}{\ensuremath{\bbR_{\geq 0}}}
+\newcommand{\bbQnp}{\ensuremath{\bbQ_{\geq}}}
+\newcommand{\bbZnp}{\ensuremath{\bbZ_{\geq}}}
+
+\newcommand{\bbRsp}{\ensuremath{\bbR_>}}
+\newcommand{\bbQsp}{\ensuremath{\bbQ_>}}
+\newcommand{\bbZsp}{\ensuremath{\bbZ_>}}
+
+\newcommand{\cp}{\textsf{P}\xspace}
+\newcommand{\cnp}{\textsf{NP}\xspace}
+
+\newcommand{\RR}{\mathbb{R}}
+\newcommand{\QQ}{\mathbb{Q}}
+\newcommand{\PP}{\mathbb{P}}
+\newcommand{\ZZ}{\mathbb{Z}}
+\newcommand{\EE}{\mathbb{E}}
+\newcommand{\NN}{\mathbb{N}}
+\newcommand{\GG}{\mathbb{G}}
+\newcommand{\GN}{\mathbb{G}_n}
+\newcommand{\rb}{\right\}\xspace}
+\newcommand{\lb}{\left\{\xspace}
+\newcommand{\lbr}{\left(\xspace} 
+\newcommand{\rbr}{\right)\xspace}
+\newcommand{\ndelta}{\ensuremath{\overline{\delta}}}
+\newcommand{\oms}{\{\!\!\{}
+\newcommand{\cms}{\}\!\!\}}
+\newcommand{\trans}{^T}
+\renewcommand{\vec}[1]{\mathbf{#1}}
+
 \usepackage{icml2020}
 
-% If accepted, instead use the following line for the camera-ready submission:
-%\usepackage[accepted]{icml2020}
-
-% The \icmltitle you define below is probably too long as a header.
-% Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Submission and Formatting Instructions for ICML 2020}
+\icmltitlerunning{TUD Datasets}
 
@@
 \icmltitle{TUD Datasets: A collection of benchmark datasets for learning with graphs}
-
-% It is OKAY to include author information, even for blind
-% submissions: the style file will automatically remove it for you
-% unless you've provided the [accepted] option to the icml2020
-% package.
-
-% List of affiliations: The first argument should be a (short)
-% identifier you will use later to specify author affiliations
-% Academic affiliations should list Department, University, City, Region, Country
-% Industry affiliations should list Company, City, Region, Country
-
-% You can specify symbols, otherwise they are numbered in order.
-% Ideally, you should not use this facility. Affiliations will be numbered
-% in order of appearance and this is the preferred way.
 \icmlsetsymbol{equal}{*}
@@
 \begin{icmlauthorlist}
-\icmlauthor{Aeiau Zzzz}{equal,to}
-\icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
-\icmlauthor{Cieua Vvvvv}{goo}
-\icmlauthor{Iaesut Saoeu}{ed}
-\icmlauthor{Fiuea Rrrr}{to}
+\icmlauthor{C. Morris}{p}
+\icmlauthor{N.\,M.\,Kriege}{vie}
+\icmlauthor{K. Kersting}{darm}
+\icmlauthor{P. Mutzw}{bonn}
+\icmlauthor{N. Neumann}{wustl}
 \end{icmlauthorlist}
 
-\icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
-\icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
-\icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}
-
-\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
-\icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}
+\icmlaffiliation{p}{CERC in Data Science for Real-Time Decision-Making, Polytechnique Montréal}
+\icmlaffiliation{vie}{University of Vienna}
+\icmlaffiliation{darm}{Machine Learning Group, TU Darmstadt}
+\icmlaffiliation{bonn}{Department of Computer Science, University of Bonn}
+\icmlaffiliation{wustl}{Washington University in St. Louis}
+\icmlcorrespondingauthor{Christopher Morris}{christopher.morris@tu-dortmund.de}
 
@@
 
-% this must go after the closing bracket ] following \twocolumn[ ...
-
-% This command actually creates the footnote in the first column
-% listing the affiliations and the copyright notice.
-% The command takes one argument, which is text to display at the start of the footnote.
-% The \icmlEqualContribution command is standard text for equal contribution.
-% Remove it (just {}) if you do not need this facility.
-
-%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
-\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.
+\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
+%\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.
 
 \begin{abstract}
-This document provides a basic paper template and submission guidelines.
-Abstracts must be a single paragraph, ideally between 4--6 sentences long.
-Gross violations will trigger corrections at the camera-ready phase.
+Recently, there has been an increasing interest in learning with graph data, especially in graph neural networks.
+However, the development of meaningful benchmark datasets and standarized evaluation prodecures are lagging behind.
+That is, most paper papers evaluate their methods on small-scale datasets leading to high standard deviations and coseuqntly hindering advancements in this area.
+To adress this, we intodruce the \textsc{Tud benchmark dataset} for graph classification and regression.
+The dataset consists of over 150 datasets from a wide range of applications and variying size.
+We provide Python based data loaders, baseline implementations, and evaluation tools.
+Here, we give an overview of the datasets, the evalution tools, and provide baseline experiments.
 \end{abstract}
@@
 
-\section*{Acknowledgements}
-Thank all people you provided datasets. Especially Xavier and Benedek
+Graph-structured data is ubiquitous across application domains ranging from chemo- and bioinformatics to image and social network analysis.
+To develop successful machine learning models in these domains, we need techniques that can exploit the rich information inherent in the graph structure, as well as the feature information contained within nodes and edges.
+In recent years, numerous approaches have been proposed for machine learning with graphs---most notably, approaches based on graph \new{kernels}~\cite{Kri+2019} or using \new{graph neural networks} (GNNs)~\cite{Ham+2017a,Gil+2017}.
+However, most papers, even recent ones, evaluate newly proposed architectures or methods on a fixed set of small-scale benchmark datasets leading to high standard deviations and hard to interpret results.
+
+Here, we give an overview \new{TUD benchn} The bencharmk consists of over 150 datasets from a wide range of domains and can be accessed via mark dataset for supervised learning with graphs, i.e., classificiation and regression.
+All datasets can convientlly be downloaded from \url{graphlearning.io}, and easily be accessed form popoluar graph learning frameworks such as Pytorch Geoeotric~\cite{Fey+2019} and DGL~\cite{Wan+2019}.
+
+\paragraph{Related work.}
+
+Give short over view of GNNs and other benchmarks and expermental studies.
+
+\paragraph{Contributions/}
+
+\section{Overview of the datasets}
+
+\section{Installation, usage, and evaluation tools}
+
+\section{Experimental evaluation}
+
+\subsection{Experimental protocol}
+
+\section{Conclusion}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% DELETE THIS PART. DO NOT PLACE CONTENT AFTER THE REFERENCES!
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \appendix
-\section{Do \emph{not} have an appendix here}
 

### 2020-03-25 main.tex
MC.

@@
 \begin{abstract}
-Recently, there has been an increasing interest in learning with graph data, especially in graph neural networks.
-However, the development of meaningful benchmark datasets and standarized evaluation prodecures are lagging behind.
-That is, most paper papers evaluate their methods on small-scale datasets leading to high standard deviations and coseuqntly hindering advancements in this area.
-To adress this, we intodruce the \textsc{Tud benchmark dataset} for graph classification and regression.
-The dataset consists of over 150 datasets from a wide range of applications and variying size.
-We provide Python based data loaders, baseline implementations, and evaluation tools.
-Here, we give an overview of the datasets, the evalution tools, and provide baseline experiments.
+Recently, there has been an increasing interest in learning with graph data, especially using graph neural networks.
+However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging behind.
+That is, most paper papers evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area.
+To address this, we introduce the \textsc{Tud benchmark dataset} for graph classification and regression.
+The dataset consists of over 150 datasets from a wide range of applications and varying sizes.
+We provide Python-based data loaders, baseline implementations, and evaluation tools.
+Here, we give an overview of the datasets, evaluation tools, and provide baseline experiments.
 \end{abstract}

### 2020-03-25 main.tex
MC.

@@
 That is, most paper papers evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area.
-To address this, we introduce the \textsc{Tud benchmark dataset} for graph classification and regression.
+To address this, we introduce the \textsc{Tud dataset} for graph classification and regression.
 The dataset consists of over 150 datasets from a wide range of applications and varying sizes.
@@
 To develop successful machine learning models in these domains, we need techniques that can exploit the rich information inherent in the graph structure, as well as the feature information contained within nodes and edges.
-In recent years, numerous approaches have been proposed for machine learning with graphs---most notably, approaches based on graph \new{kernels}~\cite{Kri+2019} or using \new{graph neural networks} (GNNs)~\cite{Ham+2017a,Gil+2017}.
+In recent years, numerous approaches have been proposed for machine learning with graphs---most notably, approaches based on graph \new{kernels}~\cite{Kri+2019} or using \new{graph neural networks} (GNNs)~\cite{Gil+2017}.
 However, most papers, even recent ones, evaluate newly proposed architectures or methods on a fixed set of small-scale benchmark datasets leading to high standard deviations and hard to interpret results.
 
-Here, we give an overview \new{TUD benchn} The bencharmk consists of over 150 datasets from a wide range of domains and can be accessed via mark dataset for supervised learning with graphs, i.e., classificiation and regression.
-All datasets can convientlly be downloaded from \url{graphlearning.io}, and easily be accessed form popoluar graph learning frameworks such as Pytorch Geoeotric~\cite{Fey+2019} and DGL~\cite{Wan+2019}.
+Here, we give an overview of \new{Tud datasets}.
+The benchmark collection consists of over 150 datasets from a wide range of domains for supervised learning with graphs, i.e., classificiation and regression.
+All datasets are provided in a common dataset format at \url{graphlearning.io}, and easily be accessed from popular graph learning frameworks such as \emph{Pytorch Geometric}~\cite{Fey+2019} and \emph{DGL}~\cite{Wan+2019}.
 
@@
 
+There exists two approaches to supervised learing with graphs, graph kernels and graph neural networks (GNNs).
+Graph kernels have been studied extensively in the past 15 years, see ~\cite{Kri+2019} for a thorough overview.
+Important approaches include random-walk and shortest paths based kernels~\cite{Gaertner2003,Sugiyama2015,Bor+2005,Kri+2017b}, as well as the Weisfeiler-Lehman subtree kernel~\cite{She+2011,Mor+2017}.
+Further recent works focus on assignment-based approaches~\cite{Kri+2016,Nik+2017}, spectral approaches~\cite{Kon+2016}, and graph decomposition approaches~\cite{Nik+2018}.
+
+Recently, GNNs~\cite{Gil+2017} emerged as a alternative to graph kernels.
+Notable instances of this model include~\cite{Duv+2015},~\cite{Li+2016},~\cite{Ham+2017} and the spectral approaches proposed in~\cite{Bru+2014,Def+2015,Kip+2017}---all of which descend from early work in~\cite{Kir+1995,Mer+2005,Sca+2009}.
+A unifying message passing architecture can be found in~\cite{Gil+2017}.
+Two recent surveys~\cite{wu2019comprehensive,zhou2018graph} provide a thorough overview of graph neural networks
+
 Give short over view of GNNs and other benchmarks and expermental studies.
 
-\paragraph{Contributions/}
+\paragraph{Contributions} We give an overivew of
 

### 2020-03-26 main.tex
MC.

@@
 
-Give short over view of GNNs and other benchmarks and expermental studies.
+The papers~\cite{Fey+2019,Err+2019,Dwi+2020} evalute GNNs using a unified evaluation procedure, however, both only use small scale datasets.
+Recently, \url{ogb.stanford.edu} launchend, however the provided datasets for graph classification focus on chemistry applications.
 
-\paragraph{Contributions} We give an overivew of
+\paragraph{Contributions} We give an overivew of \textsc{Tud dataset}.
 

### 2020-03-26 main.tex
MC.

@@
 
-\paragraph{Contributions} We give an overivew of \textsc{Tud dataset}.
+\paragraph{Contributions} We give an overview of \textsc{Tud dataset}, its unified evalution procudures, and baseline methods.
+Moreover, we report results on a experimental study comparing graph kernels and GNNs on a subset of the \textsc{Tud dataset}.
 

### 2020-03-26 main.tex
MC.

@@
 The papers~\cite{Fey+2019,Err+2019,Dwi+2020} evalute GNNs using a unified evaluation procedure, however, both only use small scale datasets.
-Recently, \url{ogb.stanford.edu} launchend, however the provided datasets for graph classification focus on chemistry applications.
+Recently, \url{ogb.stanford.edu} launchend, however the provided datasets for graph classification focus on chemistry applications, and the number is quite limited at this point.
 
@@
 \section{Overview of the datasets}
+
+The \textsc{Tud dataset} contain over 150 datasets provided at \url{graphlearning.io}.
 

### 2020-03-26 main.tex
MC.

@@
 
+The data loader, baseline method, experimental evaluation tool can be installed by running \texttt{pip install tud-datasets}, see
+
+\subsection{Eva}
+
 \section{Experimental evaluation}
@@
 \section{Conclusion}
+
+We gave an overview of the \textsc{Tud dataset}, and reported on the results of an experimental study comparing graph kernels and GNNs on a subset of the data.
+We believe that our dataset collection will spark further progress in the area of graph represention learning.
+We are looking forward to adding more dataset to our collection, and are excited about contributions from the community, and reseachers and practitionors from other areas.
+
+\section{Acknowledgement}
+
+We thank everybody who provided datasets for \textsc{Tud dataset}.
 
@@
 \end{document}
-
-% This document was modified from the file originally made available by
-% Pat Langley and Andrea Danyluk for ICML-2K. This version was created
-% by Iain Murray in 2018, and modified by Alexandre Bouchard in
-% 2019 and 2020. Previous contributors include Dan Roy, Lise Getoor and Tobias
-% Scheffer, which was slightly modified from the 2010 version by
-% Thorsten Joachims & Johannes Fuernkranz, slightly modified from the
-% 2009 version by Kiri Wagstaff and Sam Roweis's 2008 version, which is
-% slightly modified from Prasad Tadepalli's 2007 version which is a
-% lightly changed version of the previous year's version by Andrew
-% Moore, which was in turn edited from those of Kristian Kersting and
-% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2020-03-26 main.tex
MC.

@@
 
+\usepackage{ifthen}
+\newcommand{\CPP}[1][]{$\text{C\hspace{-.25ex}}^{_{_{_{++}}}}
+	\ifthenelse{\equal{#1}{}}{}{\text{\hspace{-.625ex}#1}}$}
+
 \usepackage{icml2020}
@@
 
-\section{Installation, usage, and evaluation tools}
+\section{Installation, baseline, and evaluation tools}
 
-The data loader, baseline method, experimental evaluation tool can be installed by running \texttt{pip install tud-datasets}, see
+The data loader, baseline methods, experimental evaluation tool can be installed by running \texttt{pip install tud-datasets}, see \url{XXX} for further details.
 
-\subsection{Eva}
+\subsection{Baselines}
+
+In order to provide meaningful baselines, we provide implementation of common graph kernels was well as GNNs baselines.
+We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{Shervashidze2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel, as well as the higher-order WL kernels~\cite{Mor+2019b}, in \CPP and made them accessable through the Python interface of \textsc{Tud dataset}, see \url{XXX} for further details.
+Moreover, all GNN architectures implemented in PyTorch Geometric can be used as baseline as well.
+
+Vertex kernel and edge kernel?
+
+\subsection{Evaluation tools}
+
+In order to insure a fair and meaningful comparision between methods, we propose the following evaulation and software for kernels and GNN approaches.
+Al proposed can the conviently accessed from the Python interface, see \url{XXX} for further details.
+First, for kernels we propose the established $C$-SVM implementation \textsc{LibSvm}~\cite{Cha+11} for kernels that compute a Gram matrix, and the linear $C$-SVM implementation \textsc{LibLinear}~\cite{Fan+2008} for kernels can be computed based on explicit feature maps.
+We optimize GNNs end-to-end using \textsc{Adam}~\cite{}.
+Too compute accuracies and other metrics for evaluation, we propose to use $10$-fold cross validation, where for each training fold we select a validation uniformly at random ($10\%$ of the training fold) to select hyperparamets, e.g., number of iterations, $C$ parameter, number of layers, learning rate, feature dimension.
 

### 2020-03-26 main.tex
MC.

@@
 
-In order to insure a fair and meaningful comparision between methods, we propose the following evaulation and software for kernels and GNN approaches.
-Al proposed can the conviently accessed from the Python interface, see \url{XXX} for further details.
-First, for kernels we propose the established $C$-SVM implementation \textsc{LibSvm}~\cite{Cha+11} for kernels that compute a Gram matrix, and the linear $C$-SVM implementation \textsc{LibLinear}~\cite{Fan+2008} for kernels can be computed based on explicit feature maps.
+In order to insure a fair and meaningful comparision between methods, we propose the following evaluation proceudres, and software tools for kernels and GNN approaches.
+All proposed methods can be conviently accessed from the Python interface, see \url{XXX} for further details.
+First, for kernels we propose the established $C$-SVM implementation \textsc{LibSvm}~\cite{Cha+11} for kernels that compute a Gram matrix, and the linear $C$-SVM implementation \textsc{LibLinear}~\cite{Fan+2008} for kernels  that can be computed based on explicit feature maps.
 We optimize GNNs end-to-end using \textsc{Adam}~\cite{}.
-Too compute accuracies and other metrics for evaluation, we propose to use $10$-fold cross validation, where for each training fold we select a validation uniformly at random ($10\%$ of the training fold) to select hyperparamets, e.g., number of iterations, $C$ parameter, number of layers, learning rate, feature dimension.
+Too compute accuracies and other metrics for evaluation, we propose to use $10$-fold cross validation, where we select a validation set uniformly at random from each training fold ($10\%$ of the training fold), to select hyperparamets, e.g., number of iterations, $C$ parameter, number of layers, learning rate, feature dimension, etc.
 

### 2020-03-26 main.tex
MC.

@@
 
-\subsection{Evaluation tools}
+\subsection{Evaluation tools}\label{eval}
 
@@
 
+Our intention here is to investigate the benefits XXXX. More precisely, we address the following questions:
+\begin{description}
+	\item[Q1] dfgkposdk
+	\item[Q2] dfdsfsdd
+	\item[Q3] sdfsdfsdfsdfdssdf
+\end{description}
+
 \subsection{Experimental protocol}
+
+Describe kernel, gnns used
+
+\paragraph{Datasets.}
+
+\paragraph{Graph kernels.}
+
+\paragraph{GNNs.}
+
+We used the evaluation procedute described in~\cref{eval}, describe used hyperparamter
+
+\subsection{Results and discussion}
+
+\begin{table*}[t]\centering		
+	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
+	\label{t2l}	
+	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
+		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule
+
+			& \multirow{3}{*}{\vspace*{4pt}\textbf{Graph Kernel}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
+			& & {\textsc{Data0}}         &  {\textsc{Data1}}      & {\textsc{Data1}}           & {\textsc{Data1}}       & {\textsc{Data1}}           & {\textsc{Data1}}      \\	\toprule
+			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
+				& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
+				& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
+				& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
+			\cmidrule{2-8}	
+			\multirow{4}{*}{\rotatebox{90}{GNN}}	& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
+		& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
+		& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
+		& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
+			\bottomrule
+	\end{tabular}}
+\end{table*}
 

### 2020-03-26 main.tex
MC.

@@
 
-Here, we give an overview of \new{Tud datasets}.
+Here, we give an overview of \textsc{Tud datasets}.
 The benchmark collection consists of over 150 datasets from a wide range of domains for supervised learning with graphs, i.e., classificiation and regression.
@@
 The \textsc{Tud dataset} contain over 150 datasets provided at \url{graphlearning.io}.
-
-\section{Installation, baseline, and evaluation tools}
-
 The data loader, baseline methods, experimental evaluation tool can be installed by running \texttt{pip install tud-datasets}, see \url{XXX} for further details.
@@
 
+Repeat ten times?
+
 \section{Experimental evaluation}
 
-Our intention here is to investigate the benefits XXXX. More precisely, we address the following questions:
+Our intention here is to provide baseline experiments, and compare graph kernels and GNNs. More precisely, we address the following questions:
 \begin{description}
-	\item[Q1] dfgkposdk
-	\item[Q2] dfdsfsdd
-	\item[Q3] sdfsdfsdfsdfdssdf
+	\item[Q1] Are GNNs superior to graph kernels? Is there a single method that dominates?
+	\item[Q2] ?
+	\item[Q3] ?
 \end{description}
@@
 
-Describe kernel, gnns used
+We used the following datasets, graph kernels, and GNN baselines.
 
-\paragraph{Datasets.}
+\paragraph{Datasets.} We used the \textsc{deezer\_ego\_nets}, \textsc{github\_stargazers}, \textsc{Enymes},
+\textsc{Imdb-BINARY}, \textsc{Imdb-MULTI}, \textsc{Mcf-7}, \textsc{Molt-4},	\textsc{Nci1}, \textsc{Proteins},
+\textsc{Reddit-Binary},	\textsc{reddit\_threads}, \textsc{twitch\_egos}, \textsc{Uacc257}. See the appendix for dataset statistics.
 
-\paragraph{Graph kernels.}
+\paragraph{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree}~\cite{Shervashidze2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} \textsc{WL-OA}~\cite{Kri+2016}, and $\delta$-$2$-LWL$^+$ kernel~\cite{Mor+2019b} included in the \textsc{TUD Dataset} package.
+The $C$-parameter was selected from $\{10^{-3}, 10^{-2}, \dotsc, 10^{2},$ $10^{3}\}$ from the validation set.
+For the larger datasets, we computed sparse feature vectors for each graph and used the linear $C$-SVM implementation of \text{Liblinear}~\cite{Fan+2008}.
+The number of iterations of the \textsc{$1$-WL}, \textsc{WL-OA}, and the  $\delta$-$2$-LWL$^+$ were selected from $\{0,\dotsc,5\}$.\footnote{As already shown in~\cite{She+2011}, choosing the number of iterations too large will lead to overfitting.}
 
-\paragraph{GNNs.}
+\paragraph{GNNs.} We used the GNN architectures \textsc{GCN}~\cite{Kip+2017}, \textsc{Sage}~\cite{Ham+2017}, \textsc{Gin} and \textsc{Gin-$\varepsilon$}~\cite{Xu+2018b} as neural baselines.
+For all experiments, we used the global mean operator to obtain graph-level outputs.
+For each dataset, we optimize the number of hidden units from $
+\{16, 32, 64, 128\}$, the number of layers from $ \{2, 3, 4, 5\}$ and the learning rate from $ \{0.0001, 0.001, 0.01 \}$ with respect to the validation set. The batch size was fixed to $128$.
 
-We used the evaluation procedute described in~\cref{eval}, describe used hyperparamter
+For both methods, we used the evaluation procecude described in~\cref{eval} to optimize hyperparameters and compute accuracies.
+All experiments can be fulled reprodcued from the scripts provided at \url{XXX}.
 
 \subsection{Results and discussion}
+See~\cref{t2l}.
 
@@
 	\label{t2l}	
-	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
+	\resizebox{0.6\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
 		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule

### 2020-04-04 main.tex
started text on datasets; added some comments

@@
 
+\newcommand{\nk}[1]{{{\textcolor{brown}{\textbf{[NK:} {#1}\textbf{]}}}}}
+
 \usepackage{ifthen}
@@
 Here, we give an overview of the datasets, evaluation tools, and provide baseline experiments.
+\nk{Make clear that these are datasets collected from the authors of various papers}
 \end{abstract}
@@
 The benchmark collection consists of over 150 datasets from a wide range of domains for supervised learning with graphs, i.e., classificiation and regression.
-All datasets are provided in a common dataset format at \url{graphlearning.io}, and easily be accessed from popular graph learning frameworks such as \emph{Pytorch Geometric}~\cite{Fey+2019} and \emph{DGL}~\cite{Wan+2019}.
+All datasets are provided in a common dataset format at \url{graphlearning.io}, and can easily be accessed from popular graph learning frameworks such as \emph{Pytorch Geometric}~\cite{Fey+2019} and \emph{DGL}~\cite{Wan+2019}.
 
@@
 
+\subsection{Datasets}
+
+Our collection of datasets covers graphs from various domains, which were provided by different authors.
+Therefore, they differ regarding the used graph model even within the same domain and the provided annotations, e.g., discrete or continuous node/edge attributes.
+We give an overview of some representative domains and graph models.
+
+\paragraph{Small molecules.} 
+A commonly used class of graph datasets are derived from small molecules with class labels representing, e.g., toxicity or biological activity determined in the context of drug discovery.
+A molecule is represented by a graph in which vertices take the places of atoms and edges that of chemical bonds.
+Consequently, the labels indicate atom and bond types, where additional chemical attributes are possible.
+The graph models differs, e.g., in whether hydrogen atoms represented explicitly by vertices and bonds in aromatic rings are annotated accordingly.
+Our collection contains small datasets commonly used in the early graph kernel literature such as \textsc{Mutag}~\citep{Deb+1991} and \textsc{Ptc}~\cite{Helma2001}, medium-sized datasets, e.g., \textsc{Nci1} and \textsc{Nci109}~\citep{Wal+2008,She+2011}, as well as several large datasets derived from the \emph{Tox21 Challenge 2014} or \emph{PubChem}~\citep{Kim2018}.
+For some classification tasks, the geometrical arrangement of atoms has been determined and should be taken into account in a rotation-invariant manner.
+In order to achieve this, complete graphs with edges annotated by distances are commonly used~\citep{Kri+2012,Gil+2017}.
+Our collection contains the four datasets \textsc{BZR}, \textsc{COX2}, \textsc{DHFR}, \textsc{ER} initially published by \citet{Sut+2003} in two versions, with 3d coordinates of atoms and inter-atom distances, respectively, cf.~\citep{Mah+2006,Kri+2012}.
+
+\paragraph{Bioinformatics.}
+
+\paragraph{Computer vision.}
+Graph-based methods are widely used in computer vision for various tasks using diverse graph models.
+Our collection provides several datasets originating from the \emph{IAM Graph Database}~\citep{Riesen2008} such as \textsc{Letter} and \textsc{Fingerprint}.
+Other datasets represent \textsc{Cuneiform} signs~\citep{Kriege2018}, 3d point clouds for robot grasping tasks (\textsc{FirstMM\_DB}) and semantic image processing (\textsc{MSRC})~\citep{Neu+2016}.
+
+\paragraph{Social networks.}
+Several of the provided datasets are derived from social networks
+TODO
+
+Recently, temporal graphs were considered, where edges represent the contact or interaction between two individuals at a certain point in time.
+Such graphs are of interest when studying dissemination processes such as epidemics, information and fake news.
+We provide temporal graph classification datasets derived from \textsc{Tumblr}, \textsc{Dblp} and \textsc{Facebook} as well as contacts in a \textsc{Highschool} and at the \textsc{Infectious} exhibition~\citep{Oettershagen2019}.
+
 \subsection{Baselines}
@@
 In order to provide meaningful baselines, we provide implementation of common graph kernels was well as GNNs baselines.
-We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{Shervashidze2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel, as well as the higher-order WL kernels~\cite{Mor+2019b}, in \CPP and made them accessable through the Python interface of \textsc{Tud dataset}, see \url{XXX} for further details.
+We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{Shervashidze2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} \nk{Das ist eine Variante mit Labeln und 3 Knoten oder?}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel, as well as the higher-order WL kernels~\cite{Mor+2019b}, in \CPP and made them accessable through the Python interface of \textsc{Tud dataset}, see \url{XXX} for further details.
 Moreover, all GNN architectures implemented in PyTorch Geometric can be used as baseline as well.
 
-Vertex kernel and edge kernel?
+Vertex kernel and edge kernel? \nk{Wäre interessant!}
 
@@
 For both methods, we used the evaluation procecude described in~\cref{eval} to optimize hyperparameters and compute accuracies.
-All experiments can be fulled reprodcued from the scripts provided at \url{XXX}.
+All experiments can be reproduced using the scripts provided at \url{XXX}.
 

### 2020-04-06 main.tex
description of datasets

@@
 To address this, we introduce the \textsc{Tud dataset} for graph classification and regression.
-The dataset consists of over 150 datasets from a wide range of applications and varying sizes.
+The dataset consists of over 150 \nk{Zur Zeit sind es 128.
+Mehr als 100 klingt auch gut oder?} datasets from a wide range of applications and varying sizes.
 We provide Python-based data loaders, baseline implementations, and evaluation tools.
@@
 A commonly used class of graph datasets are derived from small molecules with class labels representing, e.g., toxicity or biological activity determined in the context of drug discovery.
-A molecule is represented by a graph in which vertices take the places of atoms and edges that of chemical bonds.
+A molecule is represented by a graph in which nodes take the places of atoms and edges that of chemical bonds.
 Consequently, the labels indicate atom and bond types, where additional chemical attributes are possible.
-The graph models differs, e.g., in whether hydrogen atoms represented explicitly by vertices and bonds in aromatic rings are annotated accordingly.
+The graph models differs, e.g., in whether hydrogen atoms represented explicitly by nodes and bonds in aromatic rings are annotated accordingly.
 Our collection contains small datasets commonly used in the early graph kernel literature such as \textsc{Mutag}~\citep{Deb+1991} and \textsc{Ptc}~\cite{Helma2001}, medium-sized datasets, e.g., \textsc{Nci1} and \textsc{Nci109}~\citep{Wal+2008,She+2011}, as well as several large datasets derived from the \emph{Tox21 Challenge 2014} or \emph{PubChem}~\citep{Kim2018}.
-For some classification tasks, the geometrical arrangement of atoms has been determined and should be taken into account in a rotation-invariant manner.
+This includes the 11 datasets from anticancer screen tests with different cancer cell lines used by \citet{Yan2008} to demonstrate the efficacy of classifiers based on significant graph patterns.
+These datasets, the largest of which contain more than 79k graphs, are typically not balanced and contain far more small molecules that are identified as inactive against cancer cells.
+The \textsc{Alchemy} was proposed by~\citet{Chen2019a} for benchmarking {AI} models.
+
+For some cheminformatics prediction tasks, the geometrical arrangement of atoms has been determined and should be taken into account in a rotation-invariant manner.
 In order to achieve this, complete graphs with edges annotated by distances are commonly used~\citep{Kri+2012,Gil+2017}.
-Our collection contains the four datasets \textsc{BZR}, \textsc{COX2}, \textsc{DHFR}, \textsc{ER} initially published by \citet{Sut+2003} in two versions, with 3d coordinates of atoms and inter-atom distances, respectively, cf.~\citep{Mah+2006,Kri+2012}.
+Our collection contains the four datasets \textsc{Bzr}, \textsc{Cox2}, \textsc{Dhfr}, \textsc{Er} initially published by \citet{Sut+2003} in two versions, with 3d coordinates of atoms and inter-atom distances, respectively, cf.~\citep{Mah+2006,Kri+2012}.
 
 \paragraph{Bioinformatics.}
+The datasets \textsc{DD}, \textsc{Enzymes} and \textsc{Proteins} represent macromolecules.
+\citet{Bor+2005a} introduced a graph model for proteins, where nodes represent secondary structure elements and are annotated by their type, i.e., helix, sheet or turn, as well as several physical and chemical information.
+Two nodes are connected by an edge if they are neighbors along the amino acid sequence or one of three nearest neighbors in space.
+Using this approach, the dataset \textsc{Enzymes} was derived from the BRENDA database~\citep{Schomburg2004}.
+Here, the task is to assign enzymes to one of the 6 EC top level classes, which reflect the chemical reaction they catalyze.
+Similarly, the dataset \textsc{Proteins} was derived from \citep{Dob+2003} and comes with the task to predict whether a protein is an enzyme.
+The dataset \textsc{DD} used by \citet{She+2011} is based on the same data, but contains graphs, where nodes represent individual amino acids and edges their spatial proximity.
 
@@
 Our collection provides several datasets originating from the \emph{IAM Graph Database}~\citep{Riesen2008} such as \textsc{Letter} and \textsc{Fingerprint}.
-Other datasets represent \textsc{Cuneiform} signs~\citep{Kriege2018}, 3d point clouds for robot grasping tasks (\textsc{FirstMM\_DB}) and semantic image processing (\textsc{MSRC})~\citep{Neu+2016}.
+Other datasets represent \textsc{Cuneiform} signs~\citep{Kriege2018}, 3d point clouds for robot grasping tasks (\textsc{FirstMM\_DB}) and semantic image processing (\textsc{Msrc})~\citep{Neu+2016}.
 
 \paragraph{Social networks.}
-Several of the provided datasets are derived from social networks
-TODO
+\citet{Yan+2015a} introduced several graph classification datasets derived from social networks.
+In the \textsc{Reddit} datasets each graph represents a discussion thread, where nodes correspond to users, two of which are connected by an edge, if one responded to a comment of the other.
+This graph model is used to derive several datasets, where the classification task is to distinguish either discussion-based and question/answer-based subreddits (\textsc{Reddit-Binary}) or predict the subreddit, where the thread was posted (\textsc{Reddit-Multi-5K} and \textsc{Reddit-Multi-12K}).
+\textsc{Collab} is dataset derived from scientific collaboration networks.
+Each graph is the ego-network of a researcher and the task is to predict his research field, i.e., High Energy, Condensed Matter or Astro Physics.
+Similarly, the \textsc{Imdb} datasets consist of ego-networks derived from actor collaborations and the task is to predict the genre, e.g.,  Action vs.\@ Romance.
+Similar approaches were used by~\citet{Rozemberczki2020} to obtain larger social network datasets.
+\textsc{Reddit\_Threads} contains more than 200k graphs with the task to predict whether a thread is discussion based.
+\textsc{Deezer\_Ego\_Nets} and \textsc{Twitch\_Egos} contain ego-networks derived from online services and the task is to predict the gender and play beahavior (single or multiple games) of the central user.
+\textsc{GitHub\_Stargazers} contains graphs representing the social networks of GitHub users divided into those who starred popular machine learning and web development repositories.
 
-Recently, temporal graphs were considered, where edges represent the contact or interaction between two individuals at a certain point in time.
-Such graphs are of interest when studying dissemination processes such as epidemics, information and fake news.
-We provide temporal graph classification datasets derived from \textsc{Tumblr}, \textsc{Dblp} and \textsc{Facebook} as well as contacts in a \textsc{Highschool} and at the \textsc{Infectious} exhibition~\citep{Oettershagen2019}.
+Recently, temporal graphs were considered by \citet{Oettershagen2019}, where edges represent the contact or interaction between two individuals at a certain point in time.
+These graphs are of interest when studying dissemination processes such as the spreading of epidemics, rumours or fake news.
+We provide temporal graph classification datasets derived from \textsc{Tumblr}~\citep{rozenshtein2016reconstructing}, \textsc{Dblp} and \textsc{Facebook}~\citep{viswanath2009evolution} as well as contacts between students at the \textsc{MIT}~\cite{konect:eagle06}, in a \textsc{Highschool} and visitors at the \textsc{Infectious} exhibition~\citep{Isella2011}.
+
+\paragraph{Synthetic.}
+Several graph datasets contain synthetic instances that where typically generated to demonstrate the strengths or weaknesses of specific methods.
+The datasets \textsc{SyntheticNew} and \textsc{SyntheticNew} were created by \citet{Fer+2013} (see Erratum) and \citet{Mor+2016}, respectively, to demonstrate the ability of kernels to operate on graphs with continuous attributes.
+With the same goal, the dataset \textsc{Frankenstein} was obtained from a small molecule dataset by replacing the atom labels by MNIST digit images~\citep{Ors+2015}
+
+\citet{Knyazev2019} introduced the datasets \textsc{Colors} and \textsc{Triangles}, where the task is to count the number of nodes with a given one-hot-encoded color and the number of triangles, respectively.
+These classification tasks were considered particularly challenging for graph neural networks.
 
@@
 In order to provide meaningful baselines, we provide implementation of common graph kernels was well as GNNs baselines.
-We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{Shervashidze2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} \nk{Das ist eine Variante mit Labeln und 3 Knoten oder?}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel, as well as the higher-order WL kernels~\cite{Mor+2019b}, in \CPP and made them accessable through the Python interface of \textsc{Tud dataset}, see \url{XXX} for further details.
+We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} \nk{Das ist eine Variante mit Labeln und 3 Knoten oder?}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel, as well as the higher-order WL kernels~\cite{Mor+2019b}, in \CPP and made them accessable through the Python interface of \textsc{Tud dataset}, see \url{XXX} for further details.
 Moreover, all GNN architectures implemented in PyTorch Geometric can be used as baseline as well.
@@
 
-\paragraph{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree}~\cite{Shervashidze2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} \textsc{WL-OA}~\cite{Kri+2016}, and $\delta$-$2$-LWL$^+$ kernel~\cite{Mor+2019b} included in the \textsc{TUD Dataset} package.
+\paragraph{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} \textsc{WL-OA}~\cite{Kri+2016}, and $\delta$-$2$-LWL$^+$ kernel~\cite{Mor+2019b} included in the \textsc{TUD Dataset} package.
 The $C$-parameter was selected from $\{10^{-3}, 10^{-2}, \dotsc, 10^{2},$ $10^{3}\}$ from the validation set.

### 2020-04-09 main.tex
changed section title
AM

@@
 
-\section{Overview of the datasets}
+\section{The TUD dataset collection}
 
@@
 	\label{t2l}	
-	\resizebox{0.6\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
-		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule
+	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
+		\begin{tabular}{@{}c <{\enspace}@{}lccccccc@{}}	\toprule
 
-			& \multirow{3}{*}{\vspace*{4pt}\textbf{Graph Kernel}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
-			& & {\textsc{Data0}}         &  {\textsc{Data1}}      & {\textsc{Data1}}           & {\textsc{Data1}}       & {\textsc{Data1}}           & {\textsc{Data1}}      \\	\toprule
-			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
-				& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
-				& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
-				& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
-			\cmidrule{2-8}	
-			\multirow{4}{*}{\rotatebox{90}{GNN}}	& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
-		& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
-		& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
-		& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
+			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{7}{c}{\textbf{Dataset}}\\\cmidrule{3-9}
+			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}   & {\textsc{deezer\_ego\_nets}}      \\	\toprule
+			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}            &  50.1  \scriptsize $\pm 1.6 \pm 6.2 $       & 72.4 \scriptsize $\pm  0.5 \pm 4.0$ & 50.1  \scriptsize $\pm 0.5 \pm  3.8 $ & 84.3 \scriptsize $\pm 0.3 \pm 1.6$ &73.0  \scriptsize $\pm 0.8 \pm  4.2 $ & 72.6 \scriptsize $\pm  0.4 \pm 3.1 $ &   \scriptsize $\pm $   \\
+				& \text{WLOA}          & 56.8  \scriptsize $\pm  1.7\pm6.4 $       & 72.7  \scriptsize $\pm 0.7 \pm 4.3$ & 49.5 \scriptsize $\pm  0.4 \pm  3.5 $ & 84.9 \scriptsize $\pm  0.4 \pm 1.7$ &73.4  \scriptsize $\pm 0.7 \pm 3.7$ & 88.1 \scriptsize $\pm 0.3 \pm 2.5 $&  \scriptsize $\pm $    \\
+				& \text{GR}            &  31.9   \scriptsize $\pm 1.1 \pm4.8$       & 59.4  \scriptsize $\pm 0.4 \pm 4.6$ & 39.3 \scriptsize $\pm 0.8 \pm  4.1 $ & 58.7  \scriptsize $\pm 0.4 \pm 2.3$ & 69.0  \scriptsize $\pm 0.8 \pm 4.3$ &60.0  \scriptsize $\pm 0.2 \pm 3.2 $&  \scriptsize $\pm $    \\
+				& \text{SP}            &  40.6 \scriptsize $\pm  1.8\pm 5.8 $       & 58.3  \scriptsize $\pm 0.8 \pm  4.9$ & 39.0 \scriptsize $\pm 0.5 \pm  3.8$ &  74.1  \scriptsize $\pm 0.5 \pm 2.0 $  & 75.4  \scriptsize $\pm 0.5 \pm 4.1$ & 84.6 \scriptsize $\pm 0.3 \pm 2.5 $&   \scriptsize $\pm $   \\
+			\cmidrule{2-9}	
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GIN}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ &   \scriptsize $\pm $   \\
+		& \text{Sage}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $   \\
 			\bottomrule

### 2020-04-09 tud_benchmark/main.py

@@ -51,11 +51,11 @@ def main():
 
 
     # datataset = [["ENZYMES", True],
-    #              ["IMDB-BINARY", False], ["IMDB-MULTI", False],
-    #              ["NCI1", True],
-    #              ["PROTEINS", True],
-    #              ["REDDIT-BINARY", False],
-    #              ["deezer_ego_nets", False]]
+    #     #              ["IMDB-BINARY", False], ["IMDB-MULTI", False],
+    #     #              ["NCI1", True],
+    #     #              ["PROTEINS", True],
+    #     #              ["REDDIT-BINARY", False],
+    #     #              ["deezer_ego_nets", False]]
     # for d, use_labels in datataset:
     #
     #     dataset = d

### 2020-04-09 main.tex
MC

@@
 
+\begin{table*}[t]\centering		
+	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
+	\label{t2l}	
+	\resizebox{0.6\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
+		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
+			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
+			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Triangles}}           & {\textsc{github\_stargazers}}       & {\textsc{reddit\_threads}}      \\	\toprule
+							\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 94.23 
+							   \scriptsize $\pm 0.11  \pm 0.49$       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\
+
+			& \text{GR}            &  91.71 \scriptsize $\pm  0.04   \pm 0.52 $       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\  
+			& \text{SP}             &   91.73 \scriptsize $\pm 0.03  \pm 0.49$       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\   
+			\cmidrule{2-7}	
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GIN}            &    \scriptsize $\pm  \pm $       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ \\
+			& \text{Sage}            &    \scriptsize $\pm \pm$       & \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm $  \\
+			\bottomrule
+	\end{tabular}}
+\end{table*}
+
+\begin{table}[t]\centering		
+	\caption{Results for neural and kernel baselines.}
+	\label{t2l}	
+	\resizebox{0.85\columnwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
+		\begin{tabular}{@{}c <{\enspace}@{}lcc@{}}	\toprule
+
+			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{2}{c}{\textbf{Dataset}}\\\cmidrule{3-4}
+			&  & {\textsc{Zinc} (10k)}         &  {\textsc{Zinc} (50k)}         \\	
+			\toprule
+			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}             &   &     \\
+				& \text{GR}            &  &  \\  
+			& \text{SP}             &  & \\   
+			\cmidrule{2-4}
+			\multirow{2}{*}{\rotatebox{90}{GNN}} & \text{$1$-GNN-E}             &   \scriptsize $\pm $  &	\\	
+			& \text{$1$-GNN}             &  0.383 \scriptsize $\pm  0.020$    &  0.247 \scriptsize $\pm   0.020$ \\
+			\bottomrule
+	\end{tabular}}
+\end{table}
+
 \section{Conclusion}

### 2020-04-10 tud_benchmark/auxiliarymethods/evaluation.py
MC

@@ -39,7 +39,7 @@ def sgd_regressor_evaluation(all_feature_matrices, targets, train_index, val_ind
             c_val = targets[val_index]
 
             for a in alpha:
-                clf = SGDRegressor(alpha=a, max_iter=1000)
+                clf = SGDRegressor(alpha=a)
                 clf.fit(train, c_train)
                 p = clf.predict(val)
                 r = mse(c_val, p)

### 2020-04-10 tud_benchmark/main.py

@@ -14,40 +14,116 @@ import numpy as np
 
 
 def main():
-    datataset = [["MCF-7", True, True],
-                 ["MOLT-4", True, True],
-                 ["TRIANGLES", False, False],
-                 ["github_stargazers", False, False],
-                 ["reddit_threads", False, False]]
-    for d, use_labels, use_edge_labels in datataset:
-        dataset = d
-        classes = dp.get_dataset(dataset)
+    dp.get_dataset("ZINC_train", regression=True)
+    dp.get_dataset("ZINC_val", regression=True)
+    dp.get_dataset("ZINC_test", regression=True)
 
-        print("WL1")
-        all_matrices = []
-        for i in range(1, 6):
-            gm = kb.compute_wl_1_sparse(dataset, i, use_labels, use_edge_labels)
-            gm_n = aux.normalize_feature_vector(gm)
-            all_matrices.append(gm_n)
-        print("###")
-        print(linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=True))
+    indices_train = []
+    indices_val = []
+    indices_test = []
 
-        print("GR")
-        all_matrices = []
-        gm = kb.compute_graphlet_sparse(dataset, use_labels, use_edge_labels)
-        gm_n = aux.normalize_feature_vector(gm)
-        all_matrices.append(gm_n)
-        print("###")
-        print(linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=True))
+    infile = open("datasets/test.index.txt", "r")
+    for line in infile:
+        indices_test = line.split(",")
+        indices_test = [int(i) for i in indices_test]
 
-        print("SP")
-        all_matrices = []
-        gm = kb.compute_shortestpath_sparse(dataset, use_labels)
-        gm_n = aux.normalize_feature_vector(gm)
-        all_matrices.append(gm_n)
-        print("###")
-        print(linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=True))
+    infile = open("datasets/val.index.txt", "r")
+    for line in infile:
+        indices_val = line.split(",")
+        indices_val = [int(i) for i in indices_val]
 
+    infile = open("datasets/train.index.txt", "r")
+    for line in infile:
+        indices_train = line.split(",")
+        indices_train = [int(i) for i in indices_train]
+
+    targets = kb.read_targets("ZINC_train", indices_train)
[…]

### 2020-04-10 tud_benchmark/main.py
MC

@@ -50,6 +50,22 @@ def main():
     all_matrices = []
     for i in range(0, 6):
         all_matrices.append(kb.compute_wl_1_sparse_ZINC(i, True, True, indices_train, indices_val, indices_test))
+    print("###")
+
+    indices_train = list(range(10000))
+    indices_val = list(range(1000))
+    indices_test = list(range(1000))
+    p = sgd_regressor_evaluation(all_matrices, targets, indices_train, indices_val, indices_test, num_repetitions=1, alpha=[0.0001])
+    print(p)
+    p = ridge_regressor_evaluation(all_matrices, targets, indices_train, indices_val, indices_test, num_repetitions=1, alpha=[1.0])
+    print(p)
+
+
+
+    print("###")
+    all_matrices = []
+    for i in range(0, 6):
+        all_matrices.append(kb.compute_wl_1_sparse_ZINC(i, True, True, indices_train, indices_val, indices_test))
 
     indices_train = list(range(10000))
     indices_val = list(range(1000))
@@ -59,18 +75,7 @@ def main():
     p = ridge_regressor_evaluation(all_matrices, targets, indices_train, indices_val, indices_test)
     print(p)
 
-    print("###")
-    all_matrices = []
-    for i in range(0, 6):
-        all_matrices.append(aux.normalize_feature_vector(kb.compute_wl_1_sparse_ZINC(i, True, True, indices_train, indices_val, indices_test)))
 
-    indices_train = list(range(10000))
-    indices_val = list(range(1000))
-    indices_test = list(range(1000))
-    p = eval.sgd_regressor_evaluation(all_matrices, targets, indices_train, indices_val, indices_test)
-    print(p)
-    p = eval.ridge_regressor_evaluation(all_matrices, targets, indices_train, indices_val, indices_test)
-    print(p)
 
 
 

### 2020-04-10 tud_benchmark/main.py
MC

@@ -48,7 +48,7 @@ def main():
 
     print("###")
     all_matrices = []
-    for i in range(0, 6):
+    for i in range(4, 5):
         all_matrices.append(kb.compute_wl_1_sparse_ZINC(i, True, True, indices_train, indices_val, indices_test))
     print("###")
 

### 2020-04-11 tud_benchmark/main.py
MC

@@ -42,9 +42,9 @@ def main():
 
     # targets = kb.read_targets("ZINC_train", indices_train)
     # targets.extend(kb.read_targets("ZINC_val", indices_val))
-    targets = kb.read_targets("ZINC_test", list(range(5000)))
-    targets = np.array(targets)
-    print(len(targets))
+    # targets = kb.read_targets("ZINC_test", list(range(5000)))
+    # targets = np.array(targets)
+    # print(len(targets))
     #
     # indices_train = list(range(0,10000))
     # indices_val = list(range(10000,11000))
@@ -63,22 +63,22 @@ def main():
     # print(p)
 
 
-
-
-    all_matrices = []
-    for i in range(4, 5):
-        all_matrices.append(kb.compute_lwl_2_sparse("ZINC_test", i, True, True))
-        print(all_matrices[-1].shape)
-    print("###")
-
-
-
-    #all_matrices = [aux.normalize_feature_vector(all_matrices[-1])]
-    p = ridge_regressor_evaluation(all_matrices, targets,list(range(0,4000)),  list(range(4000, 4500)),  list(range(4500,5000)), num_repetitions=1, alpha=[0.0001])
-    print(p)
-
-
-    exit()
+    #
+    #
+    # all_matrices = []
+    # for i in range(4, 5):
+    #     all_matrices.append(kb.compute_lwl_2_sparse("ZINC_test", i, True, True))
+    #     print(all_matrices[-1].shape)
+    # print("###")
+    #
+    #
+    #
+    # #all_matrices = [aux.normalize_feature_vector(all_matrices[-1])]
+    # p = ridge_regressor_evaluation(all_matrices, targets,list(range(0,4000)),  list(range(4000, 4500)),  list(range(4500,5000)), num_repetitions=1, alpha=[0.0001])
+    # print(p)
+    #
+    #
+    # exit()
 
     #
     # print("###")
@@ -95,45 +95,45 @@ def main():
     # print(p)
 
 
-
-
-
-    print("####################################################################")
-
-    indices_train = []
-    indices_val = []
-    indices_test = []
-
-    infile = open("datasets/train_50.index.txt", "r")
-    for line in infile:
-        indices_train = line.split(",")
-        indices_train = [int(i) for i in indices_train]
-
-    infile = open("datasets/val_50.index.txt", "r")
-    for line in infile:
-        indices_val = line.split(",")
-        indices_val = [int(i) for i in indices_val]
-
-    indices_test = list(range(0, 5000))
-
[…]

### 2020-04-12 tud_benchmark/main.py
dmkljdw

@@ -45,7 +45,7 @@ def main():
 
     print("###")
 
-    all_matrices = kb.compute_wl_2_sparse_ZINC(4, True, True, indices_train, indices_val, indices_test)
+    all_matrices = [kb.compute_wl_2_sparse_ZINC(4, True, True, indices_train, indices_val, indices_test)]
 
     print("####")
     indices_train = list(range(0,10000))

### 2020-04-12 tud_benchmark/main.py
dmkljdw

@@ -14,97 +14,97 @@ import numpy as np
 
 
 def main():
-    dp.get_dataset("ZINC_train", regression=True)
-    dp.get_dataset("ZINC_val", regression=True)
-    dp.get_dataset("ZINC_test", regression=True)
-
-    indices_train = []
-    indices_val = []
-    indices_test = []
-
-    infile = open("datasets/test.index.txt", "r")
-    for line in infile:
-        indices_test = line.split(",")
-        indices_test = [int(i) for i in indices_test]
-
-    infile = open("datasets/val.index.txt", "r")
-    for line in infile:
-        indices_val = line.split(",")
-        indices_val = [int(i) for i in indices_val]
-
-    infile = open("datasets/train.index.txt", "r")
-    for line in infile:
-        indices_train = line.split(",")
-        indices_train = [int(i) for i in indices_train]
-
-    targets = kb.read_targets("ZINC_train", indices_train)
-    targets.extend(kb.read_targets("ZINC_val", indices_val))
-    targets.extend(kb.read_targets("ZINC_test", indices_test))
-    targets = np.array(targets)
-    print(len(targets))
-
-    print("###")
-
-    all_matrices = [kb.compute_wl_2_sparse_ZINC(4, True, True, indices_train, indices_val, indices_test)]
-
-    print("####")
-    indices_train = list(range(0,10000))
-    indices_val = list(range(10000,11000))
-    indices_test = list(range(11000,12000))
+    # dp.get_dataset("ZINC_train", regression=True)
+    # dp.get_dataset("ZINC_val", regression=True)
+    # dp.get_dataset("ZINC_test", regression=True)
+    #
+    # indices_train = []
+    # indices_val = []
+    # indices_test = []
+    #
+    # infile = open("datasets/test.index.txt", "r")
+    # for line in infile:
+    #     indices_test = line.split(",")
+    #     indices_test = [int(i) for i in indices_test]
+    #
+    # infile = open("datasets/val.index.txt", "r")
+    # for line in infile:
+    #     indices_val = line.split(",")
+    #     indices_val = [int(i) for i in indices_val]
+    #
+    # infile = open("datasets/train.index.txt", "r")
+    # for line in infile:
+    #     indices_train = line.split(",")
+    #     indices_train = [int(i) for i in indices_train]
+    #
+    # targets = kb.read_targets("ZINC_train", indices_train)
+    # targets.extend(kb.read_targets("ZINC_val", indices_val))
[…]

### 2020-04-12 tud_benchmark/kernel_baselines/kernel_baselines.cpp
dmkljdw

@@ -137,6 +137,92 @@ GramMatrix compute_wl_2_sparse_ZINC(int num_iterations,  bool use_labels,  bool 
 }
 
 
+GramMatrix compute_sp_sparse_ZINC(bool use_labels,  bool use_edge_labels, const std::vector<int> &indices_train, const std::vector<int> &indices_val, const std::vector<int> &indices_test) {
+
+    GraphDatabase gdb_2 = AuxiliaryMethods::read_graph_txt_file("ZINC_val");
+    gdb_2.erase(gdb_2.begin() + 0);
+
+   cout << "$$$" << endl;
+    GraphDatabase gdb = AuxiliaryMethods::read_graph_txt_file("ZINC_train");
+    gdb.erase(gdb.begin() + 0);
+    cout << "$$$" << endl;
+        GraphDatabase gdb_3 = AuxiliaryMethods::read_graph_txt_file("ZINC_test");
+    gdb_3.erase(gdb_3.begin() + 0);
+   cout << "$$$" << endl;
+
+
+   GraphDatabase gdb_new;
+   for (auto i : indices_train) {
+       gdb_new.push_back(gdb[int(i)]);
+   }
+   cout << gdb_new.size() << endl;
+   cout << "$$$" << endl;
+
+   for (auto i : indices_val) {
+       gdb_new.push_back(gdb_2[int(i)]);
+   }
+   cout << gdb_new.size() << endl;
+   cout << "$$$" << endl;
+
+
+   for (auto i : indices_test) {
+       gdb_new.push_back(gdb_3[int(i)]);
+   }
+   cout << gdb_new.size() << endl;
+   cout << "$$$" << endl;
+
+
+    ShortestPathKernel::ShortestPathKernel wl(gdb_new);
+    GramMatrix gm;
+    gm = wl.compute_gram_matrix(use_labels, false);
+
+    return gm;
+}
+
+
+GramMatrix compute_gr_sparse_ZINC(bool use_labels,  bool use_edge_labels, const std::vector<int> &indices_train, const std::vector<int> &indices_val, const std::vector<int> &indices_test) {
+
+    GraphDatabase gdb_2 = AuxiliaryMethods::read_graph_txt_file("ZINC_val");
+    gdb_2.erase(gdb_2.begin() + 0);
+
+   cout << "$$$" << endl;
[…]

### 2020-04-12 tud_benchmark/main.py
dmkljdw

@@ -14,52 +14,52 @@ import numpy as np
 
 
 def main():
-    dp.get_dataset("ZINC_train", regression=True)
-    dp.get_dataset("ZINC_val", regression=True)
-    dp.get_dataset("ZINC_test", regression=True)
-
-    indices_train = []
-    indices_val = []
-    indices_test = []
-
-    infile = open("datasets/test.index.txt", "r")
-    for line in infile:
-        indices_test = line.split(",")
-        indices_test = [int(i) for i in indices_test]
-
-    infile = open("datasets/val.index.txt", "r")
-    for line in infile:
-        indices_val = line.split(",")
-        indices_val = [int(i) for i in indices_val]
-
-    infile = open("datasets/train.index.txt", "r")
-    for line in infile:
-        indices_train = line.split(",")
-        indices_train = [int(i) for i in indices_train]
-
-    targets = kb.read_targets("ZINC_train", indices_train)
-    targets.extend(kb.read_targets("ZINC_val", indices_val))
-    targets.extend(kb.read_targets("ZINC_test", indices_test))
-    targets = np.array(targets)
-    print(len(targets))
-
-    print("###")
-
-    all_matrices = [kb.compute_sp_sparse_ZINC(True, True, indices_train, indices_val, indices_test)]
-
-    print("####")
-    indices_train = list(range(0,10000))
-    indices_val = list(range(10000,11000))
-    indices_test = list(range(11000,12000))
-
-    #all_matrices = [all_matrices[4]]
-
-    p = ridge_regressor_evaluation(all_matrices, targets, indices_train, indices_val, indices_test, num_repetitions=5,
-                                   alpha=[1.0])
-    print(p)
-
-
-
+    # dp.get_dataset("ZINC_train", regression=True)
+    # dp.get_dataset("ZINC_val", regression=True)
+    # dp.get_dataset("ZINC_test", regression=True)
+    #
+    # indices_train = []
+    # indices_val = []
+    # indices_test = []
+    #
+    # infile = open("datasets/test.index.txt", "r")
+    # for line in infile:
+    #     indices_test = line.split(",")
+    #     indices_test = [int(i) for i in indices_test]
+    #
+    # infile = open("datasets/val.index.txt", "r")
+    # for line in infile:
+    #     indices_val = line.split(",")
+    #     indices_val = [int(i) for i in indices_val]
+    #
+    # infile = open("datasets/train.index.txt", "r")
[…]

### 2020-04-12 tud_benchmark/main.py
dmkljdw

@@ -85,7 +85,7 @@ def main():
 
     print("###")
 
-    all_matrices = [kb.compute_gr_sparse_ZINC(True, True, indices_train, indices_val, indices_test)]
+    all_matrices = [kb.compute_sp_sparse_ZINC(True, True, indices_train, indices_val, indices_test)]
     print("####")
 
     indices_train = list(range(0,50000))

### 2020-04-12 tud_benchmark/main.py
dmkljdw

@@ -14,28 +14,68 @@ import numpy as np
 
 
 def main():
-    # dp.get_dataset("ZINC_train", regression=True)
-    # dp.get_dataset("ZINC_val", regression=True)
-    # dp.get_dataset("ZINC_test", regression=True)
-    #
+    dp.get_dataset("ZINC_train", regression=True)
+    dp.get_dataset("ZINC_val", regression=True)
+    dp.get_dataset("ZINC_test", regression=True)
+
+    indices_train = []
+    indices_val = []
+    indices_test = []
+
+    infile = open("datasets/test.index.txt", "r")
+    for line in infile:
+        indices_test = line.split(",")
+        indices_test = [int(i) for i in indices_test]
+
+    infile = open("datasets/val.index.txt", "r")
+    for line in infile:
+        indices_val = line.split(",")
+        indices_val = [int(i) for i in indices_val]
+
+    infile = open("datasets/train.index.txt", "r")
+    for line in infile:
+        indices_train = line.split(",")
+        indices_train = [int(i) for i in indices_train]
+
+    targets = kb.read_targets("ZINC_train", indices_train)
+    targets.extend(kb.read_targets("ZINC_val", indices_val))
+    targets.extend(kb.read_targets("ZINC_test", indices_test))
+    targets = np.array(targets)
+    print(len(targets))
+
+    print("###")
+
+    all_matrices = [aux.normalize_feature_vector(kb.compute_gr_sparse_ZINC(True, True, indices_train, indices_val, indices_test))]
+
+    print("####")
+    indices_train = list(range(0,10000))
+    indices_val = list(range(10000,11000))
+    indices_test = list(range(11000,12000))
+
+    #all_matrices = [all_matrices[4]]
+
+    p = ridge_regressor_evaluation(all_matrices, targets, indices_train, indices_val, indices_test, num_repetitions=5,
+                                   alpha=[1.0])
+    print(p)
+
+    exit()
+
+
     # indices_train = []
     # indices_val = []
     # indices_test = []
     #
-    # infile = open("datasets/test.index.txt", "r")
+    # infile = open("datasets/train_50.index.txt", "r")
     # for line in infile:
-    #     indices_test = line.split(",")
-    #     indices_test = [int(i) for i in indices_test]
+    #     indices_train = line.split(",")
+    #     indices_train = [int(i) for i in indices_train]
     #
-    # infile = open("datasets/val.index.txt", "r")
+    # infile = open("datasets/val_50.index.txt", "r")
[…]

### 2020-04-12 tud_benchmark/main.py
dmkljdw

@@ -45,7 +45,7 @@ def main():
 
     print("###")
 
-    all_matrices = [aux.normalize_feature_vector(kb.compute_gr_sparse_ZINC(True, True, indices_train, indices_val, indices_test))]
+    all_matrices = [aux.normalize_feature_vector(kb.compute_wl_1_sparse(True, True, indices_train, indices_val, indices_test))]
 
     print("####")
     indices_train = list(range(0,10000))

### 2020-04-12 tud_benchmark/main.py
dmkljdw

@@ -45,7 +45,7 @@ def main():
 
     print("###")
 
-    all_matrices = [aux.normalize_feature_vector(kb.compute_wl_1_sparse(True, True, indices_train, indices_val, indices_test))]
+    all_matrices = [aux.normalize_feature_vector(kb.compute_wl_1_sparse(4, True, True, indices_train, indices_val, indices_test))]
 
     print("####")
     indices_train = list(range(0,10000))

### 2020-04-12 tud_benchmark/main.py
dmkljdw

@@ -45,14 +45,14 @@ def main():
 
     print("###")
 
-    all_matrices = [aux.normalize_feature_vector(kb.compute_wl_1_sparse(4, True, True, indices_train, indices_val, indices_test))]
+    all_matrices = [aux.normalize_feature_vector(kb.compute_wl_1_sparse_ZINC(True, True, indices_train, indices_val, indices_test))]
 
     print("####")
     indices_train = list(range(0,10000))
     indices_val = list(range(10000,11000))
     indices_test = list(range(11000,12000))
 
-    #all_matrices = [all_matrices[4]]
+    all_matrices = [all_matrices[4]]
 
     p = ridge_regressor_evaluation(all_matrices, targets, indices_train, indices_val, indices_test, num_repetitions=5,
                                    alpha=[1.0])
@@ -61,45 +61,45 @@ def main():
     exit()
 
 
-    # indices_train = []
-    # indices_val = []
-    # indices_test = []
-    #
-    # infile = open("datasets/train_50.index.txt", "r")
-    # for line in infile:
-    #     indices_train = line.split(",")
-    #     indices_train = [int(i) for i in indices_train]
-    #
-    # infile = open("datasets/val_50.index.txt", "r")
-    # for line in infile:
-    #     indices_val = line.split(",")
-    #     indices_val = [int(i) for i in indices_val]
-    #
-    # indices_test = list(range(0,5000))
-    #
-    # targets = kb.read_targets("ZINC_train", indices_train)
-    # targets.extend(kb.read_targets("ZINC_val", indices_val))
-    # targets.extend(kb.read_targets("ZINC_test", indices_test))
-    # targets = np.array(targets)
-    # print(len(targets))
-    #
-    # print("###")
-    #
-    # all_matrices = [kb.compute_sp_sparse_ZINC(True, True, indices_train, indices_val, indices_test)]
-    # print("####")
-    #
-    # indices_train = list(range(0,50000))
-    # indices_val = list(range(50000,55000))
-    # indices_test = list(range(55000,60000))
-    #
-    # #all_matrices = [all_matrices[4]]
-    #
-    # # p = sgd_regressor_evaluation(all_matrices, targets, indices_train, indices_val, indices_test, num_repetitions=1,
-    # #                              alpha=[0.0001])
-    # # print(p)
-    # p = ridge_regressor_evaluation(all_matrices, targets, indices_train, indices_val, indices_test, num_repetitions=5,
-    #                                alpha=[1.0])
[…]

### 2020-04-12 tud_benchmark/main.py
dmkljdw

@@ -58,8 +58,6 @@ def main():
                                    alpha=[1.0])
     print(p)
 
-    exit()
-
 
     indices_train = []
     indices_val = []

### 2020-04-26 tud_benchmark/auxiliarymethods/evaluation.py
Added max iterations to linear svm.

@@ -150,7 +150,7 @@ def kernel_ridge_regressor_evaluation(all_feature_matrices, targets, train_index
 # 10-CV for linear svm with sparse feature vectors and hyperparameter selection.
 def linear_svm_evaluation(all_feature_matrices, classes, num_repetitions=10,
                           C=[10 ** 3, 10 ** 2, 10 ** 1, 10 ** 0, 10 ** -1, 10 ** -2, 10 ** -3], all_std=False,
-                          primal=True):
+                          primal=True, max_iterations=5000):
     # Acc. over all repetitions.
     test_accuracies_all = []
     # All acc. over all folds and repetitions.
@@ -173,7 +173,7 @@ def linear_svm_evaluation(all_feature_matrices, classes, num_repetitions=10,
                 c_val = classes[val_index]
 
                 for c in C:
-                    clf = LinearSVC(C=c, dual=not primal)
+                    clf = LinearSVC(C=c, dual=not primal, max_iterations=max_iterations)
                     clf.fit(train, c_train)
                     p = clf.predict(val)
                     a = np.sum(np.equal(p, c_val)) / val.shape[0]

### 2020-04-26 tud_benchmark/main.py

@@ -171,7 +171,7 @@ def main():
             gm_n = aux.normalize_feature_vector(gm)
             all_matrices.append(gm_n)
         print("###")
-        print(linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=False))
+        print(linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=False, max_iterations=5000))
 
         print("GR")
         all_matrices = []
@@ -179,7 +179,7 @@ def main():
         gm_n = aux.normalize_feature_vector(gm)
         all_matrices.append(gm_n)
         print("###")
-        print(linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=False))
+        print(linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=False, max_iterations=5000))
 
         print("SP")
         all_matrices = []
@@ -187,7 +187,7 @@ def main():
         gm_n = aux.normalize_feature_vector(gm)
         all_matrices.append(gm_n)
         print("###")
-        print(linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=False))
+        print(linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=False, max_iterations=5000))
         #
 
     #

### 2020-04-26 main.tex
MC
dmkljdw
Added max iterations to linear svm.

--- 2020-04-06 main.tex
@@
 \twocolumn[
-\icmltitle{TUD Datasets: A collection of benchmark datasets for learning with graphs}
+\icmltitle{TUDatasets: A collection of benchmark datasets for learning with graphs}
 \icmlsetsymbol{equal}{*}
@@
 	\label{t2l}	
-	\resizebox{0.6\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
+	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
 		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule
 
-			& \multirow{3}{*}{\vspace*{4pt}\textbf{Graph Kernel}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
-			& & {\textsc{Data0}}         &  {\textsc{Data1}}      & {\textsc{Data1}}           & {\textsc{Data1}}       & {\textsc{Data1}}           & {\textsc{Data1}}      \\	\toprule
-			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
-				& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
-				& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
-				& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
+			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
+			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule
+			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &  50.1  \scriptsize $\pm 1.6 \pm 6.2 $       & 72.4 \scriptsize $\pm  0.5 \pm 4.0$ & 50.1  \scriptsize $\pm 0.5 \pm  3.8 $ & 84.3 \scriptsize $\pm 0.3 \pm 1.6$ &73.0  \scriptsize $\pm 0.8 \pm  4.2 $ & 72.6 \scriptsize $\pm  0.4 \pm 3.1$  \\
+				& \text{WLOA} & 56.8  \scriptsize $\pm  1.7\pm6.4 $       & 72.7  \scriptsize $\pm 0.7 \pm 4.3$ & 49.5 \scriptsize $\pm  0.4 \pm  3.5 $ & 84.9 \scriptsize $\pm  0.4 \pm 1.7$ &73.4  \scriptsize $\pm 0.7 \pm 3.7$ & 88.1 \scriptsize $\pm 0.3 \pm 2.5 $   \\
+				& \text{GR}            &  31.9   \scriptsize $\pm 1.1 \pm4.8$       & 59.4  \scriptsize $\pm 0.4 \pm 4.6$ & 39.3 \scriptsize $\pm 0.8 \pm  4.1 $ & 58.7  \scriptsize $\pm 0.4 \pm 2.3$ & 69.0  \scriptsize $\pm 0.8 \pm 4.3$ &60.0  \scriptsize $\pm 0.2 \pm 3.2 $   \\
+				& \text{SP}            &  40.6 \scriptsize $\pm  1.8\pm 5.8 $       & 58.3  \scriptsize $\pm 0.8 \pm  4.9$ & 39.0 \scriptsize $\pm 0.5 \pm  3.8$ &  74.1  \scriptsize $\pm 0.5 \pm 2.0 $  & 75.4  \scriptsize $\pm 0.5 \pm 4.1$ & 84.6 \scriptsize $\pm 0.3 \pm 2.5 $  \\
 			\cmidrule{2-8}	
-			\multirow{4}{*}{\rotatebox{90}{GNN}}	& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
-		& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
-		& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
-		& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GIN-$\varepsilon$}    &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $    \\
+		& \text{Sage}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $  \\
 			\bottomrule
@@
 \end{table*}
+
+\begin{table*}[t]\centering		
+	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
+	\label{t2l}	
+	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
+		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
+			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
+			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Triangles}}           & {\textsc{github\_stargazers}}       & {\textsc{reddit\_threads}}      \\	\toprule
+							\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 94.23 
+							   \scriptsize $\pm 0.11  \pm 0.49$       & 94.29 \scriptsize $\pm 0.07  \pm 0.39$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\
+
+			& \text{GR}            &  91.71 \scriptsize $\pm  0.04   \pm 0.52 $       & 92.10  \scriptsize $\pm 0.02 \pm 0.45$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\  
+			& \text{SP}             &   91.73 \scriptsize $\pm 0.03  \pm 0.49$       & 92.05 \scriptsize $\pm 0.02 \pm 0.44 $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\   
+			\cmidrule{2-7}	
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GIN-E-$\varepsilon$}         &    \scriptsize $\pm  \pm $       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ \\
+			& \text{Sage}            &    \scriptsize $\pm \pm$       & \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm $  \\
+			\bottomrule
+	\end{tabular}}
+\end{table*}
+
+\begin{table}[t]\centering		
+	\caption{Results for neural and kernel baselines.}
+	\label{t2l}	
+	\resizebox{0.55\columnwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
+		\begin{tabular}{@{}c <{\enspace}@{}lcc@{}}	\toprule
+
+			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{2}{c}{\textbf{Dataset}}\\\cmidrule{3-4}
+			&  & {\textsc{Zinc} (10k)}         &  {\textsc{Zinc} (50k)}         \\	
+			\toprule
+			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}             &      \scriptsize $<\!0.000$ &  \scriptsize $ <\!0.000$  \\  
+				& \text{GR}            &\scriptsize $ <\!0.000$ &  \scriptsize $ <\!0.000$  \\  
+			& \text{SP}             &   \scriptsize $ <\!0.000$  &  \scriptsize $ <\!0.000$ \\   
+			\cmidrule{2-4}
+			\multirow{2}{*}{\rotatebox{90}{GNN}} & \text{$1$-GNN-E}             &  0.278 \scriptsize $\pm 0.022$  & 0.145 \scriptsize $\pm  0.006  $		\\	
+			& \text{$1$-GNN}             &  0.383 \scriptsize $\pm  0.020$    &  0.247 \scriptsize $\pm   0.020$ \\
+			\bottomrule
+	\end{tabular}}
+\end{table}
 

### 2020-04-26 tud_benchmark/auxiliarymethods/evaluation.py

@@ -14,55 +14,15 @@ from sklearn.linear_model import SGDRegressor, Ridge
 from sklearn.kernel_ridge import KernelRidge
 from sklearn.metrics import mean_absolute_error as mse
 
+
 # Return arg max of iterable, e.g., a list.
 def argmax(iterable):
     return max(enumerate(iterable), key=lambda x: x[1])[0]
 
 
-
-
-# 10-CV for linear svm with sparse feature vectors and hyperparameter selection.
-def sgd_regressor_evaluation(all_feature_matrices, targets, train_index, val_index, test_index, num_repetitions=5,
-                             alpha=[0.00001, 0.0001, 0.001, 0.01]):
-    # Acc. over all repetitions.
-    test_accuracies = []
-
-    for _ in range(num_repetitions):
-
-        val_accuracies = []
-        models = []
-        for f in all_feature_matrices:
-
-            train = f[train_index]
-            val = f[val_index]
-
-            c_train = targets[train_index]
-            c_val = targets[val_index]
-
-            for a in alpha:
-                clf = SGDRegressor(alpha=a)
-                clf.fit(train, c_train)
-                p = clf.predict(val)
-                r = mse(c_val, p)
-
-                models.append(clf)
-                val_accuracies.append(r)
-
-        best_i = argmax(val_accuracies)
-        best_model = models[best_i]
-
-        # Eval. model on test split that performed best on val. split.
-        test = all_feature_matrices[int(best_i / len(alpha))][test_index]
-        c_test = targets[test_index]
-        p = best_model.predict(test)
-        a = mse(c_test, p, multioutput='uniform_average')
-        test_accuracies.append(a)
-
-    return (np.array(test_accuracies).mean(), np.array(test_accuracies).std())
-
-
+# TODO: Check this.
 def ridge_regressor_evaluation(all_feature_matrices, targets, train_index, val_index, test_index, num_repetitions=5,
-                             alpha=[0.01, 0.1, 1.0, 2.0],  std=None):
+                               alpha=[0.01, 0.1, 1.0, 2.0], std=None):
     # Acc. over all repetitions.
     test_accuracies = []
 
@@ -79,7 +39,7 @@ def ridge_regressor_evaluation(all_feature_matrices, targets, train_index, val_i
             c_val = targets[val_index]
 
             for a in alpha:
-                clf = Ridge(alpha=a, solver="sag", max_iter=5000, random_state = np.random.RandomState())
[…]

### 2020-04-26 tud_benchmark/main_gnn.py

@@ -1,0 +1,23 @@
+from __future__ import division
+from auxiliarymethods.evaluation import kernel_svm_evaluation, linear_svm_evaluation, sgd_regressor_evaluation, \
+    ridge_regressor_evaluation, kernel_ridge_regressor_evaluation
+from auxiliarymethods.evaluation import gnn_evaluation
+from gnn_baselines.gin import GIN0
+from sklearn.linear_model import LinearRegression, Ridge, ElasticNet, SGDRegressor
+
+from sklearn.model_selection import train_test_split
+from sklearn.metrics import mean_absolute_error as mse
+import kernel_baselines as kb
+import auxiliarymethods.auxiliary_methods as aux
+import auxiliarymethods.datasets as dp
+from sklearn.preprocessing import StandardScaler
+import numpy as np
+
+
+def main():
+
+
+
+
+if __name__ == "__main__":
+    main()

### 2020-04-26 tud_benchmark/auxiliarymethods/evaluation.py
Added max iterations to linear svm.

@@ -268,7 +268,7 @@ def gnn_evaluation(gnn, ds_name, layers, hidden, max_num_epochs=100, batch_size=
                     vals.append(val_acc)
                     tests.append(test_acc)
 
-            # Determine best model.
+            # Determine best model based on validation set performance.
             best_i = argmax(vals)
             best_test = tests[best_i]
             test_accuracies.append(best_test)

### 2020-04-26 main.tex
GNN evaluation.

@@
-%%%%%%%% ICML 2020 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
-
 \documentclass{article}
@@
 \newcommand{\nk}[1]{{{\textcolor{brown}{\textbf{[NK:} {#1}\textbf{]}}}}}
+\newcommand{\cm}[1]{{{\textcolor{red}{\textbf{[CM:} {#1}\textbf{]}}}}}
 
@@
 \twocolumn[
-\icmltitle{TUDatasets: A collection of benchmark datasets for learning with graphs}
+\icmltitle{TUDataset: A collection of benchmark datasets for learning with graphs}
 \icmlsetsymbol{equal}{*}
@@
 Recently, there has been an increasing interest in learning with graph data, especially using graph neural networks.
-However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging behind.
-That is, most paper papers evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area.
-To address this, we introduce the \textsc{Tud dataset} for graph classification and regression.
-The dataset consists of over 150 \nk{Zur Zeit sind es 128.
-Mehr als 100 klingt auch gut oder?} datasets from a wide range of applications and varying sizes.
-We provide Python-based data loaders, baseline implementations, and evaluation tools.
+However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging.
+That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area.
+To address this, we introduce the \textsc{TuDataset} for graph classification and regression.
+The dataset consists of over 120 datasets from a wide range of applications and varying sizes.
+We provide Python-based data loaders, baseline method implementations, and evaluation tools.
 Here, we give an overview of the datasets, evaluation tools, and provide baseline experiments.
-\nk{Make clear that these are datasets collected from the authors of various papers}
+All datasets can be obtained from \url{www.graphlearning.io}.
+The experiments are fully reproduceable from the code available at \url{www.github.com/chrsmrrs/tudatasets}.
 \end{abstract}
@@
 \section{Introduction}
-
 Graph-structured data is ubiquitous across application domains ranging from chemo- and bioinformatics to image and social network analysis.
@@
 Here, we give an overview of \textsc{Tud datasets}.
-The benchmark collection consists of over 150 datasets from a wide range of domains for supervised learning with graphs, i.e., classificiation and regression.
+The benchmark collection consists of over 120 datasets from a wide range of domains for supervised learning with graphs, i.e., classificiation and regression.
 All datasets are provided in a common dataset format at \url{graphlearning.io}, and can easily be accessed from popular graph learning frameworks such as \emph{Pytorch Geometric}~\cite{Fey+2019} and \emph{DGL}~\cite{Wan+2019}.
@@
 \paragraph{Related work.}
-
-There exists two approaches to supervised learing with graphs, graph kernels and graph neural networks (GNNs).
+There exists two main approaches to supervised learning with graphs, graph kernels and graph neural networks (GNNs).
 Graph kernels have been studied extensively in the past 15 years, see ~\cite{Kri+2019} for a thorough overview.
@@
 
+\cm{Add new work from Borgwardt and Pascale Frossard.}
+
 Recently, GNNs~\cite{Gil+2017} emerged as a alternative to graph kernels.
 Notable instances of this model include~\cite{Duv+2015},~\cite{Li+2016},~\cite{Ham+2017} and the spectral approaches proposed in~\cite{Bru+2014,Def+2015,Kip+2017}---all of which descend from early work in~\cite{Kir+1995,Mer+2005,Sca+2009}.
+More expressive higher-order approaches are proposed in~\cite{Mor+2019,Mar+2019}.
 A unifying message passing architecture can be found in~\cite{Gil+2017}.
-Two recent surveys~\cite{wu2019comprehensive,zhou2018graph} provide a thorough overview of graph neural networks
+Two recent surveys~\cite{wu2019comprehensive,zhou2018graph} provide a thorough overview of graph neural networks.
 
-The papers~\cite{Fey+2019,Err+2019,Dwi+2020} evalute GNNs using a unified evaluation procedure, however, both only use small scale datasets.
-Recently, \url{ogb.stanford.edu} launchend, however the provided datasets for graph classification focus on chemistry applications, and the number is quite limited at this point.
+The papers~\cite{Fey+2019,Err+2019,Dwi+2020} evalute GNNs using a unified evaluation procedure, however, they only use small- or medium scale datasets.
+Recently, \url{ogb.stanford.edu} launchend, however the provided datasets for graph classification focus on chemistry and bioinformatic applications, and the number is quite limited at this point.
 
-\paragraph{Contributions} We give an overview of \textsc{Tud dataset}, its unified evalution procudures, and baseline methods.
+\paragraph{Contributions} We give an overview of \textsc{TuDataset}, its unified evalution procudures, and baseline methods.
 Moreover, we report results on a experimental study comparing graph kernels and GNNs on a subset of the \textsc{Tud dataset}.

### 2020-04-26 tud_benchmark/main_gnn.py

@@ -13,7 +13,7 @@ import numpy as np
 
 
 def main():
-    results = gnn_evaluation(GINWithJK, "PROTEINS", [2], [64], max_num_epochs=100, batch_size=25, start_lr=0.001, num_repetitions=2,
+    results = gnn_evaluation(GINWithJK, "PROTEINS", [1,2,3,4,5], [64], max_num_epochs=100, batch_size=25, start_lr=0.001, num_repetitions=10,
                    all_std=True)
     print(results)
 

### 2020-04-27 main.tex
Minor changes in text throughout.

@@
 
-\paragraph{Contributions} We give an overview of \textsc{TuDataset}, its unified evalution procudures, and baseline methods.
-Moreover, we report results on a experimental study comparing graph kernels and GNNs on a subset of the \textsc{Tud dataset}.
+\paragraph{Contributions} We give an overview of \textsc{TuDataset}, its unified evalution procedures, and baseline methods.
+Moreover, we report results on a experimental study comparing graph kernels and GNNs on a subset of the \textsc{TuDataset}.
 
-\section{The TUD dataset collection}
+\section{The TUDataset collection}
 
-The \textsc{Tud dataset} contain over 150 datasets provided at \url{graphlearning.io}.
-The data loader, baseline methods, experimental evaluation tool can be installed by running \texttt{pip install tud-datasets}, see \url{XXX} for further details.
+The \textsc{TuDataset} contains over 120 datasets provided at \url{graphlearning.io}.
+The data  baseline methods and experimental evaluation tools can be installed by running \texttt{pip install tudatasets}.
+See the website for dataset statistics and further documentation.
 
@@
 Our collection of datasets covers graphs from various domains, which were provided by different authors.
-Therefore, they differ regarding the used graph model even within the same domain and the provided annotations, e.g., discrete or continuous node/edge attributes.
-We give an overview of some representative domains and graph models.
+Therefore, they differ regarding the used graph model even within the same domain and the provided annotations, e.g., discrete or continuous node and edge attributes.
+Here, we give an overview of some representative domains and graph models.
 
@@
 The \textsc{Alchemy} was proposed by~\citet{Chen2019a} for benchmarking {AI} models.
+
+\cm{Mention \textsc{ZINC} and the also mention size of DS, 200k}
 
@@
 
-\subsection{Baselines}
+\subsection{Baselines Methods}
 
-In order to provide meaningful baselines, we provide implementation of common graph kernels was well as GNNs baselines.
-We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} \nk{Das ist eine Variante mit Labeln und 3 Knoten oder?}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel, as well as the higher-order WL kernels~\cite{Mor+2019b}, in \CPP and made them accessable through the Python interface of \textsc{Tud dataset}, see \url{XXX} for further details.
-Moreover, all GNN architectures implemented in PyTorch Geometric can be used as baseline as well.
+To provide meaningful baselines, we provide implementations of common graph kernel as well as GNNs baselines.
+We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} \nk{Das ist eine Variante mit Labeln und 3 Knoten oder?
+CM: Ja}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel, as well as the higher-order WL kernels~\cite{Mor+2019b}, in \CPP and made them accessible through the Python interface of \textsc{Tud dataset}, see the website for further details.
+Moreover, all GNN architectures provided by PyTorch Geometric can be conveniently used as a baseline as well.
 
-Vertex kernel and edge kernel? \nk{Wäre interessant!}
+\subsection{Evaluation Methods}\label{eval}
 
-\subsection{Evaluation tools}\label{eval}
-
-In order to insure a fair and meaningful comparision between methods, we propose the following evaluation proceudres, and software tools for kernels and GNN approaches.
-All proposed methods can be conviently accessed from the Python interface, see \url{XXX} for further details.
-First, for kernels we propose the established $C$-SVM implementation \textsc{LibSvm}~\cite{Cha+11} for kernels that compute a Gram matrix, and the linear $C$-SVM implementation \textsc{LibLinear}~\cite{Fan+2008} for kernels  that can be computed based on explicit feature maps.
+To ensure a fair and meaningful comparison between methods, we propose the following evaluation procedures for kernels and GNN approaches.
+All proposed methods can be conveniently accessed from the Python interface, see the website for further details.
+First, for kernels we propose the established $C$-SVM implementation \textsc{LibSvm}~\cite{Cha+11} for kernels that compute a Gram matrix, and the linear $C$-SVM implementation \textsc{LibLinear}~\cite{Fan+2008} for kernels  that can be computed based on sparse, explicit feature maps.
 We optimize GNNs end-to-end using \textsc{Adam}~\cite{}.
-Too compute accuracies and other metrics for evaluation, we propose to use $10$-fold cross validation, where we select a validation set uniformly at random from each training fold ($10\%$ of the training fold), to select hyperparamets, e.g., number of iterations, $C$ parameter, number of layers, learning rate, feature dimension, etc.
-
-Repeat ten times?
+Too compute accuracies and MAE, we propose to use $10$-fold cross-validation, where we select a validation set uniformly at random from each training fold ($10\%$ of the training fold), to select hyperparameters, e.g., number of iterations, $C$ parameter, number of layers, feature dimension, dots Moreover, we repeat the above evaluation ten times and report standard deviations over all ten repetitions, and additionally across all one hundred runs (i.e., ten repetitions with ten folds each.).
 
@@
 
-Our intention here is to provide baseline experiments, and compare graph kernels and GNNs. More precisely, we address the following questions:
+\cm{work on this}
+
+Our intention here is to provide baseline experiments and compare graph kernels and GNNs. More precisely, we address the following questions:
 \begin{description}
 	\item[Q1] Are GNNs superior to graph kernels? Is there a single method that dominates?
-	\item[Q2] ?
-	\item[Q3] ?
+	\item[Q2] How do kernels compare to GNNs on large-scale molecular learning tasks.
 \end{description}
@@
 \textsc{Imdb-BINARY}, \textsc{Imdb-MULTI}, \textsc{Mcf-7}, \textsc{Molt-4},	\textsc{Nci1}, \textsc{Proteins},
-\textsc{Reddit-Binary},	\textsc{reddit\_threads}, \textsc{twitch\_egos}, \textsc{Uacc257}. See the appendix for dataset statistics.
+\textsc{Reddit-Binary},	\textsc{reddit\_threads}, \textsc{twitch\_egos}, \textsc{Uacc257}. See the website for dataset statistics.
 
@@
 All experiments can be reproduced using the scripts provided at \url{XXX}.
+
+\cm{Add regression}
 

### 2020-04-27 tud_benchmark/main_gnn.py
Minor changes in text throughout.

@@ -1,6 +1,6 @@
 from __future__ import division
 from auxiliarymethods.evaluation import gnn_evaluation
-from gnn_baselines.gnn_architectures import GIN0, GINWithJK
+from gnn_baselines.gnn_architectures import GINWithJK, GraphSAGEWithJK
 from sklearn.linear_model import LinearRegression, Ridge, ElasticNet, SGDRegressor
 
 from sklearn.model_selection import train_test_split
@@ -13,12 +13,22 @@ import numpy as np
 
 
 def main():
-    results = gnn_evaluation(GINWithJK, "PROTEINS", [1,2,3,4,5], [64], max_num_epochs=100, batch_size=25, start_lr=0.001, num_repetitions=10,
-                   all_std=True)
-    print(results)
+    datasets = [
+        ["ENZYMES", True],
+        # ["IMDB-BINARY", False], ["IMDB-MULTI", False],["REDDIT-BINARY", False]
+        ["NCI1", True],
+        ["PROTEINS", True]]
 
-    results = gnn_evaluation(GIN0, "MUTAG", [1,2,3,4,5], [16, 32, 64, 128], max_num_epochs=200, batch_size=25, start_lr=0.001, num_repetitions=10,
-                   all_std=True)
+    for d, use_labels in datasets:
+        results = gnn_evaluation(GINWithJK, d, [1, 2, 3, 4, 5], [64], max_num_epochs=200, batch_size=25, start_lr=0.001,
+                                 num_repetitions=10,
+                                 all_std=True)
+        print(results)
+
+        results = gnn_evaluation(GraphSAGEWithJK, d, [1, 2, 3, 4, 5], [16, 32, 64, 128], max_num_epochs=200,
+                                 batch_size=25, start_lr=0.001, num_repetitions=10,
+                                 all_std=True)
+        print(results)
 
     print(results)
 

### 2020-04-27 tud_benchmark/auxiliarymethods/datasets.py
Minor changes in text throughout.

@@ -33,9 +33,9 @@ def read_multi_targets(ds_name):
     return np.array(classes)
 
 
-def get_dataset(dataset, regression=False, multigregression=False):
+def get_dataset(dataset, regression=False, multigregression=False, one_hot=False):
     path = osp.join(osp.dirname(osp.realpath(__file__)), '..', 'datasets', dataset)
-    TUDataset(path, name=dataset)
+    TUDataset(path, name=dataset, transform=)
 
     if multigregression:
         return read_multi_targets(dataset)

### 2020-04-27 tud_benchmark/main_gnn.py

@@ -11,6 +11,7 @@ import auxiliarymethods.datasets as dp
 from sklearn.preprocessing import StandardScaler
 import numpy as np
 
+# TODO: Add one-hot.
 
 def main():
     datasets = [
@@ -20,13 +21,15 @@ def main():
         ["PROTEINS", True]]
 
     for d, use_labels in datasets:
-        results = gnn_evaluation(GINWithJK, d, [1, 2, 3, 4, 5], [64], max_num_epochs=200, batch_size=25, start_lr=0.001,
+        classes = dp.get_dataset(d)
+
+        results = gnn_evaluation(GINWithJK, d, [1, 2, 3, 4, 5], [16, 32, 64, 128], max_num_epochs=200, batch_size=32, start_lr=0.01,
                                  num_repetitions=10,
                                  all_std=True)
         print(results)
 
         results = gnn_evaluation(GraphSAGEWithJK, d, [1, 2, 3, 4, 5], [16, 32, 64, 128], max_num_epochs=200,
-                                 batch_size=25, start_lr=0.001, num_repetitions=10,
+                                 batch_size=32, start_lr=0.01, num_repetitions=10,
                                  all_std=True)
         print(results)
 

### 2020-04-27 tud_benchmark/auxiliarymethods/datasets.py
Minor changes in text throughout.

@@ -35,7 +35,7 @@ def read_multi_targets(ds_name):
 
 def get_dataset(dataset, regression=False, multigregression=False, one_hot=False):
     path = osp.join(osp.dirname(osp.realpath(__file__)), '..', 'datasets', dataset)
-    TUDataset(path, name=dataset, transform=)
+    TUDataset(path, name=dataset)
 
     if multigregression:
         return read_multi_targets(dataset)

### 2020-05-02 tud_benchmark/auxiliarymethods/evaluation.py
Added tolerance parameter to kernel SVM.

@@ -5,64 +5,18 @@ import os.path as osp
 import numpy as np
 import torch
 import torch.nn.functional as F
+from sklearn.linear_model import Ridge
+from sklearn.metrics import mean_absolute_error as mse
 from sklearn.model_selection import KFold
 from sklearn.model_selection import train_test_split
 from sklearn.svm import LinearSVC, SVC
 from torch_geometric.data import DataLoader
 from torch_geometric.datasets import TUDataset
-from sklearn.linear_model import SGDRegressor, Ridge
-from sklearn.kernel_ridge import KernelRidge
-from sklearn.metrics import mean_absolute_error as mse
 
 
 # Return arg max of iterable, e.g., a list.
 def argmax(iterable):
     return max(enumerate(iterable), key=lambda x: x[1])[0]
-
-
-# TODO: Check this.
-def ridge_regressor_evaluation(all_feature_matrices, targets, train_index, val_index, test_index, num_repetitions=5,
-                               alpha=[0.01, 0.1, 1.0, 2.0], std=None):
-    # Acc. over all repetitions.
-    test_accuracies = []
-
-    for _ in range(num_repetitions):
-
-        val_accuracies = []
-        models = []
-        for f in all_feature_matrices:
-
-            train = f[train_index]
-            val = f[val_index]
-
-            c_train = targets[train_index]
-            c_val = targets[val_index]
-
-            for a in alpha:
-                clf = Ridge(alpha=a, solver="sag", max_iter=5000, random_state=np.random.RandomState())
-                clf.fit(train, c_train)
-                p = clf.predict(val)
-                r = mse(c_val, p)
-
-                models.append(clf)
-                val_accuracies.append(r)
-
-        best_i = argmax(val_accuracies)
-        best_model = models[best_i]
-
-        # Eval. model on test split that performed best on val. split.
-        test = all_feature_matrices[int(best_i / len(alpha))][test_index]
-        c_test = targets[test_index]
-        p = best_model.predict(test)
-
-        # print(c_test.shape, std.shape)
-
-        # a = mse(c_test * std, p * std, multioutput='uniform_average')
-        a = mse(c_test, p, multioutput='uniform_average')
-        test_accuracies.append(a)
-    print(test_accuracies)
-    return (np.array(test_accuracies).mean(), np.array(test_accuracies).std())
-
 
 # 10-CV for linear svm with sparse feature vectors and hyperparameter selection.
[…]

### 2020-05-02 tud_benchmark/main.py

@@ -11,148 +11,6 @@ import numpy as np
 
 
 def main():
-    # classes = dp.get_dataset("Tox21_AhR_training")
-    #
-    # print(sum(classes)/len(classes))
-    #
-    #
-    # # all_matrices = []
-    # # for i in range(4, 5):
-    # #     print(i)
-    # #     gm = kb.compute_wl_1_dense("Tox21_AhR_training", i, True, True)
-    # #     gm_n = aux.normalize_gram_matrix(gm)
-    # #     all_matrices.append(gm_n)
-    # # print("###")
-    # # print(kernel_svm_evaluation(all_matrices, classes, num_repetitions=1, all_std=True))
-    #
-    # all_matrices = []
-    # for i in range(4, 5):
-    #     print(i)
-    #     gm = kb.compute_lwlp_2_dense("Tox21_AhR_training", i, True, True)
-    #     gm_n = aux.normalize_gram_matrix(gm)
-    #     all_matrices.append(gm_n)
-    # print("###")
-    # print(kernel_svm_evaluation(all_matrices, classes, num_repetitions=1, all_std=True))
-
-    # indices_train = []
-    # indices_val = []
-    # indices_test = []
-    #
-    # infile = open("datasets/test_al_10.index", "r")
-    # for line in infile:
-    #     indices_test = line.split(",")
-    #     indices_test = [int(i) for i in indices_test]
-    #
-    # infile = open("datasets/val_al_10.index", "r")
-    # for line in infile:
-    #     indices_val = line.split(",")
-    #     indices_val = [int(i) for i in indices_val]
-    #
-    # infile = open("datasets/train_al_10.index", "r")
-    # for line in infile:
-    #     indices_train = line.split(",")
-    #     indices_train = [int(i) for i in indices_train]
-    #
-    #
-    # targets = dp.get_dataset("alchemy_full", multigregression=True)
-    # targets = targets[:, 1:]
-    #
-    # # mean = np.mean(targets, axis=0, keepdims=True)
-    # # std = np.std(targets, axis=0, keepdims=True)
-    # # targets = (targets - mean) / std
-    #
-    # print(targets.shape)
-    #
-    # tmp1 = targets[indices_train].tolist()
-    # tmp2 = targets[indices_val].tolist()
-    # tmp3 = targets[indices_test].tolist()
-    # targets = tmp1
-    # targets.extend(tmp2)
-    # targets.extend(tmp3)
-    # targets = np.array(targets)
[…]

### 2020-05-02 tud_benchmark/main_old.py

@@ -1,0 +1,226 @@
+from __future__ import division
+from auxiliarymethods.evaluation import kernel_svm_evaluation, linear_svm_evaluation
+
+from sklearn.model_selection import train_test_split
+from sklearn.metrics import mean_absolute_error as mse
+import kernel_baselines as kb
+import auxiliarymethods.auxiliary_methods as aux
+import auxiliarymethods.datasets as dp
+from sklearn.preprocessing import StandardScaler
+import numpy as np
+
+
+def main():
+    # classes = dp.get_dataset("Tox21_AhR_training")
+    #
+    # print(sum(classes)/len(classes))
+    #
+    #
+    # # all_matrices = []
+    # # for i in range(4, 5):
+    # #     print(i)
+    # #     gm = kb.compute_wl_1_dense("Tox21_AhR_training", i, True, True)
+    # #     gm_n = aux.normalize_gram_matrix(gm)
+    # #     all_matrices.append(gm_n)
+    # # print("###")
+    # # print(kernel_svm_evaluation(all_matrices, classes, num_repetitions=1, all_std=True))
+    #
+    # all_matrices = []
+    # for i in range(4, 5):
+    #     print(i)
+    #     gm = kb.compute_lwlp_2_dense("Tox21_AhR_training", i, True, True)
+    #     gm_n = aux.normalize_gram_matrix(gm)
+    #     all_matrices.append(gm_n)
+    # print("###")
+    # print(kernel_svm_evaluation(all_matrices, classes, num_repetitions=1, all_std=True))
+
+    # indices_train = []
+    # indices_val = []
+    # indices_test = []
+    #
+    # infile = open("datasets/test_al_10.index", "r")
+    # for line in infile:
+    #     indices_test = line.split(",")
+    #     indices_test = [int(i) for i in indices_test]
+    #
+    # infile = open("datasets/val_al_10.index", "r")
+    # for line in infile:
+    #     indices_val = line.split(",")
+    #     indices_val = [int(i) for i in indices_val]
+    #
+    # infile = open("datasets/train_al_10.index", "r")
+    # for line in infile:
+    #     indices_train = line.split(",")
+    #     indices_train = [int(i) for i in indices_train]
+    #
+    #
+    # targets = dp.get_dataset("alchemy_full", multigregression=True)
+    # targets = targets[:, 1:]
+    #
+    # # mean = np.mean(targets, axis=0, keepdims=True)
+    # # std = np.std(targets, axis=0, keepdims=True)
[…]

### 2020-05-03 tud_benchmark/main.py
Corrected Graphlet kernel.

@@ -12,6 +12,8 @@ def main():
     dataset = [["ENZYMES", True], ["IMDB-BINARY", False], ["IMDB-MULTI", False], ["NCI1", True], ["PROTEINS", True],
                  ["REDDIT-BINARY", False]]
 
+    results = []
+
     for d, use_labels in dataset:
         dataset = d
         classes = dp.get_dataset(dataset)
@@ -23,7 +25,8 @@ def main():
             gm_n = aux.normalize_gram_matrix(gm)
             all_matrices.append(gm_n)
         print("###")
-        print(kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True))
+        acc, s_1, s_2 = kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True)
+        results.append(d + " " + "WL1 " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "LWL2")
         all_matrices = []
@@ -32,7 +35,8 @@ def main():
             gm_n = aux.normalize_gram_matrix(gm)
             all_matrices.append(gm_n)
         print("###")
-        print(kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True))
+        acc, s_1, s_2 = kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True)
+        results.append(d + " " + "LWL2 " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "LWLP2")
         all_matrices = []
@@ -41,7 +45,8 @@ def main():
             gm_n = aux.normalize_gram_matrix(gm)
             all_matrices.append(gm_n)
         print("###")
-        print(kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True))
+        acc, s_1, s_2 = kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True)
+        results.append(d + " " + "LWLP2 " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "WLOA")
         all_matrices = []
@@ -50,7 +55,8 @@ def main():
             gm_n = aux.normalize_gram_matrix(gm)
             all_matrices.append(gm_n)
         print("###")
-        print(kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True))
[…]

### 2020-05-03 tud_benchmark/main.py
Corrected Graphlet kernel.

@@ -102,7 +102,7 @@ def main():
         print("###")
         acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=False,
                                     max_iterations=-1)
-        results.append(d + " " + "SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
+        results.append(d + " " + "WL1 " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "LWL2")
         all_matrices = []
@@ -113,7 +113,7 @@ def main():
         print("###")
         acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=False,
                                     max_iterations=-1)
-        results.append(d + " " + "SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
+        results.append(d + " " + "LWL2 " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "LWLP2")
         all_matrices = []
@@ -124,7 +124,7 @@ def main():
         print("###")
         acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=False,
                                     max_iterations=-1)
-        results.append(d + " " + "SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
+        results.append(d + " " + "LWLP2 " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "GR")
         all_matrices = []
@@ -134,7 +134,7 @@ def main():
         print("###")
         acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=False,
                                     max_iterations=-1)
-        results.append(d + " " + "SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
+        results.append(d + " " + "GR " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "SP")
         all_matrices = []

### 2020-05-03 tud_benchmark/main.py
Corrected Graphlet kernel.

@@ -102,6 +102,7 @@ def main():
         print("###")
         acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=False,
                                     max_iterations=-1)
+        print(d + " " + "WL1 " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "WL1 " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "LWL2")
@@ -113,6 +114,7 @@ def main():
         print("###")
         acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=False,
                                     max_iterations=-1)
+        print(d + " " + "LWL2 " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "LWL2 " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "LWLP2")
@@ -124,6 +126,7 @@ def main():
         print("###")
         acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=False,
                                     max_iterations=-1)
+        print(d + " " + "LWLP2 " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "LWLP2 " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "GR")
@@ -134,6 +137,7 @@ def main():
         print("###")
         acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=False,
                                     max_iterations=-1)
+        print(d + " " + "LWLP2 " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GR " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "SP")
@@ -144,6 +148,7 @@ def main():
         print("###")
         acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True, primal=False,
                                     max_iterations=-1)
+        print(d + " " + "SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
     for r in results:

### 2020-05-03 tud_benchmark/main.py
Corrected Graphlet kernel.

@@ -26,6 +26,7 @@ def main():
             all_matrices.append(gm_n)
         print("###")
         acc, s_1, s_2 = kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True)
+        print(d + " " + "WL1 " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "WL1 " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "LWL2")
@@ -36,6 +37,7 @@ def main():
             all_matrices.append(gm_n)
         print("###")
         acc, s_1, s_2 = kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True)
+        print(d + " " + "LWL2 " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "LWL2 " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "LWLP2")
@@ -46,6 +48,7 @@ def main():
             all_matrices.append(gm_n)
         print("###")
         acc, s_1, s_2 = kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True)
+        print(d + " " + "LWLP2 " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "LWLP2 " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "WLOA")
@@ -56,6 +59,7 @@ def main():
             all_matrices.append(gm_n)
         print("###")
         acc, s_1, s_2 = kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True)
+        print(d + " " + "WLOA " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "WLOA " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "GR")
@@ -65,6 +69,7 @@ def main():
         all_matrices.append(gm_n)
         print("###")
         acc, s_1, s_2 = kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True)
+        print(d + " " + "GR " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GR " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         print(d + " " + "SP")
[…]

### 2020-05-03 main.tex
Minor changes in text throughout.
Added tolerance parameter to kernel SVM.
Corrected Graphlet kernel.
Kernel evaluation script.

@@
 \icmlauthor{N.\,M.\,Kriege}{vie}
+\icmlauthor{Franka Bause}{vie}
 \icmlauthor{K. Kersting}{darm}
@@
 \begin{abstract}
-Recently, there has been an increasing interest in learning with graph data, especially using graph neural networks.
+Recently, there has been an increasing interest in (supervised) learning with graph data, especially using graph neural networks.
 However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging.
@@
 The dataset consists of over 120 datasets from a wide range of applications and varying sizes.
-We provide Python-based data loaders, baseline method implementations, and evaluation tools.
+We provide Python-based data loaders, kernel and graph neural network baseline methods implementations, and evaluation tools.
 Here, we give an overview of the datasets, evaluation tools, and provide baseline experiments.
@@
 \cm{Mention \textsc{ZINC} and the also mention size of DS, 200k}
+\cm{Mention \textsc{QM9}k}
 
@@
 Too compute accuracies and MAE, we propose to use $10$-fold cross-validation, where we select a validation set uniformly at random from each training fold ($10\%$ of the training fold), to select hyperparameters, e.g., number of iterations, $C$ parameter, number of layers, feature dimension, dots Moreover, we repeat the above evaluation ten times and report standard deviations over all ten repetitions, and additionally across all one hundred runs (i.e., ten repetitions with ten folds each.).
+See the appendix for examples balbalb
 
@@
 \textsc{Reddit-Binary},	\textsc{reddit\_threads}, \textsc{twitch\_egos}, \textsc{Uacc257}. See the website for dataset statistics.
+\cm{ZINC ALche}
 
@@
 For the larger datasets, we computed sparse feature vectors for each graph and used the linear $C$-SVM implementation of \text{Liblinear}~\cite{Fan+2008}.
-The number of iterations of the \textsc{$1$-WL}, \textsc{WL-OA}, and the  $\delta$-$2$-LWL$^+$ were selected from $\{0,\dotsc,5\}$.\footnote{As already shown in~\cite{She+2011}, choosing the number of iterations too large will lead to overfitting.}
+The number of iterations of the \textsc{$1$-WL}, \textsc{WL-OA}, and the  $\delta$-$2$-LWL$^+$ were selected from $\{0,\dotsc,5\}$.\footnote{As already shown in~\cite{She+2011}, choosing the number of iterations too large will lead to overfitting.}\cm{Cite sklearn}
 
@@
 For each dataset, we optimize the number of hidden units from $
-\{16, 32, 64, 128\}$, the number of layers from $ \{2, 3, 4, 5\}$ and the learning rate from $ \{0.0001, 0.001, 0.01 \}$ with respect to the validation set. The batch size was fixed to $128$.
+\{16, 32, 64, 128\}$, the number of layers from $ \{2, 3, 4, 5\}$ and the learning rate from $ \{0.0001, 0.001, 0.01 \}$ with respect to the validation set.
+The batch size was fixed to $128$.\cm{change this }
 
@@
 			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule
-			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &  50.1  \scriptsize $\pm 1.6 \pm 6.2 $       & 72.4 \scriptsize $\pm  0.5 \pm 4.0$ & 50.1  \scriptsize $\pm 0.5 \pm  3.8 $ & 84.3 \scriptsize $\pm 0.3 \pm 1.6$ &73.0  \scriptsize $\pm 0.8 \pm  4.2 $ & 72.6 \scriptsize $\pm  0.4 \pm 3.1$  \\
-				& \text{WLOA} & 56.8  \scriptsize $\pm  1.7\pm6.4 $       & 72.7  \scriptsize $\pm 0.7 \pm 4.3$ & 49.5 \scriptsize $\pm  0.4 \pm  3.5 $ & 84.9 \scriptsize $\pm  0.4 \pm 1.7$ &73.4  \scriptsize $\pm 0.7 \pm 3.7$ & 88.1 \scriptsize $\pm 0.3 \pm 2.5 $   \\
-				& \text{GR}            &  31.9   \scriptsize $\pm 1.1 \pm4.8$       & 59.4  \scriptsize $\pm 0.4 \pm 4.6$ & 39.3 \scriptsize $\pm 0.8 \pm  4.1 $ & 58.7  \scriptsize $\pm 0.4 \pm 2.3$ & 69.0  \scriptsize $\pm 0.8 \pm 4.3$ &60.0  \scriptsize $\pm 0.2 \pm 3.2 $   \\
-				& \text{SP}            &  40.6 \scriptsize $\pm  1.8\pm 5.8 $       & 58.3  \scriptsize $\pm 0.8 \pm  4.9$ & 39.0 \scriptsize $\pm 0.5 \pm  3.8$ &  74.1  \scriptsize $\pm 0.5 \pm 2.0 $  & 75.4  \scriptsize $\pm 0.5 \pm 4.1$ & 84.6 \scriptsize $\pm 0.3 \pm 2.5 $  \\
+			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &    \scriptsize $\pm  \pm  $       & \scriptsize $\pm   \pm $ &  \scriptsize $\pm  \pm   $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm  \pm   $ & \scriptsize $\pm  \pm $  \\
+				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+				& \text{WLOA} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+				& \text{GR}            &     \scriptsize $\pm  \pm$       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm   $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm $ & \scriptsize $\pm  \pm  $   \\
+				& \text{SP}            &   \scriptsize $\pm  \pm $       &  \scriptsize $\pm  \pm  $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm \pm  $  & \scriptsize $\pm  \pm $ &  \scriptsize $\pm\pm $  \\
 			\cmidrule{2-8}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GIN-$\varepsilon$}    &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $    \\
-		& \text{Sage}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $  \\
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GIN-$\varepsilon$}    & \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+		& \text{GraphSage} &          \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
 			\bottomrule
@@
 			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Triangles}}           & {\textsc{github\_stargazers}}       & {\textsc{reddit\_threads}}      \\	\toprule
-							\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 94.23 
-							   \scriptsize $\pm 0.11  \pm 0.49$       & 94.29 \scriptsize $\pm 0.07  \pm 0.39$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\
+							\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
+							   \scriptsize $\pm   \pm $       & \scriptsize $\pm   \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\
 
-			& \text{GR}            &  91.71 \scriptsize $\pm  0.04   \pm 0.52 $       & 92.10  \scriptsize $\pm 0.02 \pm 0.45$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\  
-			& \text{SP}             &   91.73 \scriptsize $\pm 0.03  \pm 0.49$       & 92.05 \scriptsize $\pm 0.02 \pm 0.44 $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\   
+			& \text{GR}            &   \scriptsize $\pm    \pm  $       &   \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\  
+			& \text{SP}             &    \scriptsize $\pm  \pm $       &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\   
 			\cmidrule{2-7}	
 			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GIN-E-$\varepsilon$}         &    \scriptsize $\pm  \pm $       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ \\
-			& \text{Sage}            &    \scriptsize $\pm \pm$       & \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm $  \\
+			& \text{GraphSage}            &    \scriptsize $\pm \pm$       & \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm $  \\
 			\bottomrule
@@
 			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{2}{c}{\textbf{Dataset}}\\\cmidrule{3-4}
-			&  & {\textsc{Zinc} (10k)}         &  {\textsc{Zinc} (50k)}         \\	
+			&  & {\textsc{Zinc}}         &  {\textsc{Alchemy}}         \\	
 			\toprule
-			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}             &      \scriptsize $<\!0.000$ &  \scriptsize $ <\!0.000$  \\  
-				& \text{GR}            &\scriptsize $ <\!0.000$ &  \scriptsize $ <\!0.000$  \\  
-			& \text{SP}             &   \scriptsize $ <\!0.000$  &  \scriptsize $ <\!0.000$ \\   
+			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}             &      \scriptsize $$ &  \scriptsize $$  \\  
+				& \text{GR}            &\scriptsize $ $ &  \scriptsize $ $  \\  
+			& \text{SP}             &   \scriptsize $ $  &  \scriptsize $ $ \\   
 			\cmidrule{2-4}
-			\multirow{2}{*}{\rotatebox{90}{GNN}} & \text{$1$-GNN-E}             &  0.278 \scriptsize $\pm 0.022$  & 0.145 \scriptsize $\pm  0.006  $		\\	
-			& \text{$1$-GNN}             &  0.383 \scriptsize $\pm  0.020$    &  0.247 \scriptsize $\pm   0.020$ \\
+			\multirow{2}{*}{\rotatebox{90}{}} & \text{$1$-GNN-E}             &   \scriptsize $\pm $  & \scriptsize $\pm   $		\\	
 			\bottomrule

### 2020-05-03 tud_benchmark/auxiliarymethods/datasets.py
Kernel evaluation script.

@@ -43,125 +43,3 @@ def get_dataset(dataset, regression=False, multigregression=False, one_hot=False
         return read_classes(dataset)
     else:
         return read_targets(dataset)
-
-# TODO: Finsih this.
-# Return dataset as list of networkx graphs.
-def read_graphs_nx(ds_name):
-    pre = ""
-
-    with open("datasets/" + pre + ds_name + "/" + ds_name + "_graph_indicator.txt", "r") as f:
-        graph_indicator = [int(i) - 1 for i in list(f)]
-    f.closed
-
-    # Nodes
-    num_graphs = max(graph_indicator)
-    node_indices = []
-    offset = []
-    c = 0
-
-    for i in range(num_graphs + 1):
-        offset.append(c)
-        c_i = graph_indicator.count(i)
-        node_indices.append((c, c + c_i - 1))
-        c += c_i
-
-    graph_db = []
-    vertex_list = []
-    for i in node_indices:
-        # Undirected graph.
-        g = nx.Graph()
-        vertex_list_g = []
-
-        for n, _ in enumerate(range(i[1] - i[0] + 1)):
-            vertex_list_g.append(n)
-            g.add_node(n)
-
-        graph_db.append(g)
-        vertex_list.append(vertex_list_g)
-
-    # Edges
-    with open("datasets/" + pre + ds_name + "/" + ds_name + "_A.txt", "r") as f:
-        edges = [i.split(',') for i in list(f)]
-    f.closed
-
-    edges = [(int(e[0].strip()) - 1, int(e[1].strip()) - 1) for e in edges]
-
-    edge_indicator = []
-    edge_list = []
-    i = 0
-    for e in edges:
-        g_id = graph_indicator[e[0]]
-        edge_indicator.append(g_id)
-        g = graph_db[g_id]
-        off = offset[g_id]
-
-        # Avoid multigraph
-        if not g.has_edge(e[0] - off, e[1] - off):
-            g.add_edge(e[0] - off, e[1] - off)
-            edge_list.append(i)
-            i += 1
-    # Node labels
-    if path.exists("datasets/" + pre + ds_name + "/" + ds_name + "_node_labels.txt"):
-        with open("datasets/" + pre + ds_name + "/" + ds_name + "_node_labels.txt", "r") as f:
-            node_labels = [int(i) for i in list(f)]
-        f.closed
-
-        for g_id, g in enumerate(graph_db):
-            off = offset[g_id]
[…]

### 2020-05-03 tud_benchmark/main_gnn.py

@@ -1,23 +1,17 @@
 from __future__ import division
-from auxiliarymethods.evaluation import gnn_evaluation
-from gnn_baselines.gnn_architectures import GINWithJK, GraphSAGEWithJK
-from sklearn.linear_model import LinearRegression, Ridge, ElasticNet, SGDRegressor
 
-from sklearn.model_selection import train_test_split
-from sklearn.metrics import mean_absolute_error as mse
-import kernel_baselines as kb
-import auxiliarymethods.auxiliary_methods as aux
 import auxiliarymethods.datasets as dp
-from sklearn.preprocessing import StandardScaler
-import numpy as np
+from auxiliarymethods.gnn_evaluation import gnn_evaluation
+from gnn_baselines.gnn_architectures import GINWithJK, GraphSAGEWithJK
+
 
 # TODO: Add one-hot.
 
 def main():
     datasets = [
-        ["ENZYMES", True],
+        #["ENZYMES", True],
         # ["IMDB-BINARY", False], ["IMDB-MULTI", False],["REDDIT-BINARY", False]
-        ["NCI1", True],
+        #["NCI1", True],
         ["PROTEINS", True]]
 
     for d, use_labels in datasets:

### 2020-05-03 main.tex
Kernel evaluation script.

@@
 
+%\renewcommand*{\familydefault}{ttdefault}
+\usepackage{listings}
+\usepackage{setspace}
+\definecolor{Code}{rgb}{0,0,0}
+\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
+\definecolor{Numbers}{rgb}{0.5,0,0}
+\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
+\definecolor{Keywords}{rgb}{0,0,1}
+\definecolor{self}{rgb}{0,0,0}
+\definecolor{Strings}{rgb}{0,0.63,0}
+\definecolor{Comments}{rgb}{0,0.63,1}
+\definecolor{Backquotes}{rgb}{0,0,0}
+\definecolor{Classname}{rgb}{0,0,0}
+\definecolor{FunctionName}{rgb}{0,0,0}
+\definecolor{Operators}{rgb}{0,0,0}
+\definecolor{Background}{rgb}{0.98,0.98,0.98}
+\lstdefinelanguage{Python}{
+	numbers=left,
+	numberstyle=\footnotesize,
+	numbersep=1em,
+	xleftmargin=1em,
+	framextopmargin=2em,
+	framexbottommargin=2em,
+	showspaces=false,
+	showtabs=false,
+	showstringspaces=false,
+	frame=l,
+	tabsize=4,
+	% Basic
+	basicstyle=\ttfamily\small\setstretch{1},
+	backgroundcolor=\color{Background},
+	% Comments
+	commentstyle=\color{Comments}\slshape,
+	% Strings
+	stringstyle=\color{Strings},
+	morecomment=[s][\color{Strings}]{"""}{"""},
+	morecomment=[s][\color{Strings}]{'''}{'''},
+	% keywords
+	morekeywords={import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,None,access,as,,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert},
+	keywordstyle={\color{Keywords}\bfseries},
+	% additional keywords
+	morekeywords={[2]@invariant,pylab,numpy,np,scipy},
+	keywordstyle={[2]\color{Decorators}\slshape},
+	emph={self},
+	emphstyle={\color{self}\slshape},
+	%
+}
 \usepackage{icml2020}
@@
 
+\onecolumn
+\section{Evaluation Method Examples}
+\lstinputlisting[language=Python]{example.py}
+
 \end{document}

### 2020-05-03 example.py

@@ -1,0 +1,19 @@
+import kernel_baselines as kb
+import auxiliarymethods.auxiliary_methods as aux
+import auxiliarymethods.datasets as dp
+from auxiliarymethods.kernel_evaluation import kernel_svm_evaluation
+
+# Download datasets.
+classes = dp.get_dataset("ENZYMES")
+
+all_matrices = []
+for i in range(1, 6):
+    # Use node labels and no edge labels.
+    gm = kb.compute_wl_1_dense("ENZYMES", i, True, False)
+    # Apply cosine normalization.
+    gm = aux.normalize_gram_matrix(gm)
+    all_matrices.append(gm)
+
+# Perform 10 repetions of 10-CV using LIBSVM.
+print(kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True))
+

### 2020-05-03 tud_benchmark/auxiliarymethods/gnn_evaluation.py

@@ -16,7 +16,6 @@ def argmax(iterable):
     return max(enumerate(iterable), key=lambda x: x[1])[0]
 
 
-
 # One training epoch for GNN model.
 def train(train_loader, model, optimizer, device):
     model.train()
@@ -84,12 +83,14 @@ def gnn_evaluation(gnn, ds_name, layers, hidden, max_num_epochs=100, batch_size=
             # Sample 10% split from training split for validation.
             train_index, val_index = train_test_split(train_index, test_size=0.1)
 
-            test_dataset = dataset[test_index.tolist()]
-            val_dataset = dataset[val_index.tolist()]
             train_dataset = dataset[train_index.tolist()]
-            test_loader = DataLoader(test_dataset, batch_size=batch_size)
+            val_dataset = dataset[val_index.tolist()]
+            test_dataset = dataset[test_index.tolist()]
+
+
             train_loader = DataLoader(train_dataset, batch_size=batch_size)
             val_loader = DataLoader(val_dataset, batch_size=batch_size)
+            test_loader = DataLoader(test_dataset, batch_size=batch_size)
 
             # Collect val. and test acc. over all hyperparameter combinations.
             vals = []
@@ -98,7 +99,7 @@ def gnn_evaluation(gnn, ds_name, layers, hidden, max_num_epochs=100, batch_size=
                 for h in hidden:
                     model = gnn(dataset, l, h).to(device)
                     # Reset parameters before each run.
-                    model.reset_parameters()
+                    #model.reset_parameters()
 
                     optimizer = torch.optim.Adam(model.parameters(), lr=start_lr)
                     scheduler = torch.optim.lr_scheduler.ReduceLROnPlateau(optimizer, mode='min',

### 2020-05-03 tud_benchmark/main_gnn.py

@@ -12,10 +12,18 @@ def main():
         #["ENZYMES", True],
         # ["IMDB-BINARY", False], ["IMDB-MULTI", False],["REDDIT-BINARY", False]
         #["NCI1", True],
-        ["PROTEINS", True]]
+        ["NCI1", True]]
 
     for d, use_labels in datasets:
+
         classes = dp.get_dataset(d)
+
+        results = gnn_evaluation(GINWithJK, d, [2], [64], max_num_epochs=50, batch_size=32, start_lr=0.01,
+                                 num_repetitions=1,
+                                 all_std=True)
+        print(results)
+        exit()
+
 
         results = gnn_evaluation(GINWithJK, d, [1, 2, 3, 4, 5], [16, 32, 64, 128], max_num_epochs=200, batch_size=32, start_lr=0.01,
                                  num_repetitions=10,

### 2020-05-03 tud_benchmark/auxiliarymethods/gnn_evaluation.py
GNN baseline:   + Added one-hot degree when node labels are given.

@@ -5,16 +5,29 @@ import os.path as osp
 import numpy as np
 import torch
 import torch.nn.functional as F
+import torch_geometric.transforms as T
 from sklearn.model_selection import KFold
 from sklearn.model_selection import train_test_split
 from torch_geometric.data import DataLoader
 from torch_geometric.datasets import TUDataset
+from torch_geometric.utils import degree
 
 
 # Return arg max of iterable, e.g., a list.
 def argmax(iterable):
     return max(enumerate(iterable), key=lambda x: x[1])[0]
 
+
+class NormalizedDegree(object):
+    def __init__(self, mean, std):
+        self.mean = mean
+        self.std = std
+
+    def __call__(self, data):
+        deg = degree(data.edge_index[0], dtype=torch.float)
+        deg = (deg - self.mean) / self.std
+        data.x = deg.view(-1, 1)
+        return data
 
 # One training epoch for GNN model.
 def train(train_loader, model, optimizer, device):
@@ -69,6 +82,21 @@ def gnn_evaluation(gnn, ds_name, layers, hidden, max_num_epochs=100, batch_size=
     # Load dataset.
     path = osp.join(osp.dirname(osp.realpath(__file__)), '..', 'datasets', ds_name)
     dataset = TUDataset(path, name=ds_name).shuffle()
+
+    if dataset.data.x is None:
+        max_degree = 0
+        degs = []
+        for data in dataset:
+            degs += [degree(data.edge_index[0], dtype=torch.long)]
+            max_degree = max(max_degree, degs[-1].max().item())
+
+        if max_degree < 1000:
+            dataset.transform = T.OneHotDegree(max_degree)
+        else:
+            deg = torch.cat(degs, dim=0).to(torch.float)
+            mean, std = deg.mean().item(), deg.std().item()
+            dataset.transform = NormalizedDegree(mean, std)
+
     device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
     test_accuracies_all = []
@@ -87,7 +115,6 @@ def gnn_evaluation(gnn, ds_name, layers, hidden, max_num_epochs=100, batch_size=
             val_dataset = dataset[val_index.tolist()]
             test_dataset = dataset[test_index.tolist()]
 
-
             train_loader = DataLoader(train_dataset, batch_size=batch_size)
             val_loader = DataLoader(val_dataset, batch_size=batch_size)
             test_loader = DataLoader(test_dataset, batch_size=batch_size)
[…]

### 2020-05-03 tud_benchmark/main_gnn.py

@@ -14,26 +14,14 @@ def main():
         #["NCI1", True],
         ["NCI1", True]]
 
-    for d, use_labels in datasets:
+    d = "IMDB-BINARY"
+    dp.get_dataset(d)
 
-        classes = dp.get_dataset(d)
-
-        results = gnn_evaluation(GINWithJK, d, [2], [64], max_num_epochs=50, batch_size=32, start_lr=0.01,
-                                 num_repetitions=1,
-                                 all_std=True)
-        print(results)
-        exit()
+    results = gnn_evaluation(GINWithJK, d, [4], [64], max_num_epochs=50, batch_size=32, start_lr=0.001, num_repetitions=1, all_std=True)
+    print(results)
 
 
-        results = gnn_evaluation(GINWithJK, d, [1, 2, 3, 4, 5], [16, 32, 64, 128], max_num_epochs=200, batch_size=32, start_lr=0.01,
-                                 num_repetitions=10,
-                                 all_std=True)
-        print(results)
 
-        results = gnn_evaluation(GraphSAGEWithJK, d, [1, 2, 3, 4, 5], [16, 32, 64, 128], max_num_epochs=200,
-                                 batch_size=32, start_lr=0.01, num_repetitions=10,
-                                 all_std=True)
-        print(results)
 
     print(results)
 

### 2020-05-03 tud_benchmark/auxiliarymethods/gnn_evaluation.py
GNN baseline:   + Added one-hot degree when node labels are given.

@@ -83,6 +83,7 @@ def gnn_evaluation(gnn, ds_name, layers, hidden, max_num_epochs=100, batch_size=
     path = osp.join(osp.dirname(osp.realpath(__file__)), '..', 'datasets', ds_name)
     dataset = TUDataset(path, name=ds_name).shuffle()
 
+    # One-hot degree if node labels are not available.
     if dataset.data.x is None:
         max_degree = 0
         degs = []
@@ -136,6 +137,9 @@ def gnn_evaluation(gnn, ds_name, layers, hidden, max_num_epochs=100, batch_size=
                     val_acc, test_acc = train_model(train_loader, val_loader, test_loader, model, optimizer, scheduler,
                                                     device,
                                                     max_num_epochs)
+                    print(l, h)
+                    print(val_acc, test_acc)
+
                     vals.append(val_acc)
                     tests.append(test_acc)
 

### 2020-05-04 tud_benchmark/main_gnn.py
Work on GNN evaluation code. ++

@@ -8,7 +8,7 @@ from gnn_baselines.gnn_architectures import GIN
 def main():
 
 
-    d = "ENZYMES"
+    d = "IMDB-BINARY"
     dp.get_dataset(d)
 
     results = gnn_evaluation(GIN, d, [2,3,5,6], [32,64,128], max_num_epochs=100, batch_size=128, start_lr=0.01, num_repetitions=1, all_std=True)

### 2020-05-04 tud_benchmark/auxiliarymethods/gnn_evaluation.py
Work on GNN evaluation code. ++

@@ -82,9 +82,9 @@ def gnn_evaluation(gnn, ds_name, layers, hidden, max_num_epochs=100, batch_size=
     test_accuracies_complete = []
 
     for i in range(num_repetitions):
-        kf = KFold(n_splits=10, shuffle=True)
         # Test acc. over all folds.
         test_accuracies = []
+        kf = KFold(n_splits=10, shuffle=True)
 
         for train_index, test_index in kf.split(list(range(len(dataset)))):
             # Sample 10% split from training split for validation.
@@ -117,11 +117,11 @@ def gnn_evaluation(gnn, ds_name, layers, hidden, max_num_epochs=100, batch_size=
                     for epoch in range(1, max_num_epochs + 1):
                         lr = scheduler.optimizer.param_groups[0]['lr']
                         train(train_loader, model, optimizer, device)
-                        val_error = test(val_loader, model, device)
-                        scheduler.step(val_error)
+                        val_acc = test(val_loader, model, device)
+                        scheduler.step(val_acc)
 
-                        if val_error > best_val_acc:
-                            best_val_acc = val_error
+                        if val_acc > best_val_acc:
+                            best_val_acc = val_acc
                             best_test = test(test_loader, model, device)
 
                         # Break if learning rate is smaller 10**-6.

### 2020-05-04 tud_benchmark/auxiliarymethods/kernel_evaluation.py

@@ -19,7 +19,7 @@ def linear_svm_evaluation(all_feature_matrices, classes, num_repetitions=10,
         kf = KFold(n_splits=10, shuffle=True)
 
         for train_index, test_index in kf.split(list(range(len(classes)))):
-            # Sample 10% for validation.
+            # Sample 10% split from training split for validation.
             train_index, val_index = train_test_split(train_index, test_size=0.1)
             best_val_acc = 0.0
             best_test = 0.0

### 2020-05-04 tud_benchmark/main_gnn.py

@@ -11,7 +11,7 @@ def main():
     d = "IMDB-BINARY"
     dp.get_dataset(d)
 
-    results = gnn_evaluation(GIN, d, [2,3,5,6], [32,64,128], max_num_epochs=100, batch_size=128, start_lr=0.01, num_repetitions=1, all_std=True)
+    results = gnn_evaluation(GIN, d, [2,3,4], [64], max_num_epochs=100, batch_size=128, start_lr=0.01, num_repetitions=1, all_std=True)
     print(results)
 
     print(results)

### 2020-05-04 tud_benchmark/auxiliarymethods/gnn_evaluation.py
Work on GNN evaluation code. ++

@@ -123,6 +123,7 @@ def gnn_evaluation(gnn, ds_name, layers, hidden, max_num_epochs=100, batch_size=
                         if val_acc > best_val_acc:
                             best_val_acc = val_acc
                             best_test = test(test_loader, model, device)
+                            print(best_test)
 
                         # Break if learning rate is smaller 10**-6.
                         if lr < 0.000001:

### 2020-05-04 tud_benchmark/auxiliarymethods/gnn_evaluation.py
Work on GNN evaluation code. ++

@@ -123,12 +123,12 @@ def gnn_evaluation(gnn, ds_name, layers, hidden, max_num_epochs=100, batch_size=
                         if val_acc > best_val_acc:
                             best_val_acc = val_acc
                             best_test = test(test_loader, model, device)
-                            print(best_test)
+
 
                         # Break if learning rate is smaller 10**-6.
                         if lr < 0.000001:
                             break
-
+            print(best_test)
             test_accuracies.append(best_test)
 
             if all_std:

### 2020-05-09 main.tex
Work on GNN evaluation code. ++
MC.

@@
 			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GIN-$\varepsilon$}    & \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-		& \text{GraphSage} &          \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+		& \text{GIN-$\varepsilon$-JK} &          \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
 			\bottomrule
@@
 \end{table*}
+
+eintragen
+IMDB-BINARY GINWithJK 72.93333333333334 0.5185449728701322 4.122566622330749
+IMDB-BINARY GIN 72.06666666666668 0.3091206165165233 4.024370206076419
+IMDB-MULTI GINWithJK 50.644444444444446 1.01153837126587 4.59462917806765
+IMDB-MULTI GIN 48.84444444444444 0.37051848890073463 3.523185988018918
+NCI1 GINWithJK 79.67558799675588 0.4130683399269047 1.5714739782362184
+NCI1 GIN 78.01297648012977 0.38333502994634977 1.9142541830162463
+PROTEINS GINWithJK 71.27895752895752 0.9574183044143284 4.459876910576175
+PROTEINS GIN 71.16527241527241 0.3211668436757545 3.612551907408368
+REDDIT-BINARY GINWithJK 90.31666666666668 0.4326918328582383 1.9894862541760765
+
+REDDIT-BINARY GIN 90.18333333333334 0.39228674319799567 2.169805418823438
+
+ENZYMES WL1 50.28333333333334 1.1524129275375015 6.872065030089411
+ENZYMES LWL2 55.6 1.5709162223930901 6.788552455748164
+ENZYMES LWLP2 53.55 1.5402921800749356 6.3274314606235675
+ENZYMES WLOA 56.7 2.0094222497468714 7.129671957546308
+ENZYMES GR 32.35 1.036688102672266 5.359804100897718
+ENZYMES SP 39.8 1.2840906856172143 6.473364229243128
+IMDB-BINARY WL1 72.57 0.9143850392476894 4.133412633647891
+IMDB-BINARY LWL2 73.37 0.6372597586541924 4.430925411243119
+IMDB-BINARY LWLP2 76.65 1.353698637068088 4.924175057814253
+IMDB-BINARY WLOA 72.69 0.6818357573492301 4.749094650562357
+IMDB-BINARY GR 59.19 0.865390085452797 5.017359863513877
+IMDB-BINARY SP 57.860000000000014 1.4291256067959874 5.734143353631822
+IMDB-MULTI WL1 50.09333333333333 0.6262409901769259 3.811118237764636
+IMDB-MULTI LWL2 50.15333333333333 0.38418745424597134 4.055016098063676
+
+IMDB-MULTI LWLP2 74.01333333333334 0.9360911636516311 4.502818870194288
+IMDB-MULTI WLOA 49.86666666666666 0.6352602266438174 4.455209185760966
+IMDB-MULTI GR 39.17333333333333 0.7660577291852385 4.380887784202853
+IMDB-MULTI SP 39.50666666666666 0.18184242262647857 3.3791780723194287
+NCI1 WL1 84.38929440389293 0.25125704415427325 1.6049986739634532
+NCI1 LWL2 84.89537712895375 0.20028336376892103 1.7608176856505284
+NCI1 LWLP2 84.32846715328466 0.35931558467907326 1.9074851647350406
+NCI1 WLOA 84.985401459854 0.26237917572915365 1.944431716559596
+NCI1 GR 65.8272506082725 0.31011161731748405 2.3057620215984294
+NCI1 SP 74.21411192214111 0.26335881513838716 2.007846272147655
+PROTEINS WL1 73.49348455598457 0.6459030975700468 4.234672201391122
+PROTEINS LWL2 74.79681467181469 0.665180097352863 4.60334576380455
+PROTEINS LWLP2 75.63296332046333 0.5832232093036747 4.118575468095003
+PROTEINS WLOA 73.48656692406692 0.6497356451647441 4.4435644964869745
+PROTEINS GR 71.91473616473615 0.5582152728034838 4.153766329154282
+PROTEINS SP 75.29930823680823 0.433922307671726 3.6869730552272064
+REDDIT-BINARY WL1 73.15 0.5860887304837047 3.1547583108694712
+REDDIT-BINARY LWL2 89.09 0.4856953777832335 2.504376169827528
 
@@
 \lstinputlisting[language=Python]{example.py}
+\cm{Add linear svm and GNN example}
 

### 2020-05-09 tud_benchmark/main_kernel.py

@@ -75,7 +75,7 @@ def main():
 
     dataset = [["MOLT-4", True, True], ["TRIANGLES", False, False], ["MCF-7", True, True],
                  ["github_stargazers", False, False],
-                 ["reddit_threads", False, False], ]
+                 ["reddit_threads", False, False]]
 
     for d, use_labels, use_edge_labels in dataset:
         print(d)

### 2020-05-09 main.tex
MC.

@@
 
-eintragen
+Bitte eintragen
 IMDB-BINARY GINWithJK 72.93333333333334 0.5185449728701322 4.122566622330749

### 2020-05-09 tud_benchmark/main_kernel.py

@@ -109,13 +109,13 @@ def main():
         # print(d + " " + "LWLP2SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
         # results.append(d + " " + "LWLP2SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
-        all_matrices = []
-        gm = kb.compute_graphlet_sparse(dataset, use_labels, use_edge_labels)
-        gm_n = aux.normalize_feature_vector(gm)
-        all_matrices.append(gm_n)
-        acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=num_reps, all_std=True)
-        print(d + " " + "GRSP " + str(acc) + " " + str(s_1) + " " + str(s_2))
-        results.append(d + " " + "GRSP " + str(acc) + " " + str(s_1) + " " + str(s_2))
+        # all_matrices = []
+        # gm = kb.compute_graphlet_sparse(dataset, use_labels, use_edge_labels)
+        # gm_n = aux.normalize_feature_vector(gm)
+        # all_matrices.append(gm_n)
+        # acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=num_reps, all_std=True)
+        # print(d + " " + "GRSP " + str(acc) + " " + str(s_1) + " " + str(s_2))
+        # results.append(d + " " + "GRSP " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         all_matrices = []
         gm = kb.compute_shortestpath_sparse(dataset, use_labels)

### 2020-05-10 main.tex
Fixed GNN evaluation.

--- 2020-05-09 main.tex
@@
 REDDIT-BINARY GINWithJK 90.31666666666668 0.4326918328582383 1.9894862541760765
-
 REDDIT-BINARY GIN 90.18333333333334 0.39228674319799567 2.169805418823438

### 2020-05-10 tud_benchmark/auxiliarymethods/gnn_evaluation.py

@@ -123,7 +123,6 @@ def gnn_evaluation(gnn, ds_name, layers, hidden, max_num_epochs=200, batch_size=
                             best_val_acc = val_acc
                             best_test = test(test_loader, model, device)*100.0
 
-
                         # Break if learning rate is smaller 10**-6.
                         if lr < 0.000001:
                             break

### 2020-05-10 tud_benchmark/main_gnn.py

@@ -87,7 +87,7 @@ def main():
         print(d + " " + "GINEWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GINWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
-        acc, s_1, s_2 = gnn_evaluation(GINE, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200, batch_size=128,
+        acc, s_1, s_2 = gnn_evaluation(GINE, d, [2, 3, 4, 5], [64, 128], max_num_epochs=100, batch_size=128,
                                        start_lr=0.01,
                                        num_repetitions=num_reps, all_std=True)
         print(d + " " + "GINE " + str(acc) + " " + str(s_1) + " " + str(s_2))

### 2020-05-10 tud_benchmark/main_gnn.py
Fixed GNN evaluation.

@@ -81,7 +81,7 @@ def main():
     for d, use_labels in dataset:
         dp.get_dataset(d)
 
-        acc, s_1, s_2 = gnn_evaluation(GINEWithJK, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200,
+        acc, s_1, s_2 = gnn_evaluation(GINEWithJK, d, [2, 3, 4, 5], [64, 128], max_num_epochs=100,
                                        batch_size=128, start_lr=0.01,
                                        num_repetitions=num_reps, all_std=True)
         print(d + " " + "GINEWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
@@ -102,13 +102,13 @@ def main():
     for d, use_labels in dataset:
         dp.get_dataset(d)
 
-        acc, s_1, s_2 = gnn_evaluation(GINWithJK, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200,
+        acc, s_1, s_2 = gnn_evaluation(GINWithJK, d, [2, 3, 4, 5], [64, 128], max_num_epochs=100,
                                        batch_size=128, start_lr=0.01,
                                        num_repetitions=num_reps, all_std=True)
         print(d + " " + "GINWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GINWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
-        acc, s_1, s_2 = gnn_evaluation(GIN, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200, batch_size=128,
+        acc, s_1, s_2 = gnn_evaluation(GIN, d, [2, 3, 4, 5], [64, 128], max_num_epochs=100, batch_size=128,
                                        start_lr=0.01,
                                        num_repetitions=num_reps, all_std=True)
         print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))

### 2020-05-12 main.tex
Fixed GNN evaluation.
MC

--- 2020-05-09 main.tex
@@
 			\cmidrule{2-8}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GIN-$\varepsilon$}    & \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-		& \text{GIN-$\varepsilon$-JK} &          \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GINE-$\varepsilon$}   &  \scriptsize $\pm \pm $ &  72.9  \scriptsize $\pm 0.5 \pm 4.1$       & 48.8 \scriptsize $\pm 0.4 \pm 3.5 $  &78.0 \scriptsize $\pm 0.4  \pm 1.9  $  & 71.2  \scriptsize $\pm 0.3 \pm 3.6 $ & 90.2  \scriptsize $\pm 0.4  \pm 2.2 $   \\
+		& \text{GINE-$\varepsilon$-JK} & \scriptsize $\pm \pm $     &  72.9  \scriptsize $\pm 0.5 \pm 4.1 $ & 50.6 \scriptsize $\pm 1.0 \pm 4.6 $ & 79.7  \scriptsize $\pm 0.4  \pm 1.6$ & 71.3 \scriptsize $\pm 1.0 \pm 4.5$ &  90.3 \scriptsize $\pm 0.4  \pm 2.0  $   \\
 			\bottomrule
@@
 
-eintragen
-IMDB-BINARY GINWithJK 72.93333333333334 0.5185449728701322 4.122566622330749
-IMDB-BINARY GIN 72.06666666666668 0.3091206165165233 4.024370206076419
-IMDB-MULTI GINWithJK 50.644444444444446 1.01153837126587 4.59462917806765
-IMDB-MULTI GIN 48.84444444444444 0.37051848890073463 3.523185988018918
-NCI1 GINWithJK 79.67558799675588 0.4130683399269047 1.5714739782362184
-NCI1 GIN 78.01297648012977 0.38333502994634977 1.9142541830162463
-PROTEINS GINWithJK 71.27895752895752 0.9574183044143284 4.459876910576175
-PROTEINS GIN 71.16527241527241 0.3211668436757545 3.612551907408368
-REDDIT-BINARY GINWithJK 90.31666666666668 0.4326918328582383 1.9894862541760765
-
-REDDIT-BINARY GIN 90.18333333333334 0.39228674319799567 2.169805418823438
+Bitte eintragen
 

### 2020-05-12 tud_benchmark/main_gnn.py

@@ -82,12 +82,12 @@ def main():
         dp.get_dataset(d)
 
         acc, s_1, s_2 = gnn_evaluation(GINEWithJK, d, [3], [64], max_num_epochs=200,
-                                       batch_size=128, start_lr=0.01,
+                                       batch_size=64, start_lr=0.01,
                                        num_repetitions=num_reps, all_std=True)
         print(d + " " + "GINEWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GINWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
-        acc, s_1, s_2 = gnn_evaluation(GINE, d, [3], [64], max_num_epochs=200, batch_size=128,
+        acc, s_1, s_2 = gnn_evaluation(GINE, d, [3], [64], max_num_epochs=200, batch_size=64,
                                        start_lr=0.01,
                                        num_repetitions=num_reps, all_std=True)
         print(d + " " + "GINE " + str(acc) + " " + str(s_1) + " " + str(s_2))
@@ -122,12 +122,12 @@ def main():
         dp.get_dataset(d)
 
         acc, s_1, s_2 = gnn_evaluation(GINE, d, [3], [64], max_num_epochs=200,
-                                       batch_size=128, start_lr=0.01,
+                                       batch_size=64, start_lr=0.01,
                                        num_repetitions=num_reps, all_std=True)
         print(d + " " + "GINE " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GINE " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
-        acc, s_1, s_2 = gnn_evaluation(GINE0, d, [3], [64], max_num_epochs=200, batch_size=128,
+        acc, s_1, s_2 = gnn_evaluation(GINE0, d, [3], [64], max_num_epochs=200, batch_size=64,
                                        start_lr=0.01,
                                        num_repetitions=num_reps, all_std=True)
         print(d + " " + "GINE0 " + str(acc) + " " + str(s_1) + " " + str(s_2))

### 2020-05-13 tud_benchmark/main_kernel.py
Experiments

@@ -6,67 +6,78 @@ from auxiliarymethods.kernel_evaluation import kernel_svm_evaluation
 
 
 def main():
+    all_matrices = []
+    classes = dp.get_dataset("ENZYMES")
+    for i in range(1, 6):
+        gm = kb.compute_wl_1_sparse("ENZYMES", i, True, False)
+        gm_n = aux.normalize_feature_vector(gm)
+        all_matrices.append(gm_n)
+    acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=2, all_std=True)
+    print("ENYZMES" + " " + "WL1SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
+
+    exit()
+
     # Smaller datasets using LIBSVM.
     dataset = [["ENZYMES", True], ["IMDB-BINARY", False], ["IMDB-MULTI", False], ["NCI1", True], ["PROTEINS", True],
                  ["REDDIT-BINARY", False]]
 
     results = []
-    #
-    # for d, use_labels in dataset:
-    #     dataset = d
-    #     classes = dp.get_dataset(dataset)
-    #
-    #     all_matrices = []
-    #     for i in range(1, 6):
-    #         gm = kb.compute_wl_1_dense(dataset, i, use_labels, False)
-    #         gm_n = aux.normalize_gram_matrix(gm)
-    #         all_matrices.append(gm_n)
-    #     acc, s_1, s_2 = kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True)
-    #     print(d + " " + "WL1 " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #     results.append(d + " " + "WL1 " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #
-    #     all_matrices = []
-    #     for i in range(1, 6):
-    #         gm = kb.compute_lwl_2_dense(dataset, i, use_labels, False, False)
-    #         gm_n = aux.normalize_gram_matrix(gm)
-    #         all_matrices.append(gm_n)
-    #     acc, s_1, s_2 = kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True)
-    #     print(d + " " + "LWL2 " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #     results.append(d + " " + "LWL2 " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #
-    #     all_matrices = []
-    #     for i in range(1, 6):
[…]

### 2020-05-13 tud_benchmark/auxiliarymethods/kernel_evaluation.py
Experiments

@@ -29,7 +29,7 @@ def linear_svm_evaluation(all_feature_matrices, classes, num_repetitions=10,
                 train = gram_matrix[inner_train_index]
                 val = gram_matrix[val_index]
 
-                c_train = classes[train_index]
+                c_train = classes[inner_train_index]
                 c_val = classes[val_index]
 
                 for c in C:

### 2020-05-13 tud_benchmark/main_kernel.py

@@ -82,7 +82,7 @@ def main():
     ####################################################################################################################
     # Larger datasets using LIBLINEAR.
 
-    num_reps=3
+    num_reps= 3
 
     dataset = [["MOLT-4", True, True], ["TRIANGLES", False, False], ["MCF-7", True, True],
                  ["github_stargazers", False, False],

### 2020-05-13 main.tex
Experiments

@@
 			\cmidrule{2-8}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GINE-$\varepsilon$}   &  \scriptsize $\pm \pm $ &  72.9  \scriptsize $\pm 0.5 \pm 4.1$       & 48.8 \scriptsize $\pm 0.4 \pm 3.5 $  &78.0 \scriptsize $\pm 0.4  \pm 1.9  $  & 71.2  \scriptsize $\pm 0.3 \pm 3.6 $ & 90.2  \scriptsize $\pm 0.4  \pm 2.2 $   \\
-		& \text{GINE-$\varepsilon$-JK} & \scriptsize $\pm \pm $     &  72.9  \scriptsize $\pm 0.5 \pm 4.1 $ & 50.6 \scriptsize $\pm 1.0 \pm 4.6 $ & 79.7  \scriptsize $\pm 0.4  \pm 1.6$ & 71.3 \scriptsize $\pm 1.0 \pm 4.5$ &  90.3 \scriptsize $\pm 0.4  \pm 2.0  $   \\
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GINE-$\varepsilon$}   &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+		& \text{GINE-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
 			\bottomrule
@@
 \end{table*}
-
-Bitte eintragen
-
-ENZYMES WL1 50.28333333333334 1.1524129275375015 6.872065030089411
-ENZYMES LWL2 55.6 1.5709162223930901 6.788552455748164
-ENZYMES LWLP2 53.55 1.5402921800749356 6.3274314606235675
-ENZYMES WLOA 56.7 2.0094222497468714 7.129671957546308
-ENZYMES GR 32.35 1.036688102672266 5.359804100897718
-ENZYMES SP 39.8 1.2840906856172143 6.473364229243128
-IMDB-BINARY WL1 72.57 0.9143850392476894 4.133412633647891
-IMDB-BINARY LWL2 73.37 0.6372597586541924 4.430925411243119
-IMDB-BINARY LWLP2 76.65 1.353698637068088 4.924175057814253
-IMDB-BINARY WLOA 72.69 0.6818357573492301 4.749094650562357
-IMDB-BINARY GR 59.19 0.865390085452797 5.017359863513877
-IMDB-BINARY SP 57.860000000000014 1.4291256067959874 5.734143353631822
-IMDB-MULTI WL1 50.09333333333333 0.6262409901769259 3.811118237764636
-IMDB-MULTI LWL2 50.15333333333333 0.38418745424597134 4.055016098063676
-
-IMDB-MULTI LWLP2 74.01333333333334 0.9360911636516311 4.502818870194288
-IMDB-MULTI WLOA 49.86666666666666 0.6352602266438174 4.455209185760966
-IMDB-MULTI GR 39.17333333333333 0.7660577291852385 4.380887784202853
-IMDB-MULTI SP 39.50666666666666 0.18184242262647857 3.3791780723194287
-NCI1 WL1 84.38929440389293 0.25125704415427325 1.6049986739634532
-NCI1 LWL2 84.89537712895375 0.20028336376892103 1.7608176856505284
-NCI1 LWLP2 84.32846715328466 0.35931558467907326 1.9074851647350406
-NCI1 WLOA 84.985401459854 0.26237917572915365 1.944431716559596
-NCI1 GR 65.8272506082725 0.31011161731748405 2.3057620215984294
-NCI1 SP 74.21411192214111 0.26335881513838716 2.007846272147655
-PROTEINS WL1 73.49348455598457 0.6459030975700468 4.234672201391122
-PROTEINS LWL2 74.79681467181469 0.665180097352863 4.60334576380455
-PROTEINS LWLP2 75.63296332046333 0.5832232093036747 4.118575468095003
-PROTEINS WLOA 73.48656692406692 0.6497356451647441 4.4435644964869745
-PROTEINS GR 71.91473616473615 0.5582152728034838 4.153766329154282
-PROTEINS SP 75.29930823680823 0.433922307671726 3.6869730552272064
-REDDIT-BINARY WL1 73.15 0.5860887304837047 3.1547583108694712
-REDDIT-BINARY LWL2 89.09 0.4856953777832335 2.504376169827528
 

### 2020-05-13 tud_benchmark/main_kernel.py

@@ -7,12 +7,12 @@ from auxiliarymethods.kernel_evaluation import kernel_svm_evaluation
 
 def main():
     all_matrices = []
-    classes = dp.get_dataset("ENZYMES")
+    classes = dp.get_dataset("NCI1")
     for i in range(1, 6):
-        gm = kb.compute_wl_1_sparse("ENZYMES", i, True, False)
+        gm = kb.compute_graphlet_sparse("NCI1", True, False)
         gm_n = aux.normalize_feature_vector(gm)
         all_matrices.append(gm_n)
-    acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=2, all_std=True)
+    acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=1, all_std=True)
     print("ENYZMES" + " " + "WL1SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
     exit()

### 2020-05-13 tud_benchmark/main_kernel.py
Experiments

@@ -6,16 +6,6 @@ from auxiliarymethods.kernel_evaluation import kernel_svm_evaluation
 
 
 def main():
-    all_matrices = []
-    classes = dp.get_dataset("NCI1")
-    for i in range(1, 6):
-        gm = kb.compute_graphlet_sparse("NCI1", True, False)
-        gm_n = aux.normalize_feature_vector(gm)
-        all_matrices.append(gm_n)
-    acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=1, all_std=True)
-    print("ENYZMES" + " " + "WL1SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
-
-    exit()
 
     # Smaller datasets using LIBSVM.
     dataset = [["ENZYMES", True], ["IMDB-BINARY", False], ["IMDB-MULTI", False], ["NCI1", True], ["PROTEINS", True],

### 2020-05-18 main.tex
MC>
Added results

@@
 
+\cm{add articles discussing insuff. of small datasets like so https://arxiv.org/pdf/1905.04579.pdf and add other papers}
+
 \cm{Add new work from Borgwardt and Pascale Frossard.}
@@
 			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule
-			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &    \scriptsize $\pm  \pm  $       & \scriptsize $\pm   \pm $ &  \scriptsize $\pm  \pm   $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm  \pm   $ & \scriptsize $\pm  \pm $  \\
+			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &    \scriptsize $52.3\pm 0.7 \pm 6.7 $       & \scriptsize $72.6\pm  0.6 \pm 4.1$ &  \scriptsize $50.3\pm 0.8 \pm  3.8 $ &  \scriptsize $84.5\pm 0.3 \pm 1.7$ &  \scriptsize $72.8\pm 0.8 \pm  3.9 $ & \scriptsize $73.9\pm 0.6 \pm 3.2$  \\
 				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
 				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-				& \text{WLOA} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-				& \text{GR}            &     \scriptsize $\pm  \pm$       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm   $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm $ & \scriptsize $\pm  \pm  $   \\
-				& \text{SP}            &   \scriptsize $\pm  \pm $       &  \scriptsize $\pm  \pm  $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm \pm  $  & \scriptsize $\pm  \pm $ &  \scriptsize $\pm\pm $  \\
+				& \text{WLOA} &   \scriptsize $58.4\pm 2.0 \pm 7.4$       &  \scriptsize $73.2\pm 0.8 \pm 3.8$ &  \scriptsize $49.4\pm 0.3 \pm 3.6 $ & \scriptsize $85.4\pm  0.2 \pm 1.4$ &  \scriptsize $73.2\pm 0.6 \pm 3.5$ &  \scriptsize $88.4\pm 0.4 \pm 2.1 $   \\
+				& \text{GR}            &     \scriptsize $30.1\pm 0.8 \pm 6.0$       &  \scriptsize $59.0\pm 0.9 \pm 5.7$ &  \scriptsize $39.6\pm 0.5 \pm 3.6  $ &  \scriptsize $66.2\pm 0.2\pm 2.2$ &  \scriptsize $71.4\pm 0.6\pm 4.4 $ & \scriptsize $60.0\pm 0.2 \pm  2.7$   \\
+				& \text{SP}            &   \scriptsize $40.5\pm 1.6 \pm 6.2$       &  \scriptsize $58.7\pm 0.9 \pm 4.6 $ &  \scriptsize $39.5\pm 0.9 \pm 4.2$ &  \scriptsize $74.5\pm 0.4\pm 2.2 $  & \scriptsize $75.9\pm 0.6 \pm 4.0$ &  \scriptsize $84.6\pm0.2\pm 0.4 $  \\
 			\cmidrule{2-8}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GINE-$\varepsilon$}   &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-		& \text{GINE-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GINE-$\varepsilon$}   &   \scriptsize $\pm \pm $       &  \scriptsize $72.4\pm 0.6\pm 4.0 $ &  \scriptsize $49.7\pm 0.2 \pm  3.9$ & \scriptsize $79.0\pm  0.5 \pm 1.9 $ &  \scriptsize $71.3\pm 0.4 \pm 4.0$ &  \scriptsize $90.0\pm 0.6 \pm 1.7 $   \\
+		& \text{GINE-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       &  \scriptsize $73.4\pm 0.6\pm 4.4$ &  \scriptsize $50.6\pm 0.5 \pm 4.2 $ & \scriptsize $79.1\pm  0.2 \pm 1.5 $ &  \scriptsize $72.4\pm 0.6 \pm 1.7 $ &  \scriptsize $90.6\pm 0.2 \pm  2.2$   \\
 			\bottomrule
@@
 							\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
-							   \scriptsize $\pm   \pm $       & \scriptsize $\pm   \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\
+							   \scriptsize $94.5\pm  0.0 \pm 0.4$       & \scriptsize $94.6\pm 0.1  \pm 0.3$ & \scriptsize $36.5\pm 0.1\pm0.7$ &  \scriptsize $63.9\pm 0.1\pm1.3$ & \scriptsize $77.0\pm 0.0\pm0.3$  \\
 
-			& \text{GR}            &   \scriptsize $\pm    \pm  $       &   \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\  
-			& \text{SP}             &    \scriptsize $\pm  \pm $       &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\   
+			& \text{GR}            &   \scriptsize $91.7\pm  0.0  \pm 0.5 $       &   \scriptsize $92.1\pm 0.0 \pm 0.4$ & \scriptsize $14.3\pm 0.0 \pm 0.6$ &  \scriptsize $53.5\pm 0.0 \pm1.3$ & \scriptsize $51.2\pm 0.0 \pm 0.4$  \\
+			& \text{SP}             &    \scriptsize $91.7\pm 0.0 \pm 0.4 $       &  \scriptsize $92.1\pm 0.0 \pm 0.4 $ & \scriptsize $16.5\pm 0.1 \pm 0.4$ &  \scriptsize $64.1\pm 0.1\pm1.4$ & \scriptsize $77.3\pm 0.0 \pm0.3$  \\
 			\cmidrule{2-7}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GIN-E-$\varepsilon$}         &    \scriptsize $\pm  \pm $       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ \\
-			& \text{GraphSage}            &    \scriptsize $\pm \pm$       & \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm $  \\
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GIN-E-$\varepsilon$}         &    \scriptsize $92.0\pm  0.1\pm 0.6$       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ \\
+			& \text{GraphSage}            &    \scriptsize $91.8\pm 0.0\pm 0.5$       & \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm $  \\
 			\bottomrule

### 2020-05-18 main.tex
MC

--- 2020-05-13 main.tex
@@
 
+\cm{add articles discussing insuff. of small datasets like so https://arxiv.org/pdf/1905.04579.pdf and add other papers}
+
 \cm{Add new work from Borgwardt and Pascale Frossard.}
+
+\cm{Add IPC paper}
 
@@
 			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &    \scriptsize $\pm  \pm  $       & \scriptsize $\pm   \pm $ &  \scriptsize $\pm  \pm   $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm  \pm   $ & \scriptsize $\pm  \pm $  \\
-				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
 				& \text{WLOA} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
@@
 			\cmidrule{2-8}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GINE-$\varepsilon$}   &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-		& \text{GINE-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GIN-$\varepsilon$}   &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+		& \text{GIN-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
 			\bottomrule
@@
 			\cmidrule{2-7}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GIN-E-$\varepsilon$}         &    \scriptsize $\pm  \pm $       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ \\
-			& \text{GraphSage}            &    \scriptsize $\pm \pm$       & \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm $  \\
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GINE-$\varepsilon$}         &    \scriptsize $\pm  \pm $       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ \\
+			& \text{GINE-$\varepsilon$-JK}            &    \scriptsize $\pm \pm$       & \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm $  \\
 			\bottomrule

### 2020-05-18 main.tex
MC

--- 2020-05-18 main.tex
@@
 
+\cm{Add IPC paper}
+
 Recently, GNNs~\cite{Gil+2017} emerged as a alternative to graph kernels.
@@
 			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule
+
 			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &    \scriptsize $52.3\pm 0.7 \pm 6.7 $       & \scriptsize $72.6\pm  0.6 \pm 4.1$ &  \scriptsize $50.3\pm 0.8 \pm  3.8 $ &  \scriptsize $84.5\pm 0.3 \pm 1.7$ &  \scriptsize $72.8\pm 0.8 \pm  3.9 $ & \scriptsize $73.9\pm 0.6 \pm 3.2$  \\
-				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
 				& \text{WLOA} &   \scriptsize $58.4\pm 2.0 \pm 7.4$       &  \scriptsize $73.2\pm 0.8 \pm 3.8$ &  \scriptsize $49.4\pm 0.3 \pm 3.6 $ & \scriptsize $85.4\pm  0.2 \pm 1.4$ &  \scriptsize $73.2\pm 0.6 \pm 3.5$ &  \scriptsize $88.4\pm 0.4 \pm 2.1 $   \\
@@
 			\cmidrule{2-7}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GIN-E-$\varepsilon$}         &    \scriptsize $92.0\pm  0.1\pm 0.6$       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ \\
-			& \text{GraphSage}            &    \scriptsize $91.8\pm 0.0\pm 0.5$       & \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm $  \\
+	\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GINE-$\varepsilon$}   	&  \scriptsize $\pm \pm $   &   \scriptsize $\pm \pm $  &  \scriptsize $\pm \pm $   &  \scriptsize $\pm \pm $   &  \scriptsize $\pm \pm $   \\
+& \text{GINE-$\varepsilon$-JK} &   	  \scriptsize $\pm \pm $ 	&  \scriptsize $\pm \pm $ 	&  \scriptsize $\pm \pm $ 	&  \scriptsize $\pm \pm $ 	&  \scriptsize $\pm \pm $     \\
 \bottomrule
@@
 \end{table*}
+
+MCF-7 GINE 92.04177169607492 0.11168932242902482 0.6168139326015197
+MCF-7 GINEWithJK 91.82451086304165 0.03544550008458542 0.4987522858590044
+MOLT-4 GINE 92.27880821092846 0.1002790474000517 0.6244032371312984
+MOLT-4 GINEWithJK 92.19749601455855 0.01200982424702308 0.4789451008784327
 

### 2020-05-25 tud_benchmark/main_gnn.py
Added add pooling to GNNs.

@@ -17,12 +17,12 @@ def main():
         dp.get_dataset(d)
 
         acc, s_1, s_2 = gnn_evaluation(GIN, d, [1,2,3,4,5], [64,128], add_pool=True, max_num_epochs=200, batch_size=128,
-                                       start_lr=0.01, num_repetitions=1, all_std=True)
+                                       start_lr=0.01, num_repetitions=num_reps, all_std=True)
         print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
-        acc, s_1, s_2 = gnn_evaluation(GIN, d, [1,2,3,4,5], [64,128], add_pool=False, max_num_epochs=200, batch_size=128,
-                                       start_lr=0.01, num_repetitions=1, all_std=True)
+        acc, s_1, s_2 = gnn_evaluation(GIN, d, [1,2,3,4,5], [32,64,128], add_pool=False, max_num_epochs=200, batch_size=128,
+                                       start_lr=0.01, num_repetitions=num_reps, all_std=True)
         print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
 

### 2020-05-25 tud_benchmark/main_gnn.py
Added add pooling to GNNs.

@@ -26,6 +26,16 @@ def main():
         print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
+        acc, s_1, s_2 = gnn_evaluation(GIN0, d, [1,2,3,4,5], [64,128], add_pool=True, max_num_epochs=200, batch_size=128,
+                                       start_lr=0.01, num_repetitions=num_reps, all_std=True)
+        print(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
+        results.append(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
+
+        acc, s_1, s_2 = gnn_evaluation(GIN0, d, [1,2,3,4,5], [32,64,128], add_pool=False, max_num_epochs=200, batch_size=128,
+                                       start_lr=0.01, num_repetitions=num_reps, all_std=True)
+        print(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
+        results.append(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
+
 
     # results = []
     # for d, use_labels in dataset:

### 2020-05-25 tud_benchmark/main_gnn.py
Added add pooling to GNNs.

@@ -16,22 +16,22 @@ def main():
     for d, use_labels in dataset:
         dp.get_dataset(d)
 
-        acc, s_1, s_2 = gnn_evaluation(GIN, d, [1,2,3,4,5], [64,128], add_pool=True, max_num_epochs=200, batch_size=128,
+        acc, s_1, s_2 = gnn_evaluation(GIN, d, [1,2,3,4,5], [16,32,64,128], add_pool=True, max_num_epochs=200, batch_size=128,
                                        start_lr=0.01, num_repetitions=num_reps, all_std=True)
         print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
-        acc, s_1, s_2 = gnn_evaluation(GIN, d, [1,2,3,4,5], [32,64,128], add_pool=False, max_num_epochs=200, batch_size=128,
+        acc, s_1, s_2 = gnn_evaluation(GIN, d, [1,2,3,4,5], [16,32,64,128], add_pool=False, max_num_epochs=200, batch_size=128,
                                        start_lr=0.01, num_repetitions=num_reps, all_std=True)
         print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
-        acc, s_1, s_2 = gnn_evaluation(GIN0, d, [1,2,3,4,5], [64,128], add_pool=True, max_num_epochs=200, batch_size=128,
+        acc, s_1, s_2 = gnn_evaluation(GIN0, d, [1,2,3,4,5], [16,32,64,128], add_pool=True, max_num_epochs=200, batch_size=128,
                                        start_lr=0.01, num_repetitions=num_reps, all_std=True)
         print(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
-        acc, s_1, s_2 = gnn_evaluation(GIN0, d, [1,2,3,4,5], [32,64,128], add_pool=False, max_num_epochs=200, batch_size=128,
+        acc, s_1, s_2 = gnn_evaluation(GIN0, d, [1,2,3,4,5], [16,32,64,128], add_pool=False, max_num_epochs=200, batch_size=128,
[…]

### 2020-05-25 tud_benchmark/auxiliarymethods/gnn_evaluation.py
Added add pooling to GNNs.

@@ -54,7 +54,7 @@ def test(loader, model, device):
 
 
 # 10-CV for GNN training and hyperparameter selection.
-def gnn_evaluation(gnn, ds_name, layers, hidden, add_pool=False, max_num_epochs=200, batch_size=128,  start_lr=0.01, num_repetitions=10, all_std=True):
+def gnn_evaluation(gnn, ds_name, layers, hidden, add_pool=False, max_num_epochs=200, batch_size=128, start_lr=0.01, num_repetitions=10, all_std=True):
     # Load dataset and shuffle.
     path = osp.join(osp.dirname(osp.realpath(__file__)), '..', 'datasets', ds_name)
     dataset = TUDataset(path, name=ds_name).shuffle()

### 2020-05-25 tud_benchmark/main_gnn.py

@@ -6,36 +6,36 @@ import os.path as osp
 
 def main():
     num_reps = 10
-    # NeuriPS stuff, ENZYMES
-    print("NeurIPS")
-
-    # Smaller datasets.
-    dataset = [["ENZYMES", True]]
-
-    results = []
-    for d, use_labels in dataset:
-        dp.get_dataset(d)
-
-        acc, s_1, s_2 = gnn_evaluation(GIN, d, [1,2,3,4,5], [16,32,64,128], add_pool=True, max_num_epochs=200, batch_size=128,
-                                       start_lr=0.01, num_repetitions=num_reps, all_std=True)
-        print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
-        results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
-
-        acc, s_1, s_2 = gnn_evaluation(GIN, d, [1,2,3,4,5], [16,32,64,128], add_pool=False, max_num_epochs=200, batch_size=128,
-                                       start_lr=0.01, num_repetitions=num_reps, all_std=True)
-        print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
-        results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
-
-        acc, s_1, s_2 = gnn_evaluation(GIN0, d, [1,2,3,4,5], [16,32,64,128], add_pool=True, max_num_epochs=200, batch_size=128,
-                                       start_lr=0.01, num_repetitions=num_reps, all_std=True)
-        print(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
-        results.append(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
-
-        acc, s_1, s_2 = gnn_evaluation(GIN0, d, [1,2,3,4,5], [16,32,64,128], add_pool=False, max_num_epochs=200, batch_size=128,
-                                       start_lr=0.01, num_repetitions=num_reps, all_std=True)
-        print(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
-        results.append(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
-
+    # # NeuriPS stuff, ENZYMES
+    # print("NeurIPS")
+    #
[…]

### 2020-05-25 main.tex
results
MC
Added add pooling to GNNs.

--- 2020-05-18 main.tex
@@
 			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule
-			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &    \scriptsize $\pm  \pm  $       & \scriptsize $\pm   \pm $ &  \scriptsize $\pm  \pm   $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm  \pm   $ & \scriptsize $\pm  \pm $  \\
+
+			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &   $52.3$ \scriptsize $\pm 0.7 \pm 6.7 $       & $72.6$ \scriptsize $\pm  0.6 \pm 4.1$ &  $50.3$ \scriptsize $\pm 0.8 \pm  3.8 $ & $84.5$ \scriptsize $\pm 0.3 \pm 1.7$ & $72.8$ \scriptsize $\pm 0.8 \pm  3.9 $ & $73.9$ \scriptsize $\pm 0.6 \pm 3.2$  \\
 %				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
 %				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-				& \text{WLOA} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-				& \text{GR}            &     \scriptsize $\pm  \pm$       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm   $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm $ & \scriptsize $\pm  \pm  $   \\
-				& \text{SP}            &   \scriptsize $\pm  \pm $       &  \scriptsize $\pm  \pm  $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm \pm  $  & \scriptsize $\pm  \pm $ &  \scriptsize $\pm\pm $  \\
+				& \text{WLOA} & $58.4$ \scriptsize $\pm 2.0 \pm 7.4$       &  $73.2$ \scriptsize $\pm 0.8 \pm 3.8$ & $49.4$ \scriptsize $\pm 0.3 \pm 3.6 $ & $85.4$ \scriptsize $\pm  0.2 \pm 1.4$ & $73.2$ \scriptsize $\pm 0.6 \pm 3.5$ & $88.4$ \scriptsize $\pm 0.4 \pm 2.1 $   \\
+				& \text{GR}            &    $30.1$ \scriptsize $\pm 0.8 \pm 6.0$       & $59.0$ \scriptsize $\pm 0.9 \pm 5.7$ & $39.6$ \scriptsize $\pm 0.5 \pm 3.6  $ & $66.2$ \scriptsize $\pm 0.2\pm 2.2$ & $71.4$ \scriptsize $\pm 0.6\pm 4.4 $ & $60.0$ \scriptsize $\pm 0.2 \pm  2.7$   \\
+				& \text{SP}            & $40.5$  \scriptsize $\pm 1.6 \pm 6.2$       & $58.7$ \scriptsize $\pm 0.9 \pm 4.6 $ & $39.5$ \scriptsize $\pm 0.9 \pm 4.2$ & $74.5$ \scriptsize $\pm 0.4\pm 2.2 $  &$75.9$ \scriptsize $\pm 0.6 \pm 4.0$ & $84.6$ \scriptsize $\pm0.2\pm 0.4 $  \\
 			\cmidrule{2-8}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GIN-$\varepsilon$}   &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-		& \text{GIN-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GINE-$\varepsilon$}   &   \scriptsize $\pm \pm $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
+		& \text{GINE-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
 		\bottomrule
@@
 			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
-			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Triangles}}           & {\textsc{github\_stargazers}}       & {\textsc{reddit\_threads}}      \\	\toprule
+			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Yeast}}           & {\textsc{github\_stargazers}}       & {\textsc{reddit\_threads}}      \\	\toprule
 							\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
-							   \scriptsize $\pm   \pm $       & \scriptsize $\pm   \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\
+							   $94.5$ \scriptsize $\pm  0.0 \pm 0.4$       &$94.6$ \scriptsize $\pm 0.1  \pm 0.3$ & $$ \scriptsize $\pm \pm$ &  $63.9$ \scriptsize $\pm 0.1\pm1.3$ &$77.0$ \scriptsize $\pm 0.0\pm0.3$  \\
 
-			& \text{GR}            &   \scriptsize $\pm    \pm  $       &   \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\  
-			& \text{SP}             &    \scriptsize $\pm  \pm $       &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\   
+			& \text{GR}            & $91.7$  \scriptsize $\pm  0.0  \pm 0.5 $       & $92.1$ \scriptsize $\pm 0.0 \pm 0.4$ & $$ \scriptsize $\pm  \pm $ &  $53.5$ \scriptsize $\pm 0.0 \pm1.3$ & $51.2$ \scriptsize $\pm 0.0 \pm 0.4$  \\
+			& \text{SP}             &  $91.7$  \scriptsize $\pm 0.0 \pm 0.4 $       &$92.1$  \scriptsize $\pm 0.0 \pm 0.4 $ & $$ \scriptsize $\pm  \pm $ & $64.1$ \scriptsize $\pm 0.1\pm1.4$ & $77.3$ \scriptsize $\pm 0.0 \pm0.3$  \\
 			\cmidrule{2-7}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GINE-$\varepsilon$}         &    \scriptsize $\pm  \pm $       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ \\
-			& \text{GINE-$\varepsilon$-JK}            &    \scriptsize $\pm \pm$       & \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm $  \\
+	\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GIN-E-$\varepsilon$}         &  $92.0$ \scriptsize $\pm  0.1\pm 0.6$       & $92.3$ \scriptsize $\pm0.1 \pm 0.6$ & \scriptsize $\pm \pm$ &  67.1 \scriptsize $\pm 0.5 \pm 1.6  $ & 77.2 \scriptsize $\pm 0.0  \pm 0.3$ \\
+	& \text{GINE-$\varepsilon$-JK}   &   $91.8$ \scriptsize $\pm 0.0\pm 0.5$       & $92.2$ \scriptsize $\pm 0.0\pm0.5$ & \scriptsize $\pm \pm$ &  67.2 \scriptsize $\pm 0.4 \pm 1.3$ &  77.3  \scriptsize $\pm 0.0 \pm 0.3 $  \\
 \bottomrule
@@
 \begin{table}[t]\centering	
+	\cm{Maybe add qm9}	
 	\caption{Results for neural and kernel baselines.}

### 2020-05-25 tud_benchmark/main_gnn.py

@@ -1,6 +1,6 @@
 import auxiliarymethods.datasets as dp
 from auxiliarymethods.gnn_evaluation import gnn_evaluation
-from gnn_baselines.gnn_architectures import GIN0, GIN
+from gnn_baselines.gnn_architectures import GIN0, GIN, GINE, GINEWithJK
 
 import os.path as osp
 
@@ -124,43 +124,43 @@ def main():
     #
     # print("TUD")
     #
-    # # Larger datasets using LIBLINEAR.
-    # dataset = [["MCF-7", True], ["MOLT-4", True]]
-    #
-    # for d, use_labels in dataset:
-    #     dp.get_dataset(d)
-    #
-    #     acc, s_1, s_2 = gnn_evaluation(GINE, d, [3], [64], max_num_epochs=200, batch_size=64,
-    #                                    start_lr=0.01,
-    #                                    num_repetitions=num_reps, all_std=True)
-    #     print(d + " " + "GINE " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #     results.append(d + " " + "GINE " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #
-    #     acc, s_1, s_2 = gnn_evaluation(GINEWithJK, d, [3], [64], max_num_epochs=200,
-    #                                    batch_size=64, start_lr=0.01,
-    #                                    num_repetitions=num_reps, all_std=True)
-    #     print(d + " " + "GINEWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #     results.append(d + " " + "GINWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
-
-    print("TUD")
-    dataset = [["TRIANGLES", False],
-        ["reddit_threads", False]
-    ]
+    # Larger datasets using LIBLINEAR.
+    dataset = [["Yeast", True], ["MCF-7", True], ["MOLT-4", True]]
 
     for d, use_labels in dataset:
         dp.get_dataset(d)
 
-        acc, s_1, s_2 = gnn_evaluation(GIN, d, [3], [64], max_num_epochs=200, batch_size=64,
+        acc, s_1, s_2 = gnn_evaluation(GINE, d, [3], [64], max_num_epochs=200, batch_size=64,
                                        start_lr=0.01,
                                        num_repetitions=num_reps, all_std=True)
-        print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
[…]

### 2020-05-25 tud_benchmark/main_gnn.py
Added add pooling to GNNs.

@@ -5,7 +5,7 @@ from gnn_baselines.gnn_architectures import GIN0, GIN, GINE, GINEWithJK
 import os.path as osp
 
 def main():
-    num_reps = 10
+    num_reps = 3
     # # NeuriPS stuff, ENZYMES
     # print("NeurIPS")
     #

### 2020-05-25 tud_benchmark/auxiliarymethods/gnn_evaluation.py
Added add pooling to GNNs.

@@ -138,3 +138,89 @@ def gnn_evaluation(gnn, ds_name, layers, hidden, add_pool=False, max_num_epochs=
                 np.array(test_accuracies_complete).std())
     else:
         return (np.array(test_accuracies_all).mean(), np.array(test_accuracies_all).std())
+
+
+def gnn_evaluation_old(gnn, ds_name, layers, hidden, max_num_epochs=200, batch_size=128, start_lr=0.01, num_repetitions=10, all_std=True):
+    # Load dataset and shuffle.
+    path = osp.join(osp.dirname(osp.realpath(__file__)), '..', 'datasets', ds_name)
+    dataset = TUDataset(path, name=ds_name).shuffle()
+
+    # One-hot degree if node labels are not available.
+    if dataset.data.x is None:
+        max_degree = 0
+        degs = []
+        for data in dataset:
+            degs += [degree(data.edge_index[0], dtype=torch.long)]
+            max_degree = max(max_degree, degs[-1].max().item())
+
+        if max_degree < 1000:
+            dataset.transform = T.OneHotDegree(max_degree)
+        else:
+            deg = torch.cat(degs, dim=0).to(torch.float)
+            mean, std = deg.mean().item(), deg.std().item()
+            dataset.transform = NormalizedDegree(mean, std)
+
+    # Set device.
+    device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+
+    test_accuracies_all = []
+    test_accuracies_complete = []
+
+    for i in range(num_repetitions):
+        # Test acc. over all folds.
+        test_accuracies = []
+        kf = KFold(n_splits=10, shuffle=True)
+        dataset.shuffle()
+
+        for train_index, test_index in kf.split(list(range(len(dataset)))):
+            # Sample 10% split from training split for validation.
+            train_index, val_index = train_test_split(train_index, test_size=0.1)
+            best_val_acc = 0.0
+            best_test = 0.0
+
+            # Split data.
+            train_dataset = dataset[train_index.tolist()]
+            val_dataset = dataset[val_index.tolist()]
+            test_dataset = dataset[test_index.tolist()]
+
+            # Prepare batching.
+            train_loader = DataLoader(train_dataset, batch_size=batch_size, shuffle=True)
+            val_loader = DataLoader(val_dataset, batch_size=batch_size, shuffle=True)
+            test_loader = DataLoader(test_dataset, batch_size=batch_size, shuffle=True)
+
[…]

### 2020-05-25 tud_benchmark/main_gnn.py
Added add pooling to GNNs.

@@ -1,5 +1,5 @@
 import auxiliarymethods.datasets as dp
-from auxiliarymethods.gnn_evaluation import gnn_evaluation
+from auxiliarymethods.gnn_evaluation import gnn_evaluation,gnn_evaluation_old
 from gnn_baselines.gnn_architectures import GIN0, GIN, GINE, GINEWithJK
 
 import os.path as osp
@@ -130,13 +130,13 @@ def main():
     for d, use_labels in dataset:
         dp.get_dataset(d)
 
-        acc, s_1, s_2 = gnn_evaluation(GINE, d, [3], [64], max_num_epochs=200, batch_size=64,
+        acc, s_1, s_2 = gnn_evaluation_old(GINE, d, [3], [64], max_num_epochs=200, batch_size=64,
                                        start_lr=0.01,
                                        num_repetitions=num_reps, all_std=True)
         print(d + " " + "GINE " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GINE " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
-        acc, s_1, s_2 = gnn_evaluation(GINEWithJK, d, [3], [64], max_num_epochs=200,
+        acc, s_1, s_2 = gnn_evaluation_old(GINEWithJK, d, [3], [64], max_num_epochs=200,
                                        batch_size=64, start_lr=0.01,
                                        num_repetitions=num_reps, all_std=True)
         print(d + " " + "GINEWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))

### 2020-05-25 tud_benchmark/main_kernel.py
New exp. for Yeast (replaces TRIANGLES)

@@ -8,64 +8,59 @@ from auxiliarymethods.kernel_evaluation import kernel_svm_evaluation
 def main():
 
 
-    # Larger datasets using LIBLINEAR.
-    results = []
-    num_reps= 3
+    # # Larger datasets using LIBLINEAR.
+    # results = []
+    # num_reps= 3
+    #
+    # dataset = [["Yeast", True, True]]
+    #
+    # for d, use_labels, use_edge_labels in dataset:
+    #     print(d)
+    #     dataset = d
+    #     classes = dp.get_dataset(dataset)
+    #
+    #     # all_matrices = []
+    #     # for i in range(3, 4):
+    #     #     gm = kb.compute_wl_1_sparse(dataset, i, use_labels, use_edge_labels)
+    #     #     gm_n = aux.normalize_feature_vector(gm)
+    #     #     all_matrices.append(gm_n)
+    #     # acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=num_reps, all_std=True)
+    #     # print(d + " " + "WL1SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
+    #     # results.append(d + " " + "WL1SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
+    #
+    #     all_matrices = []
+    #     for i in range(3,4):
+    #         gm = kb.compute_lwlp_2_sparse(dataset, i, use_labels, use_edge_labels, False)
+    #         gm_n = aux.normalize_feature_vector(gm)
+    #         all_matrices.append(gm_n)
+    #     acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=1, all_std=True)
+    #     print(d + " " + "LWLP2SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
+    #     results.append(d + " " + "LWLP2SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
+    #
+    #     all_matrices = []
+    #     for i in range(3,4):
+    #         gm = kb.compute_lwl_2_sparse(dataset, i, use_labels, use_edge_labels, False)
+    #         gm_n = aux.normalize_feature_vector(gm)
+    #         all_matrices.append(gm_n)
+    #     acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=1, all_std=True)
+    #     print(d + " " + "LWL2SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
[…]

### 2020-05-26 tud_benchmark/main_kernel.py
MC.

@@ -163,6 +163,7 @@ def main():
             gm = kb.compute_wl_1_sparse(dataset, i, use_labels, use_edge_labels)
             gm_n = aux.normalize_feature_vector(gm)
             all_matrices.append(gm_n)
+
         acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=num_reps, all_std=True)
         print(d + " " + "WL1SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "WL1SP " + str(acc) + " " + str(s_1) + " " + str(s_2))

### 2020-06-06 main.tex
MC.
added Yeast results

@@
 
+\usepackage{natbib}
+
 \usepackage{booktabs}
@@
 \usepackage{tikz}
+\newcommand{\xhdr}[1]{{\noindent\bfseries #1}}
 
@@
 The dataset consists of over 120 datasets from a wide range of applications and varying sizes.
-We provide Python-based data loaders, kernel and graph neural network baseline methods implementations, and evaluation tools.
-Here, we give an overview of the datasets, evaluation tools, and provide baseline experiments.
-All datasets can be obtained from \url{www.graphlearning.io}.
-The experiments are fully reproduceable from the code available at \url{www.github.com/chrsmrrs/tudatasets}.
+We provide Python-based data loaders, kernel, and graph neural network baseline methods implementations, and evaluation tools.
+Here, we give an overview of the datasets, standardized evaluation procedures, and provide baseline experiments.
+All datasets are available at \url{www.graphlearning.io}.
+The experiments are fully reproducible from the code available at \url{www.github.com/chrsmrrs/tudatasets}.
 \end{abstract}
@@
 \section{Introduction}
-Graph-structured data is ubiquitous across application domains ranging from chemo- and bioinformatics to image and social network analysis.
+Graph-structured data is ubiquitous across application domains ranging from chemo- and bioinformatics~\cite{Barabasi2004,Sto+2020} to image~\cite{Sim+2017} and social network analysis~\cite{Eas+2010}.
 To develop successful machine learning models in these domains, we need techniques that can exploit the rich information inherent in the graph structure, as well as the feature information contained within nodes and edges.
@@
 
-Here, we give an overview of \textsc{Tud datasets}.
-The benchmark collection consists of over 120 datasets from a wide range of domains for supervised learning with graphs, i.e., classificiation and regression.
-All datasets are provided in a common dataset format at \url{graphlearning.io}, and can easily be accessed from popular graph learning frameworks such as \emph{Pytorch Geometric}~\cite{Fey+2019} and \emph{DGL}~\cite{Wan+2019}.
+\paragraph{Present work.} 
+Here, we give an overview of \textsc{TuDatasets}.
+The benchmark collection consists of over 120 datasets from a wide range of domains for supervised learning with graphs, i.e., classification and regression.
+All datasets are provided in a standard dataset format at \url{graphlearning.io} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019} and \textsc{DGL}~\cite{Wan+2019}.
+To facilitate standard comparison of kernel and neural approaches, we provide implementations of standard algorithms and easy-to-use evaluation procedures.
+Moreover, we report results on an experimental study comparing graph kernels and GNNs on a subset of the \textsc{TuDataset}.
 
-\paragraph{Related work.}
-There exists two main approaches to supervised learning with graphs, graph kernels and graph neural networks (GNNs).
-Graph kernels have been studied extensively in the past 15 years, see ~\cite{Kri+2019} for a thorough overview.
-Important approaches include random-walk and shortest paths based kernels~\cite{Gaertner2003,Sugiyama2015,Bor+2005,Kri+2017b}, as well as the Weisfeiler-Lehman subtree kernel~\cite{She+2011,Mor+2017}.
-Further recent works focus on assignment-based approaches~\cite{Kri+2016,Nik+2017}, spectral approaches~\cite{Kon+2016}, and graph decomposition approaches~\cite{Nik+2018}.
+\xhdr{Related work.}
+There exist two main approaches to supervised learning with graphs, graph kernels and graph neural networks (GNNs).
+Graph kernels have been studied extensively in the past 15 years, see~\cite{Kri+2019} for a thorough overview.
+Important approaches include random-walk and shortest paths based kernels~\cite{Gae+2003,Sugiyama2015,Bor+2005,Kri+2017b}, as well as the Weisfeiler-Lehman subtree kernel~\cite{She+2011,Mor+2017}.
+Further recent works focus on assignment-based approaches~\cite{Kri+2016,Nik+2017}, spectral approaches~\cite{Kon+2016}, and graph decomposition approaches~\cite{Nik+2018}, randomized binning approaches~\cite{Hei+2019}, and the extension of kernels based on the Weisfeiler-Leman algorithm~\cite{Tog+2019, Rie+2019}.
+For a theoretical investigation of graph kernels, see~\cite{Kri+2018}.
+Recently, graph neural networks (GNNs)~\cite{Gil+2017,Sca+2009} emerged as an alternative to graph kernels.
+Notable instances of this architecture include, e.g.,~\cite{Duv+2015,Ham+2017,Vel+2018}, and the spectral approaches proposed in, e.g.,~\cite{Bru+2014,Def+2015,Kip+2017,Mon+2017}---all of which descend from early work in~\cite{Kir+1995,Mer+2005,Spe+1997,Sca+2009}.
+A survey of recent advancements in GNN techniques can be found, e.g., in~\cite{Cha+2020,Wu+2019,Zho+2018}.
 
-\cm{add articles discussing insuff. of small datasets like so https://arxiv.org/pdf/1905.04579.pdf and add other papers}
-
-\cm{Add new work from Borgwardt and Pascale Frossard.}
-
-\cm{Add IPC paper}
-
-Recently, GNNs~\cite{Gil+2017} emerged as a alternative to graph kernels.
-Notable instances of this model include~\cite{Duv+2015},~\cite{Li+2016},~\cite{Ham+2017} and the spectral approaches proposed in~\cite{Bru+2014,Def+2015,Kip+2017}---all of which descend from early work in~\cite{Kir+1995,Mer+2005,Sca+2009}.
-More expressive higher-order approaches are proposed in~\cite{Mor+2019,Mar+2019}.
-A unifying message passing architecture can be found in~\cite{Gil+2017}.
-Two recent surveys~\cite{wu2019comprehensive,zhou2018graph} provide a thorough overview of graph neural networks.
-
-The papers~\cite{Fey+2019,Err+2019,Dwi+2020} evalute GNNs using a unified evaluation procedure, however, they only use small- or medium scale datasets.
-Recently, \url{ogb.stanford.edu} launchend, however the provided datasets for graph classification focus on chemistry and bioinformatic applications, and the number is quite limited at this point.
-
-\paragraph{Contributions} We give an overview of \textsc{TuDataset}, its unified evalution procedures, and baseline methods.
-Moreover, we report results on a experimental study comparing graph kernels and GNNs on a subset of the \textsc{TuDataset}.
+The papers~\cite{Fey+2019,Che+2019,Err+2019,Dwi+2020} evaluate GNNs using a unified evaluation procedure, however, they only use small- or medium scale datasets.
+Recently, \url{ogb.stanford.edu}~\cite{Hu+2020} launched, however, the provided datasets for graph classification focus on chemistry and bioinformatic applications, and the number is quite limited at this point.
+Moreover, the datasets proposed in~\cite{Fer+2019} focuses on instances from planning competitions.
 
@@
 							\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
-							   $94.5$ \scriptsize $\pm  0.0 \pm 0.4$       &$94.6$ \scriptsize $\pm 0.1  \pm 0.3$ & $$ \scriptsize $\pm \pm$ &  $63.9$ \scriptsize $\pm 0.1\pm1.3$ &$77.0$ \scriptsize $\pm 0.0\pm0.3$  \\
+							   $94.5$ \scriptsize $<0.1 \pm 0.4$  &$94.6$ \scriptsize $\pm 0.1  \pm 0.3$ & $89.2$ \scriptsize $\pm 0.1 \pm 0.4$ &  $63.9$ \scriptsize $\pm 0.1\pm 1.3$ &$77.0$ \scriptsize $<0.1 \pm 0.3$  \\
 
-			& \text{GR}            & $91.7$  \scriptsize $\pm  0.0  \pm 0.5 $       & $92.1$ \scriptsize $\pm 0.0 \pm 0.4$ & $$ \scriptsize $\pm  \pm $ &  $53.5$ \scriptsize $\pm 0.0 \pm1.3$ & $51.2$ \scriptsize $\pm 0.0 \pm 0.4$  \\
-			& \text{SP}             &  $91.7$  \scriptsize $\pm 0.0 \pm 0.4 $       &$92.1$  \scriptsize $\pm 0.0 \pm 0.4 $ & $$ \scriptsize $\pm  \pm $ & $64.1$ \scriptsize $\pm 0.1\pm1.4$ & $77.3$ \scriptsize $\pm 0.0 \pm0.3$  \\
+			& \text{GR}            & $91.7$  \scriptsize $<0.1  \pm 0.5 $       & $92.1$ \scriptsize $<0.1 \pm 0.4$ & $88.2$ \scriptsize $<0.1  \pm 0.4$ &  $53.5$ \scriptsize $<0.1 \pm 1.3$ & $51.2$ \scriptsize $<0.1 \pm 0.4$  \\
+			& \text{SP}             &  $91.7$  \scriptsize $<0.1 \pm 0.4 $       &$92.1$  \scriptsize $<0.1 \pm 0.4 $ & $88.2$ \scriptsize $<0.1  \pm 0.4$ & $64.1$ \scriptsize $\pm 0.1\pm 1.4$ & $77.3$ \scriptsize $<0.1 \pm 0.3$  \\
 			\cmidrule{2-7}	
-	\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GIN-E-$\varepsilon$}         &  $92.0$ \scriptsize $\pm  0.1\pm 0.6$       & $92.3$ \scriptsize $\pm0.1 \pm 0.6$ & \scriptsize $\pm \pm$ &  67.1 \scriptsize $\pm 0.5 \pm 1.6  $ & 77.2 \scriptsize $\pm 0.0  \pm 0.3$ \\
-	& \text{GINE-$\varepsilon$-JK}   &   $91.8$ \scriptsize $\pm 0.0\pm 0.5$       & $92.2$ \scriptsize $\pm 0.0\pm0.5$ & \scriptsize $\pm \pm$ &  67.2 \scriptsize $\pm 0.4 \pm 1.3$ &  77.3  \scriptsize $\pm 0.0 \pm 0.3 $  \\
+	\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GIN-E-$\varepsilon$}         &  $92.0$ \scriptsize $\pm  0.1 \pm 0.6$       & $92.3$ \scriptsize $\pm 0.1 \pm 0.6$ & \scriptsize $\pm \pm$ &  $67.1$ \scriptsize $\pm 0.5 \pm 1.6  $ & $77.2$ \scriptsize $<0.1  \pm 0.3$ \\
+	& \text{GINE-$\varepsilon$-JK}   &   $91.8$ \scriptsize $<0.1 \pm 0.5$       & $92.2$ \scriptsize $<0.1 \pm 0.5$ & \scriptsize $\pm \pm$ & $67.2$ \scriptsize $\pm 0.4 \pm 1.3$ &  $77.3$  \scriptsize $<0.1 \pm 0.3 $  \\
 \bottomrule
@@
 \end{table*}
+
+Yeast GINE 88.31840671346515 0.003881831878911156 0.32166787163196536
+Yeast GINEWithJK 88.18231308533625 0.04015610969845854 0.3325038752499045
 

### 2020-06-06 tud_benchmark/auxiliarymethods/kernel_evaluation.py

@@ -33,7 +33,7 @@ def linear_svm_evaluation(all_feature_matrices, classes, num_repetitions=10,
                 c_val = classes[val_index]
 
                 for c in C:
-                    clf = LinearSVC(C=c, tol=0.01, dual=True)
+                    clf = LinearSVC(C=c, tol=0.01, dual=False)
                     clf.fit(train, c_train)
                     val_acc = accuracy_score(c_val, clf.predict(val)) * 100.0
 
@@ -49,7 +49,7 @@ def linear_svm_evaluation(all_feature_matrices, classes, num_repetitions=10,
 
             c_train = classes[train_index]
             c_test = classes[test_index]
-            clf = LinearSVC(C=best_c, tol=0.01, dual=True)
+            clf = LinearSVC(C=best_c, tol=0.01, dual=False)
             clf.fit(train, c_train)
             best_test = accuracy_score(c_test, clf.predict(test)) * 100.0
 

### 2020-06-06 main.tex
MC.

@@
 The data  baseline methods and experimental evaluation tools can be installed by running \texttt{pip install tudatasets}.
-See the website for dataset statistics and further documentation.
+See the website for dataset statistics and documentation.
 
@@
 
-Our collection of datasets covers graphs from various domains, which were provided by different authors.
+Our collection of datasets covers graphs from various domains, contributed by different authors.
 Therefore, they differ regarding the used graph model even within the same domain and the provided annotations, e.g., discrete or continuous node and edge attributes.
@@
 
-\paragraph{Small molecules.} 
-A commonly used class of graph datasets are derived from small molecules with class labels representing, e.g., toxicity or biological activity determined in the context of drug discovery.
-A molecule is represented by a graph in which nodes take the places of atoms and edges that of chemical bonds.
-Consequently, the labels indicate atom and bond types, where additional chemical attributes are possible.
-The graph models differs, e.g., in whether hydrogen atoms represented explicitly by nodes and bonds in aromatic rings are annotated accordingly.
-Our collection contains small datasets commonly used in the early graph kernel literature such as \textsc{Mutag}~\citep{Deb+1991} and \textsc{Ptc}~\cite{Helma2001}, medium-sized datasets, e.g., \textsc{Nci1} and \textsc{Nci109}~\citep{Wal+2008,She+2011}, as well as several large datasets derived from the \emph{Tox21 Challenge 2014} or \emph{PubChem}~\citep{Kim2018}.
-This includes the 11 datasets from anticancer screen tests with different cancer cell lines used by \citet{Yan2008} to demonstrate the efficacy of classifiers based on significant graph patterns.
+\xhdr{Small molecules.} 
+A common class of graph datasets consist of small molecules with class labels representing, e.g., toxicity or biological activity.
+Here, a graph encodes a molecule, i.e., nodes take the places of atoms and edges that of chemical bonds.
+Consequently, the labels encode atom and bond types, with possibly  additional chemical attributes.
+The graph models differs, e.g., in whether hydrogen atoms are represented explicitly by nodes, and bonds in aromatic rings are annotated accordingly.
+
+Our collection contains small datasets commonly used in the early graph kernel literature such as \textsc{Mutag}~\cite{Deb+1991} and \textsc{Ptc}~\cite{Helma2001}, medium-sized datasets, e.g., \textsc{Nci1} and \textsc{Nci109}~\cite{Wal+2008,She+2011}, as well as several large datasets derived from the \textsc{Tox21 Challenge 2014} or \textsc{PubChem}~\cite{Kim2018}.
+This includes the eleven datasets from anticancer screen tests with different cancer cell lines used by~\citet{Yan2008} to demonstrate the efficacy of classifiers based on significant graph patterns.
 These datasets, the largest of which contain more than 79k graphs, are typically not balanced and contain far more small molecules that are identified as inactive against cancer cells.
-The \textsc{Alchemy} was proposed by~\citet{Chen2019a} for benchmarking {AI} models.
+Moreover, our collection also contain large-scale molecular regression tasks such as \textsc{Alchemy}~\cite{Che+2020}, \textsc{Qm9}~\cite{Ram+2014}, and \textsc{ZINC}~\cite{Dwi+2020,Jin+2018a}.
+For the two former we also provide 3D coordinates which are crucual to study rotation-invariant GNN architectures.
 
-\cm{Mention \textsc{ZINC} and the also mention size of DS, 200k}
-\cm{Mention \textsc{QM9}k}
-
-For some cheminformatics prediction tasks, the geometrical arrangement of atoms has been determined and should be taken into account in a rotation-invariant manner.
-In order to achieve this, complete graphs with edges annotated by distances are commonly used~\citep{Kri+2012,Gil+2017}.
-Our collection contains the four datasets \textsc{Bzr}, \textsc{Cox2}, \textsc{Dhfr}, \textsc{Er} initially published by \citet{Sut+2003} in two versions, with 3d coordinates of atoms and inter-atom distances, respectively, cf.~\citep{Mah+2006,Kri+2012}.
-
-\paragraph{Bioinformatics.}
+\xhdr{Bioinformatics.}
 The datasets \textsc{DD}, \textsc{Enzymes} and \textsc{Proteins} represent macromolecules.
@@
 Two nodes are connected by an edge if they are neighbors along the amino acid sequence or one of three nearest neighbors in space.
-Using this approach, the dataset \textsc{Enzymes} was derived from the BRENDA database~\citep{Schomburg2004}.
+Using this approach, the dataset \textsc{Enzymes} was derived from the \textsc{Brenda} database~\cite{Schomburg2004}.
 Here, the task is to assign enzymes to one of the 6 EC top level classes, which reflect the chemical reaction they catalyze.
@@
 
-\paragraph{Computer vision.}
+\xhdr{Computer vision.}
 Graph-based methods are widely used in computer vision for various tasks using diverse graph models.
 Our collection provides several datasets originating from the \emph{IAM Graph Database}~\citep{Riesen2008} such as \textsc{Letter} and \textsc{Fingerprint}.
-Other datasets represent \textsc{Cuneiform} signs~\citep{Kriege2018}, 3d point clouds for robot grasping tasks (\textsc{FirstMM\_DB}) and semantic image processing (\textsc{Msrc})~\citep{Neu+2016}.
+Other datasets represent \textsc{Cuneiform} signs~\citep{Kriege2018}, 3D point clouds for robot grasping tasks (\textsc{FirstMM\_DB}) and semantic image processing (\textsc{Msrc})~\cite{Neu+2016}.
 
-\paragraph{Social networks.}
+\xhdr{Social networks.}
 \citet{Yan+2015a} introduced several graph classification datasets derived from social networks.
@@
 \textsc{Collab} is dataset derived from scientific collaboration networks.
-Each graph is the ego-network of a researcher and the task is to predict his research field, i.e., High Energy, Condensed Matter or Astro Physics.
+Each graph is the ego-network of a researcher and the task is to predict his research field, i.e., high energy, condensed matter or astro physics.
 Similarly, the \textsc{Imdb} datasets consist of ego-networks derived from actor collaborations and the task is to predict the genre, e.g.,  Action vs.\@ Romance.
@@
 
-\paragraph{Synthetic.}
+\xhdr{Synthetic.}
 Several graph datasets contain synthetic instances that where typically generated to demonstrate the strengths or weaknesses of specific methods.
@@
 To provide meaningful baselines, we provide implementations of common graph kernel as well as GNNs baselines.
-We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} \nk{Das ist eine Variante mit Labeln und 3 Knoten oder?
-CM: Ja}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel, as well as the higher-order WL kernels~\cite{Mor+2019b}, in \CPP and made them accessible through the Python interface of \textsc{Tud dataset}, see the website for further details.
-Moreover, all GNN architectures provided by PyTorch Geometric can be conveniently used as a baseline as well.
+We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel, as well as the higher-order WL kernels~\cite{Mor+2019b}, in \CPP and made them accessible through the Python interface of \textsc{TuDataset}, see the website for further details.
+Moreover, all GNN architectures provided by \textsc{PyTorch Geometric} can be conveniently used as a baseline as well.
 
@@
 To ensure a fair and meaningful comparison between methods, we propose the following evaluation procedures for kernels and GNN approaches.
-All proposed methods can be conveniently accessed from the Python interface, see the website for further details.
+All proposed methods and evaluation tools can be conveniently accessed from the Python interface, see the appendix for further details.
 First, for kernels we propose the established $C$-SVM implementation \textsc{LibSvm}~\cite{Cha+11} for kernels that compute a Gram matrix, and the linear $C$-SVM implementation \textsc{LibLinear}~\cite{Fan+2008} for kernels  that can be computed based on sparse, explicit feature maps.
-We optimize GNNs end-to-end using \textsc{Adam}~\cite{}.
-Too compute accuracies and MAE, we propose to use $10$-fold cross-validation, where we select a validation set uniformly at random from each training fold ($10\%$ of the training fold), to select hyperparameters, e.g., number of iterations, $C$ parameter, number of layers, feature dimension, dots Moreover, we repeat the above evaluation ten times and report standard deviations over all ten repetitions, and additionally across all one hundred runs (i.e., ten repetitions with ten folds each.).
-See the appendix for examples balbalb
+We optimize GNNs end-to-end using \textsc{Adam}~\cite{Kin+2015}.
+To compute classification accuracies, we propose to use $10$-fold cross-validation, where we select a validation set uniformly at random from each training fold ($10\%$ of the training fold), to select hyperparameters, e.g., number of iterations, $C$ parameter, number of layers, feature dimension, \dots.
+Moreover, we repeat the above evaluation ten times and report standard deviations over all ten repetitions, and additionally across all one hundred runs (i.e., ten repetitions with ten folds each.).
+For the large-scale molecule learning tasks, we either use random splits (80\%/10\%/10\%) or provided, fixed splits, and report MAE (mean std.
+MAE, mean std.
+logMAE for multi-target regression, see \cite{Kli+2020}) over five runs.
 

### 2020-06-06 main.tex
MC.

@@
 \xhdr{Small molecules.} 
-A common class of graph datasets consist of small molecules with class labels representing, e.g., toxicity or biological activity.
+A common class of graph datasets consists of small molecules with class labels representing, e.g., toxicity or biological activity.
 Here, a graph encodes a molecule, i.e., nodes take the places of atoms and edges that of chemical bonds.
 Consequently, the labels encode atom and bond types, with possibly additional chemical attributes.
-The graph models differs, e.g., in whether hydrogen atoms are represented explicitly by nodes, and bonds in aromatic rings are annotated accordingly.
+The graph models differ, e.g., in whether hydrogen atoms are represented explicitly by nodes, and bonds in aromatic rings are annotated accordingly.
 
@@
 Moreover, our collection also contain large-scale molecular regression tasks such as \textsc{Alchemy}~\cite{Che+2020}, \textsc{Qm9}~\cite{Ram+2014}, and \textsc{ZINC}~\cite{Dwi+2020,Jin+2018a}.
-For the two former we also provide 3D coordinates which are crucual to study rotation-invariant GNN architectures.
+For the two formers, we also provide 3D coordinates, which are crucial to study rotation-invariant GNN architectures.
 
@@
 The datasets \textsc{DD}, \textsc{Enzymes} and \textsc{Proteins} represent macromolecules.
-\citet{Bor+2005a} introduced a graph model for proteins, where nodes represent secondary structure elements and are annotated by their type, i.e., helix, sheet or turn, as well as several physical and chemical information.
-Two nodes are connected by an edge if they are neighbors along the amino acid sequence or one of three nearest neighbors in space.
+\citet{Bor+2005a} introduced a graph model for proteins, where nodes represent secondary structure elements and are annotated by their type, i.e., helix, sheet, or turn, as well as several physical and chemical information.
+An edge connects two nodes if they are neighbors along the amino acid sequence or one of three nearest neighbors in space.
 Using this approach, the dataset \textsc{Enzymes} was derived from the \textsc{Brenda} database~\cite{Schomburg2004}.
-Here, the task is to assign enzymes to one of the 6 EC top level classes, which reflect the chemical reaction they catalyze.
-Similarly, the dataset \textsc{Proteins} was derived from \citep{Dob+2003} and comes with the task to predict whether a protein is an enzyme.
-The dataset \textsc{DD} used by \citet{She+2011} is based on the same data, but contains graphs, where nodes represent individual amino acids and edges their spatial proximity.
+Here, the task is to assign enzymes to one of the 6 EC top-level classes, which reflect the catalyze chemical reaction.
+Similarly, the dataset \textsc{Proteins} was derived from \citep{Dob+2003}, and the task is to predict whether a protein is an enzyme.
+The dataset \textsc{DD} used by \citet{She+2011} is based on the same data but contains graphs, where nodes represent individual amino acids and edges their spatial proximity.
 
@@
 \citet{Yan+2015a} introduced several graph classification datasets derived from social networks.
-In the \textsc{Reddit} datasets each graph represents a discussion thread, where nodes correspond to users, two of which are connected by an edge, if one responded to a comment of the other.
+In the \textsc{Reddit} datasets, each graph represents a discussion thread, where nodes correspond to users, two of which are connected by an edge if one responded to a comment of the other.
 This graph model is used to derive several datasets, where the classification task is to distinguish either discussion-based and question/answer-based subreddits (\textsc{Reddit-Binary}) or predict the subreddit, where the thread was posted (\textsc{Reddit-Multi-5K} and \textsc{Reddit-Multi-12K}).
-\textsc{Collab} is dataset derived from scientific collaboration networks.
-Each graph is the ego-network of a researcher and the task is to predict his research field, i.e., high energy, condensed matter or astro physics.
-Similarly, the \textsc{Imdb} datasets consist of ego-networks derived from actor collaborations and the task is to predict the genre, e.g.,  Action vs.\@ Romance.
-Similar approaches were used by~\citet{Rozemberczki2020} to obtain larger social network datasets.
-\textsc{Reddit\_Threads} contains more than 200k graphs with the task to predict whether a thread is discussion based.
-\textsc{Deezer\_Ego\_Nets} and \textsc{Twitch\_Egos} contain ego-networks derived from online services and the task is to predict the gender and play beahavior (single or multiple games) of the central user.
-\textsc{GitHub\_Stargazers} contains graphs representing the social networks of GitHub users divided into those who starred popular machine learning and web development repositories.
+\textsc{Collab} are datasets derived from scientific collaboration networks.
+Each graph is the ego-network of a researcher, and the task is to predict his research field, i.e., high energy, condensed matter, or astrophysics.
+Similarly, the \textsc{Imdb} datasets consist of ego-networks derived from actor collaborations, and the task is to predict the genre, e.g.,  Action vs.\@ Romance.
+\citet{Rozemberczki2020} used similar approaches to obtain more massive social network datasets.
+\textsc{Reddit\_Threads} contains more than 200k graphs with the task to predict whether a thread is discussion-based.
+\textsc{Deezer\_Ego\_Nets} and \textsc{Twitch\_Egos} contain ego-networks derived from online services, and the task is to predict the gender and play behavior (single or multiple games) of the central user.
+\textsc{GitHub\_Stargazers} contains graphs representing the social networks of GitHub users divided into those who starred in popular machine learning and web development repositories.
 
@@
 \xhdr{Synthetic.}
-Several graph datasets contain synthetic instances that where typically generated to demonstrate the strengths or weaknesses of specific methods.
+We also provide several synthetic graph datasets to demonstrate the strengths or weaknesses of specific methods.
 The datasets \textsc{SyntheticNew} and \textsc{SyntheticNew} were created by \citet{Fer+2013} (see Erratum) and \citet{Mor+2016}, respectively, to demonstrate the ability of kernels to operate on graphs with continuous attributes.
-With the same goal, the dataset \textsc{Frankenstein} was obtained from a small molecule dataset by replacing the atom labels by MNIST digit images~\citep{Ors+2015}
-
 \citet{Knyazev2019} introduced the datasets \textsc{Colors} and \textsc{Triangles}, where the task is to count the number of nodes with a given one-hot-encoded color and the number of triangles, respectively.
-These classification tasks were considered particularly challenging for graph neural networks.
 
@@
 To provide meaningful baselines, we provide implementations of common graph kernel as well as GNNs baselines.
-We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel, as well as the higher-order WL kernels~\cite{Mor+2019b}, in \CPP and made them accessible through the Python interface of \textsc{TuDataset}, see the website for further details.
+We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{TuDataset}, see the website for further details.
 Moreover, all GNN architectures provided by \textsc{PyTorch Geometric} can be conveniently used as a baseline as well.
@@
 Moreover, we repeat the above evaluation ten times and report standard deviations over all ten repetitions, and additionally across all one hundred runs (i.e., ten repetitions with ten folds each.).
-For the large-scale molecule learning tasks, we either use random splits (80\%/10\%/10\%) or provided, fixed splits, and report MAE (mean std.
+For the large-scale molecule learning tasks, we either use random splits (80\%/10\%/10\%) or provided, fixed splits and report MAE (mean std.
 MAE, mean std.
@@
 
-\cm{work on this}
-
-Our intention here is to provide baseline experiments and compare graph kernels and GNNs. More precisely, we address the following questions:
-\begin{description}
-	\item[Q1] Are GNNs superior to graph kernels? Is there a single method that dominates?
-	\item[Q2] How do kernels compare to GNNs on large-scale molecular learning tasks.
-\end{description}
-
+Our intention here is to provide baseline experiments and compare graph kernels and GNNs
 \subsection{Experimental protocol}
-
 We used the following datasets, graph kernels, and GNN baselines.
 
-\paragraph{Datasets.} We used the \textsc{deezer\_ego\_nets}, \textsc{github\_stargazers}, \textsc{Enymes},
+\xhdr{Datasets.} We used the \textsc{deezer\_ego\_nets}, \textsc{github\_stargazers}, \textsc{Enymes},
 \textsc{Imdb-BINARY}, \textsc{Imdb-MULTI}, \textsc{Mcf-7}, \textsc{Molt-4},	\textsc{Nci1}, \textsc{Proteins},
@@
 
-We gave an overview of the \textsc{Tud dataset}, and reported on the results of an experimental study comparing graph kernels and GNNs on a subset of the data.
+We gave an overview of the \textsc{TuDataset}, and reported on the results of an experimental study comparing graph kernels and GNNs on a subset of the data.
 We believe that our dataset collection will spark further progress in the area of graph represention learning.
@@
 
-We thank everybody who provided datasets for \textsc{Tud dataset}.
+We thank everybody who provided datasets for \textsc{TuDataset}.
 

### 2020-06-07 main.tex
fff

@@
 
-\icmltitlerunning{TUD Datasets}
+\icmltitlerunning{TUDatasets}
 
@@
 Moreover, the datasets proposed in~\cite{Fer+2019} focuses on instances from planning competitions.
+http://www.jmlr.org/papers/volume21/18-370/18-370.pdf
 
@@
 \subsection{Datasets}
+
+\begin{table*}[ht]\centering		
+	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
+	\label{t2l}	
+	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{.9}
+		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule
+
+			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
+			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule
+
+			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &   $52.3$ \scriptsize $\pm 0.7 \pm 6.7 $       & $72.6$ \scriptsize $\pm  0.6 \pm 4.1$ &  $50.3$ \scriptsize $\pm 0.8 \pm  3.8 $ & $84.5$ \scriptsize $\pm 0.3 \pm 1.7$ & $72.8$ \scriptsize $\pm 0.8 \pm  3.9 $ & $73.9$ \scriptsize $\pm 0.6 \pm 3.2$  \\
+			%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+			%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+			& \text{WLOA} & $58.4$ \scriptsize $\pm 2.0 \pm 7.4$       &  $73.2$ \scriptsize $\pm 0.8 \pm 3.8$ & $49.4$ \scriptsize $\pm 0.3 \pm 3.6 $ & $85.4$ \scriptsize $\pm  0.2 \pm 1.4$ & $73.2$ \scriptsize $\pm 0.6 \pm 3.5$ & $88.4$ \scriptsize $\pm 0.4 \pm 2.1 $   \\
+			& \text{GR}            &    $30.1$ \scriptsize $\pm 0.8 \pm 6.0$       & $59.0$ \scriptsize $\pm 0.9 \pm 5.7$ & $39.6$ \scriptsize $\pm 0.5 \pm 3.6  $ & $66.2$ \scriptsize $\pm 0.2\pm 2.2$ & $71.4$ \scriptsize $\pm 0.6\pm 4.4 $ & $60.0$ \scriptsize $\pm 0.2 \pm  2.7$   \\
+			& \text{SP}            & $40.5$  \scriptsize $\pm 1.6 \pm 6.2$       & $58.7$ \scriptsize $\pm 0.9 \pm 4.6 $ & $39.5$ \scriptsize $\pm 0.9 \pm 4.2$ & $74.5$ \scriptsize $\pm 0.4\pm 2.2 $  &$75.9$ \scriptsize $\pm 0.6 \pm 4.0$ & $84.6$ \scriptsize $\pm0.2\pm 0.4 $  \\
+			\cmidrule{2-8}	
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \textsc{Gin-$\varepsilon$}   &   \scriptsize $\pm \pm $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
+			& \textsc{Gin-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
+			\bottomrule
+	\end{tabular}}
+\end{table*}		
+\begin{table*}[t]\centering		
+	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
+	\label{t2l}	
+	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{.9}
+		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
+			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
+			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Yeast}}           & {\textsc{github\_star.}}       & {\textsc{reddit\_threads}}      \\	\toprule
+			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
+			$94.5$ \scriptsize $<0.1 \pm 0.4$  &$94.6$ \scriptsize $\pm 0.1  \pm 0.3$ & $89.2$ \scriptsize $\pm 0.1 \pm 0.4$ &  $63.9$ \scriptsize $\pm 0.1\pm 1.3$ &$77.0$ \scriptsize $<0.1 \pm 0.3$  \\
+
+			& \text{GR}            & $91.7$  \scriptsize $<0.1  \pm 0.5 $       & $92.1$ \scriptsize $<0.1 \pm 0.4$ & $88.2$ \scriptsize $<0.1  \pm 0.4$ &  $53.5$ \scriptsize $<0.1 \pm 1.3$ & $51.2$ \scriptsize $<0.1 \pm 0.4$  \\
+			& \text{SP}             &  $91.7$  \scriptsize $<0.1 \pm 0.4 $       &$92.1$  \scriptsize $<0.1 \pm 0.4 $ & $88.2$ \scriptsize $<0.1  \pm 0.4$ & $64.1$ \scriptsize $\pm 0.1\pm 1.4$ & $77.3$ \scriptsize $<0.1 \pm 0.3$  \\
+			\cmidrule{2-7}	
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \textsc{Gine-$\varepsilon$}         &  $92.0$ \scriptsize $\pm  0.1 \pm 0.6$       & $92.3$ \scriptsize $\pm 0.1 \pm 0.6$ & 88.3 \scriptsize $<0.1 \pm 0.3$ &  $67.1$ \scriptsize $\pm 0.5 \pm 1.6  $ & $77.2$ \scriptsize $<0.1  \pm 0.3$ \\
+			& \textsc{Gine-$\varepsilon$-JK}   &   $91.8$ \scriptsize $<0.1 \pm 0.5$       & $92.2$ \scriptsize $<0.1 \pm 0.5$ & 88.2  \scriptsize $<0.1 \pm 0.3$ & $67.2$ \scriptsize $\pm 0.4 \pm 1.3$ &  $77.3$  \scriptsize $<0.1 \pm 0.3 $  \\
+			\bottomrule
+	\end{tabular}}
+\end{table*}
 
@@
 
-\subsection{Baselines Methods}
-
-To provide meaningful baselines, we provide implementations of common graph kernel as well as GNNs baselines.
+\xhdr{Baselines methods.} To provide meaningful baselines, we provide implementations of common graph kernel as well as GNNs baselines.
 We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{TuDataset}, see the website for further details.
@@
 
-\subsection{Evaluation Methods}\label{eval}
-
-To ensure a fair and meaningful comparison between methods, we propose the following evaluation procedures for kernels and GNN approaches.
+\xhdr{Evaluation methods.}\label{eval} To ensure a fair and meaningful comparison between methods, we propose the following evaluation procedures for kernels and GNN approaches.
 All proposed methods and evaluation tools can be conveniently accessed from the Python interface, see the appendix for further details.
@@
 
+\begin{table}[]\centering	
+	\caption{Mean MAE (mean std. MAE, logMAE) on large-scale (multi-target) molecular regression tasks.\label{neural_short_tt}}
+	\resizebox{.75\columnwidth}{!}{\renewcommand{\arraystretch}{1.0}
+		\begin{tabular}{lcc}	\toprule
+			\multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{2}{c}{\textbf{Dataset}}\\\cmidrule{2-3}
+			& {\textsc{Zinc}}     & {\textsc{alchemy}}   \\	\toprule
+			\textsc{Gine-$\varepsilon$}    & 0.084                                                                                                                                                                                                                                     \scriptsize $\pm 0.004$   &                                                                                                                                                                                                                                0.103 {\scriptsize $\pm 0.001$} -2.956 {\scriptsize $\pm 0.029$} \\
+			\bottomrule
+	\end{tabular}}
+\end{table}
+
 \section{Experimental evaluation}
 
-Our intention here is to provide baseline experiments and compare graph kernels and GNNs
-\subsection{Experimental protocol}
+Our intention here is to provide baseline experiments and compare graph kernels and GNNs.
+See the appendix for detailed experimental protocal.
 We used the following datasets, graph kernels, and GNN baselines.
 
-\xhdr{Datasets.} We used the \textsc{deezer\_ego\_nets}, \textsc{github\_stargazers}, \textsc{Enymes},
-\textsc{Imdb-BINARY}, \textsc{Imdb-MULTI}, \textsc{Mcf-7}, \textsc{Molt-4},	\textsc{Nci1}, \textsc{Proteins},
-\textsc{Reddit-Binary},	\textsc{reddit\_threads}, \textsc{twitch\_egos}, \textsc{Uacc257}. See the website for dataset statistics.
-\cm{ZINC ALche}
+\xhdr{Datasets.} We used the \textsc{deezer\_ego\_nets}, \textsc{github\_stargazers}, \textsc{Enymes}, \textsc{Imdb-Binary}, \textsc{Imdb-Multi}, \textsc{Mcf-7}, \textsc{Molt-4},	\textsc{NCI1}, \textsc{Proteins},
+\textsc{Reddit-Binary},	\textsc{reddit\_threads}, \textsc{twitch\_egos}, \textsc{Uacc257} graph classification datasets, and the \textsc{Alchemy}, \textsc{QM9}, \textsc{Zinc} (multi-target) regression datasets.
+See the website for dataset statistics.
 
-\paragraph{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} \textsc{WL-OA}~\cite{Kri+2016}, and $\delta$-$2$-LWL$^+$ kernel~\cite{Mor+2019b} included in the \textsc{TUD Dataset} package.
+\xhdr{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} \textsc{WL-OA}~\cite{Kri+2016} included in the \textsc{TUDataset} package.
 The $C$-parameter was selected from $\{10^{-3}, 10^{-2}, \dotsc, 10^{2},$ $10^{3}\}$ from the validation set.
 For the larger datasets, we computed sparse feature vectors for each graph and used the linear $C$-SVM implementation of \text{Liblinear}~\cite{Fan+2008}.
-The number of iterations of the \textsc{$1$-WL}, \textsc{WL-OA}, and the  $\delta$-$2$-LWL$^+$ were selected from $\{0,\dotsc,5\}$.\footnote{As already shown in~\cite{She+2011}, choosing the number of iterations too large will lead to overfitting.}\cm{Cite sklearn}
+The number of iterations of the \textsc{$1$-WL}, \textsc{WL-OA}, and the  $\delta$-$2$-LWL$^+$ were selected from $\{0,\dotsc,5\}$.\footnote{As already shown in~\cite{She+2011}, choosing the number of iterations too large will lead to overfitting.}
 
-\paragraph{GNNs.} We used the GNN architectures \textsc{GCN}~\cite{Kip+2017}, \textsc{Sage}~\cite{Ham+2017}, \textsc{Gin} and \textsc{Gin-$\varepsilon$}~\cite{Xu+2018b} as neural baselines.
-For all experiments, we used the global mean operator to obtain graph-level outputs.
-For each dataset, we optimize the number of hidden units from $
-\{16, 32, 64, 128\}$, the number of layers from $ \{2, 3, 4, 5\}$ and the learning rate from $ \{0.0001, 0.001, 0.01 \}$ with respect to the validation set.
-The batch size was fixed to $128$.\cm{change this }
+All kernel experiments were conducted on a workstation with an \text{Intel Xeon E5-2690v4} with 2.60\si GHz and 384\si GB of RAM running \text{Ubuntu 16.04.6 LTS} using a single core.
+Moreover, we used the GNU \CC Compiler 5.5.0 with the flag \texttt{--O2}.
 
-For both methods, we used the evaluation procecude described in~\cref{eval} to optimize hyperparameters and compute accuracies.
-All experiments can be reproduced using the scripts provided at \url{XXX}.
+\xhdr{GNNs.} 
+For comparision with kernel methods, we used \textsc{Gin-$\varepsilon$}~\cite{Xu+2018b} and \textsc{Gin-$\varepsilon$-JK} with jumping knowledge networks as a neural baselines~\cite{Xu+2018}.
+For data with (continuous) edge features, we used a $2$-layer MLP to map them to the same number of components as the node features and combined them using summation (\textsc{Gine-$\varepsilon$} and \textsc{Gine-$\varepsilon$}-JK).
+We used mean pooling to pool the learned node embeddings to a graph embedding and used $2$-layer MLP for the final classification, using a dropout layer with $p = 0.5$ after the first layer of the MLP.
+We optimized the number of hidden units from $
+\{ 32, 64, 128\}$, the number of layers from $ \{1, 2, 3, 4, 5\}$ using the validation set.
+Moreover, we use learning rate decay of $0.5$ with a patience parameter of $5$ with starting learning rate of $0.01$ and a minimum of $10^{-6}$.
+For both methods, we used the evaluation procedute described in~\cref{eval} to optimize hyperparameters and compute accuracies.
+See the appendix for details on the hyperparameter and evaluation protocols used for the larger molecular regression tasks, \textsc{Zinc} and \textsc{Alchemy}.
 
-\cm{Add regression}
+All results can be reproduced using the scripts provided at \url{www.github.com/chrsmrrs/tudataset}.
 
@@
 See~\cref{t2l}.
-
-\begin{table*}[t]\centering		
-	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
-	\label{t2l}	
-	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
-		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule
-
-			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
-			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule
-
-			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &   $52.3$ \scriptsize $\pm 0.7 \pm 6.7 $       & $72.6$ \scriptsize $\pm  0.6 \pm 4.1$ &  $50.3$ \scriptsize $\pm 0.8 \pm  3.8 $ & $84.5$ \scriptsize $\pm 0.3 \pm 1.7$ & $72.8$ \scriptsize $\pm 0.8 \pm  3.9 $ & $73.9$ \scriptsize $\pm 0.6 \pm 3.2$  \\
-%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-				& \text{WLOA} & $58.4$ \scriptsize $\pm 2.0 \pm 7.4$       &  $73.2$ \scriptsize $\pm 0.8 \pm 3.8$ & $49.4$ \scriptsize $\pm 0.3 \pm 3.6 $ & $85.4$ \scriptsize $\pm  0.2 \pm 1.4$ & $73.2$ \scriptsize $\pm 0.6 \pm 3.5$ & $88.4$ \scriptsize $\pm 0.4 \pm 2.1 $   \\
-				& \text{GR}            &    $30.1$ \scriptsize $\pm 0.8 \pm 6.0$       & $59.0$ \scriptsize $\pm 0.9 \pm 5.7$ & $39.6$ \scriptsize $\pm 0.5 \pm 3.6  $ & $66.2$ \scriptsize $\pm 0.2\pm 2.2$ & $71.4$ \scriptsize $\pm 0.6\pm 4.4 $ & $60.0$ \scriptsize $\pm 0.2 \pm  2.7$   \\
-				& \text{SP}            & $40.5$  \scriptsize $\pm 1.6 \pm 6.2$       & $58.7$ \scriptsize $\pm 0.9 \pm 4.6 $ & $39.5$ \scriptsize $\pm 0.9 \pm 4.2$ & $74.5$ \scriptsize $\pm 0.4\pm 2.2 $  &$75.9$ \scriptsize $\pm 0.6 \pm 4.0$ & $84.6$ \scriptsize $\pm0.2\pm 0.4 $  \\
-			\cmidrule{2-8}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GINE-$\varepsilon$}   &   \scriptsize $\pm \pm $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
-		& \text{GINE-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
-		\bottomrule
-	\end{tabular}}
-\end{table*}
-
-\begin{table*}[t]\centering		
-	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
-	\label{t2l}	
-	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
-		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
-			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
-			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Yeast}}           & {\textsc{github\_stargazers}}       & {\textsc{reddit\_threads}}      \\	\toprule
-							\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
-							   $94.5$ \scriptsize $<0.1 \pm 0.4$  &$94.6$ \scriptsize $\pm 0.1  \pm 0.3$ & $89.2$ \scriptsize $\pm 0.1 \pm 0.4$ &  $63.9$ \scriptsize $\pm 0.1\pm 1.3$ &$77.0$ \scriptsize $<0.1 \pm 0.3$  \\
-
-			& \text{GR}            & $91.7$  \scriptsize $<0.1  \pm 0.5 $       & $92.1$ \scriptsize $<0.1 \pm 0.4$ & $88.2$ \scriptsize $<0.1  \pm 0.4$ &  $53.5$ \scriptsize $<0.1 \pm 1.3$ & $51.2$ \scriptsize $<0.1 \pm 0.4$  \\
-			& \text{SP}             &  $91.7$  \scriptsize $<0.1 \pm 0.4 $       &$92.1$  \scriptsize $<0.1 \pm 0.4 $ & $88.2$ \scriptsize $<0.1  \pm 0.4$ & $64.1$ \scriptsize $\pm 0.1\pm 1.4$ & $77.3$ \scriptsize $<0.1 \pm 0.3$  \\
-			\cmidrule{2-7}	
-	\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GIN-E-$\varepsilon$}         &  $92.0$ \scriptsize $\pm  0.1 \pm 0.6$       & $92.3$ \scriptsize $\pm 0.1 \pm 0.6$ & \scriptsize $\pm \pm$ &  $67.1$ \scriptsize $\pm 0.5 \pm 1.6  $ & $77.2$ \scriptsize $<0.1  \pm 0.3$ \\
-	& \text{GINE-$\varepsilon$-JK}   &   $91.8$ \scriptsize $<0.1 \pm 0.5$       & $92.2$ \scriptsize $<0.1 \pm 0.5$ & \scriptsize $\pm \pm$ & $67.2$ \scriptsize $\pm 0.4 \pm 1.3$ &  $77.3$  \scriptsize $<0.1 \pm 0.3 $  \\
-\bottomrule
-	\end{tabular}}
-\end{table*}
-
-Yeast GINE 88.31840671346515 0.003881831878911156 0.32166787163196536
-Yeast GINEWithJK 88.18231308533625 0.04015610969845854 0.3325038752499045
-
-\begin{table}[t]\centering	
-	\cm{Maybe add qm9}	
-	\caption{Results for neural and kernel baselines.}
-	\label{t2l}	
-	\resizebox{0.55\columnwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
-		\begin{tabular}{@{}c <{\enspace}@{}lcc@{}}	\toprule
-
-			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{2}{c}{\textbf{Dataset}}\\\cmidrule{3-4}
-			&  & {\textsc{Zinc}}         &  {\textsc{Alchemy}}         \\	
-			\toprule
-			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}             &      \scriptsize $$ &  \scriptsize $$  \\  
-				& \text{GR}            &\scriptsize $ $ &  \scriptsize $ $  \\  
-			& \text{SP}             &   \scriptsize $ $  &  \scriptsize $ $ \\   
-			\cmidrule{2-4}
-			\multirow{2}{*}{\rotatebox{90}{}} & \text{$1$-GNN-E}             &   \scriptsize $\pm $  & \scriptsize $\pm   $		\\	
-			\bottomrule
-	\end{tabular}}
-\end{table}
 
@@
 \onecolumn
+
 \section{Evaluation Method Examples}
@@
 
+\section{Experimental protocol and hyperparameters for \textsc{Zinc} and \textsc{Alchemy}}
+For the larger molecular regression tasks, \textsc{Zinc} and \textsc{Alchemy}, we closely followed the hyperparameters found in~\cite{Dwi+2020} and~\cite{Che+2020}, respectively, for the (\textsc{Gine-$\varepsilon$} layers.
+That is, for \textsc{Zinc}, we used four (\textsc{Gine-$\varepsilon$} layers with a hidden dimension of 256 followed by batch norm and a $4$-layer MLP for the joint regression of the twelve targets, after applying mean pooling.
+For \textsc{Alchemy} and \textsc{QM9}, we used six layers with 64 (hidden) node features and a set2seq layer~\cite{Vin+2016} for graph-level pooling, followed by a $2$-layer MLP for the joint regression of the twelve targets.
+
+For \textsc{Zinc}, we used the given train, validation split, test split, and report the MAE over the test set.
+For the \textsc{Alchemy} dataset, we uniformly and at random sampled 80\% of the graphs for training, and 10\% for validation and testing, respectively.
+Moreover, following~\cite{Che+2020,Gil+2017}, we normalized the targets of the training split to zero mean and unit variance.
+We used a single model to predict all targets.
+Following~\cite{Kli+2020}, we report mean standardized MAE and mean standardized logMAE.
+We repeated each experiment five times (with different random splits in case of \textsc{Alchemy}) and report average scores and standard deviations.
+All neural experiments were conducted on a workstation with four Nvidia Tesla V100 GPU cards with 32GB of GPU memory running Oracle Linux Server 7.7.
+
 \end{document}

### 2020-06-07 tud_benchmark/main_gnn.py

@@ -1,32 +1,34 @@
 import auxiliarymethods.datasets as dp
-from auxiliarymethods.gnn_evaluation import gnn_evaluation,gnn_evaluation_old
+import os.path as osp
+from auxiliarymethods.gnn_evaluation import gnn_evaluation, gnn_evaluation_old
 from gnn_baselines.gnn_architectures import GIN0, GIN, GINE, GINEWithJK
 
-import os.path as osp
 
 def main():
     num_reps = 10
     # NeuriPS stuff, ENZYMES
-    print("NeurIPS")
-
-    # Smaller datasets.
-    dataset = [["ENZYMES", True]]
-
-    results = []
-    for d, use_labels in dataset:
-        dp.get_dataset(d)
-
-        acc, s_1, s_2 = gnn_evaluation(GIN0, d, [1,2,3,4,5], [32,64,128], add_pool=False, max_num_epochs=200, batch_size=128,
-                                       start_lr=0.01, num_repetitions=num_reps, all_std=True)
-        print(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
-        results.append(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
-
-        acc, s_1, s_2 = gnn_evaluation(GIN, d, [1,2,3,4,5], [32,64,128], add_pool=False, max_num_epochs=200, batch_size=128,
-                                       start_lr=0.01, num_repetitions=num_reps, all_std=True)
-        print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
-        results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
-
-    exit()
+    # print("NeurIPS")
+    #
+    # # Smaller datasets.
+    # dataset = [["ENZYMES", True]]
+    #
+    # results = []
+    # for d, use_labels in dataset:
+    #     dp.get_dataset(d)
+    #
+    #     acc, s_1, s_2 = gnn_evaluation(GIN0, d, [1, 2, 3, 4, 5], [32, 64, 128], add_pool=False, max_num_epochs=200,
+    #                                    batch_size=128,
+    #                                    start_lr=0.01, num_repetitions=num_reps, all_std=True)
+    #     print(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
[…]

### 2020-06-07 tud_benchmark/main_gnn.py
fff

@@ -94,8 +94,10 @@ def main():
 
     print("TUD")
     # Smaller datasets.
-    dataset = [["IMDB-BINARY", False], ["IMDB-MULTI", False], ["NCI1", True], ["PROTEINS", True],
-               ["REDDIT-BINARY", False], ["ENZYMES", True]]
+    # dataset = [["IMDB-BINARY", False], ["IMDB-MULTI", False], ["NCI1", True], ["PROTEINS", True],
+    #            ["REDDIT-BINARY", False], ["ENZYMES", True]]
+
+    dataset = [["ENZYMES", True]]
 
     results = []
     for d, use_labels in dataset:

### 2020-06-07 main.tex
MC.

@@
 	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
-	\label{t2l}	
+	\label{t2ll}	
 	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{.9}
@@
 For the larger datasets, we computed sparse feature vectors for each graph and used the linear $C$-SVM implementation of \text{Liblinear}~\cite{Fan+2008}.
-The number of iterations of the \textsc{$1$-WL}, \textsc{WL-OA}, and the  $\delta$-$2$-LWL$^+$ were selected from $\{0,\dotsc,5\}$.\footnote{As already shown in~\cite{She+2011}, choosing the number of iterations too large will lead to overfitting.}
+The number of iterations of the \textsc{$1$-WL} and \textsc{WL-OA} were selected from $\{0,\dotsc,5\}$.\footnote{As already shown in~\cite{She+2011}, choosing the number of iterations too large will lead to overfitting.}
 
@@
 \subsection{Results and discussion}
-See~\cref{t2l}.
+See~\cref{t2l,t2ll,neural_short_tt}.
+On the small-scale datasets, see \cref{t2l}, the \textsc{WLOA} performs best overall, i.e., only on the \textsc{IMDB-Binary} and the \textsc{Reddit-Binary} dataset it is beating by the the $1$-\textsc{WL} or the neural baselines.
+However, it does not scale midscale datasets, \cref{t2l}, as it relies on Gram matrix computation.
+Here, the $1$-WL performs, excluding \textsc{github\_stargazers}, where the neural baseline perform best overall.
 
@@
 For \textsc{Zinc}, we used the given train, validation split, test split, and report the MAE over the test set.
-For the \textsc{Alchemy} dataset, we uniformly and at random sampled 80\% of the graphs for training, and 10\% for validation and testing, respectively.
+For the \textsc{Alchemy} and \textsc{QM9} datasets, we uniformly and at random sampled 80\% of the graphs for training, and 10\% for validation and testing, respectively.
 Moreover, following~\cite{Che+2020,Gil+2017}, we normalized the targets of the training split to zero mean and unit variance.
@@
 We repeated each experiment five times (with different random splits in case of \textsc{Alchemy}) and report average scores and standard deviations.
+Moreover, we use learning rate decay of $0.5$ with a patience parameter of $5$ with starting learning rate of $0.001$ and a minimum of $10^{-6}$.
+
+For the \textsc{QM9} dataset, we additionally used the \textsc{MPNN}~\cite{Gil+2017} architecture as a baseline, closely following the setup of~\cite{Gil+2017}.
+For the (\textsc{Gine-$\varepsilon$}  and the \textsc{MPNN} architecture, following~\citeauthor{Gil+2017}~\cite{Gil+2017}, we used a complete graph, computed pairwise $\ell_2$ distances based on the 3D-coordinates, and concatenated them to the edge features.
+We note here that our intent is not the beat state-of-the-art, physical knowledge-incorporating architectures, e.g., \textsf{DimeNet}~\cite{Kli+2020} or \textsf{Cormorant}~\cite{And+2019}, but to solely provide baseline scores.
+
 All neural experiments were conducted on a workstation with four Nvidia Tesla V100 GPU cards with 32GB of GPU memory running Oracle Linux Server 7.7.

### 2020-06-07 main.tex
MC.

@@
 	\label{t2l}	
-	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{.9}
+	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
 		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule
@@
 	\label{t2ll}	
-	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{.9}
+	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
 		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
@@
 	\caption{Mean MAE (mean std. MAE, logMAE) on large-scale (multi-target) molecular regression tasks.\label{neural_short_tt}}
-	\resizebox{.75\columnwidth}{!}{\renewcommand{\arraystretch}{1.0}
-		\begin{tabular}{lcc}	\toprule
-			\multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{2}{c}{\textbf{Dataset}}\\\cmidrule{2-3}
-			& {\textsc{Zinc}}     & {\textsc{alchemy}}   \\	\toprule
-			\textsc{Gine-$\varepsilon$}    & 0.084                                                                                                                                                                                                                                     \scriptsize $\pm 0.004$   &                                                                                                                                                                                                                                0.103 {\scriptsize $\pm 0.001$} -2.956 {\scriptsize $\pm 0.029$} \\
+	\resizebox{1.0\columnwidth}{!}{\renewcommand{\arraystretch}{1.1}
+		\begin{tabular}{lccc}	\toprule
+			\multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{2}{c}{\textbf{Dataset}}\\\cmidrule{2-4}
+			& {\textsc{Zinc}}     & {\textsc{alchemy}}   & {\textsc{Qm9}}   \\	\toprule
+			\textsc{Gine-$\varepsilon$}    & 0.084                                                                                                                                                                                                                                     \scriptsize $\pm 0.004$   &                                                                                                                                                                                                                                0.103 {\scriptsize $\pm 0.001$} -2.956 {\scriptsize $\pm 0.029$} &  0.081 {\scriptsize $\pm 0.003$} -3.400 {\scriptsize $\pm  0.094 $}   \\
+			\textsc{MPNN}    & ---                                                                                                                                                                                                                                    & --- & 0.034 {\scriptsize $\pm 0.001$} {-4.156}{\scriptsize $\pm 0.030$}  \\
 			\bottomrule
@@
 
-All results can be reproduced using the scripts provided at \url{www.github.com/chrsmrrs/tudataset}.
+All results can be reproduced using the scripts provided at \url{www.github.com/XXX/XXX}.
 
@@
 Here, the $1$-WL performs, excluding \textsc{github\_stargazers}, where the neural baseline perform best overall.
+On the molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architecture such as \textsc{MPNN} can signifcant gains over the generic \textsc{Gin-$\varepsilon$} baseline.
 
@@
 
-We thank everybody who provided datasets for \textsc{TuDataset}.
+We thank everybody who provided datasets to the  \textsc{TuDataset} dataset collection.
 
@@
 For the \textsc{QM9} dataset, we additionally used the \textsc{MPNN}~\cite{Gil+2017} architecture as a baseline, closely following the setup of~\cite{Gil+2017}.
-For the (\textsc{Gine-$\varepsilon$}  and the \textsc{MPNN} architecture, following~\citeauthor{Gil+2017}~\cite{Gil+2017}, we used a complete graph, computed pairwise $\ell_2$ distances based on the 3D-coordinates, and concatenated them to the edge features.
-We note here that our intent is not the beat state-of-the-art, physical knowledge-incorporating architectures, e.g., \textsf{DimeNet}~\cite{Kli+2020} or \textsf{Cormorant}~\cite{And+2019}, but to solely provide baseline scores.
+For the \textsc{Gine-$\varepsilon$}  and the \textsc{MPNN} architecture, following~\citeauthor{Gil+2017}~\cite{Gil+2017}, we used a complete graph, computed pairwise $\ell_2$ distances based on the 3D-coordinates, and concatenated them to the edge features.
+We note here that our intent is not the beat state-of-the-art, physical knowledge-incorporating architectures, e.g., \textsc{DimeNet}~\cite{Kli+2020} or \textsc{Cormorant}~\cite{And+2019}, but to solely provide baseline scores.
 

### 2020-06-07 main.tex
MC.

@@
 \begin{table*}[ht]\centering		
-	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
+	\caption{Classification accuracies in percent and standard deviations on small-scale datasets.}
 	\label{t2l}	
@@
 \begin{table*}[t]\centering		
-	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
+	\caption{Classification accuracies in percent and standard deviations on mid-scale datasets.}
 	\label{t2ll}	
@@
 \xhdr{Baselines methods.} To provide meaningful baselines, we provide implementations of common graph kernel as well as GNNs baselines.
-We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{TuDataset}, see the website for further details.
+We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{TuDataset}.
 Moreover, all GNN architectures provided by \textsc{PyTorch Geometric} can be conveniently used as a baseline as well.
+See~\cref{eval} for further details and example code.
 
@@
 	\caption{Mean MAE (mean std. MAE, logMAE) on large-scale (multi-target) molecular regression tasks.\label{neural_short_tt}}
-	\resizebox{1.0\columnwidth}{!}{\renewcommand{\arraystretch}{1.1}
+	\resizebox{1.0\columnwidth}{!}{\renewcommand{\arraystretch}{1.2}
 		\begin{tabular}{lccc}	\toprule
@@
 
-Our intention here is to provide baseline experiments and compare graph kernels and GNNs.
+Our intent here is to provide baseline experiments and compare graph kernels and GNNs.
 See the appendix for detailed experimental protocal.
@@
 See~\cref{t2l,t2ll,neural_short_tt}.
-On the small-scale datasets, see \cref{t2l}, the \textsc{WLOA} performs best overall, i.e., only on the \textsc{IMDB-Binary} and the \textsc{Reddit-Binary} dataset it is beating by the the $1$-\textsc{WL} or the neural baselines.
+On the small-scale datasets, see \cref{t2l}, the \textsc{WLOA} performs best overall, i.e., only on the \textsc{IMDB-Binary} and the \textsc{Reddit-Binary} dataset it is beaten by the $1$-\textsc{WL} or the neural baselines.
 However, it does not scale midscale datasets, \cref{t2l}, as it relies on Gram matrix computation.
 Here, the $1$-WL performs, excluding \textsc{github\_stargazers}, where the neural baseline perform best overall.
-On the molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architecture such as \textsc{MPNN} can signifcant gains over the generic \textsc{Gin-$\varepsilon$} baseline.
+On the molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architecture such as \textsc{MPNN} result in signifcant gains over the generic \textsc{Gin-$\varepsilon$} baseline.
 
@@
 We gave an overview of the \textsc{TuDataset}, and reported on the results of an experimental study comparing graph kernels and GNNs on a subset of the data.
-We believe that our dataset collection will spark further progress in the area of graph represention learning.
-We are looking forward to adding more dataset to our collection, and are excited about contributions from the community, and reseachers and practitionors from other areas.
+We believe that our dataset collection will spark further progress in the area of graph represention learning, are looking forward to adding more dataset, and are excited about contributions from the community, and reseachers and practitionors from other areas.
 
@@
 
-\section{Evaluation Method Examples}
+\section{Evaluation examples}
+
+\xhdr{Kernel with kernelized SVM}
 \lstinputlisting[language=Python]{example.py}
-\cm{Add linear svm and GNN example}
 
-\section{Experimental protocol and hyperparameters for \textsc{Zinc} and \textsc{Alchemy}}
+\xhdr{Sparse feature maps with linear SVM}
+\lstinputlisting[language=Python]{example_sparse.py}
+
+\xhdr{GNN evaluation}
+\lstinputlisting[language=Python]{example_gnn.py}
+
+\section{Experimental protocol and hyperparameters for \textsc{Zinc}, \textsc{Alchemy}, \textsc{QM9}}
 For the larger molecular regression tasks, \textsc{Zinc} and \textsc{Alchemy}, we closely followed the hyperparameters found in~\cite{Dwi+2020} and~\cite{Che+2020}, respectively, for the (\textsc{Gine-$\varepsilon$} layers.

### 2020-06-07 example.py

@@ -1,19 +1,21 @@
-import kernel_baselines as kb
 import auxiliarymethods.auxiliary_methods as aux
 import auxiliarymethods.datasets as dp
+import kernel_baselines as kb
 from auxiliarymethods.kernel_evaluation import kernel_svm_evaluation
 
 # Download datasets.
 classes = dp.get_dataset("ENZYMES")
+use_labels, use_edge_labels = True, False
 
 all_matrices = []
 for i in range(1, 6):
     # Use node labels and no edge labels.
-    gm = kb.compute_wl_1_dense("ENZYMES", i, True, False)
+    gm = kb.compute_wl_1_dense("ENZYMES", i, use_labels, use_edge_labels)
     # Apply cosine normalization.
     gm = aux.normalize_gram_matrix(gm)
     all_matrices.append(gm)
 
 # Perform 10 repetions of 10-CV using LIBSVM.
-print(kernel_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True))
+print(kernel_svm_evaluation(all_matrices, classes,
+                            num_repetitions=10, all_std=True))
 

### 2020-06-07 example_gnn.py

@@ -1,0 +1,10 @@
+import auxiliarymethods.datasets as dp
+from auxiliarymethods.gnn_evaluation import gnn_evaluation
+from gnn_baselines.gnn_architectures import GIN
+
+dataset = "PROTEINS"
+use_labels = True
+dp.get_dataset(dataset)
+
+print(gnn_evaluation(GIN, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200,
+                     batch_size=128, start_lr=0.01, num_repetitions=10, all_std=True))

### 2020-06-07 example_sparse.py

@@ -1,0 +1,19 @@
+import auxiliarymethods.auxiliary_methods as aux
+import auxiliarymethods.datasets as dp
+import kernel_baselines as kb
+from auxiliarymethods.kernel_evaluation import linear_svm_evaluation
+
+classes = dp.get_dataset("MOLT-4")
+use_labels, use_edge_labels = True, True
+
+all_matrices = []
+for i in range(1, 6):
+    # Use node labels and edge labels.
+    gm = kb.compute_wl_1_sparse(dataset, i, use_labels, use_edge_labels)
+    # Apply \ell_2 normalization.
+    gm_n = aux.normalize_feature_vector(gm)
+    all_matrices.append(gm_n)
+
+# Perform 10 repetions of 10-CV using LIBINEAR.
+print(linear_svm_evaluation(all_matrices, classes,
+                            num_repetitions=num_reps, all_std=True))

### 2020-06-07 tud_benchmark/main_gnn.py

@@ -1,103 +1,15 @@
 import auxiliarymethods.datasets as dp
 import os.path as osp
 from auxiliarymethods.gnn_evaluation import gnn_evaluation, gnn_evaluation_old
-from gnn_baselines.gnn_architectures import GIN0, GIN, GINE, GINEWithJK
+from gnn_baselines.gnn_architectures import GIN, GINWithJK, GINE, GINEWithJK
 
 
 def main():
     num_reps = 10
-    # NeuriPS stuff, ENZYMES
-    # print("NeurIPS")
-    #
-    # # Smaller datasets.
-    # dataset = [["ENZYMES", True]]
-    #
-    # results = []
-    # for d, use_labels in dataset:
-    #     dp.get_dataset(d)
-    #
-    #     acc, s_1, s_2 = gnn_evaluation(GIN0, d, [1, 2, 3, 4, 5], [32, 64, 128], add_pool=False, max_num_epochs=200,
-    #                                    batch_size=128,
-    #                                    start_lr=0.01, num_repetitions=num_reps, all_std=True)
-    #     print(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #     results.append(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #
-    #     acc, s_1, s_2 = gnn_evaluation(GIN, d, [1, 2, 3, 4, 5], [32, 64, 128], add_pool=False, max_num_epochs=200,
-    #                                    batch_size=128,
-    #                                    start_lr=0.01, num_repetitions=num_reps, all_std=True)
-    #     print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #     results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #
-    # exit()
 
-    # results = []
-    # for d, use_labels in dataset:
-    #     dp.get_dataset(d)
-    #
-    #     acc, s_1, s_2 = gnn_evaluation(GIN0, d, [1, 2, 3, 4, 5], [32, 64, 128], add_pool=True, max_num_epochs=200, batch_size=128,
-    #                                    start_lr=0.01, num_repetitions=num_reps, all_std=True)
-    #     print(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #     results.append(d + " " + "GIN0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #
[…]

### 2020-06-07 tud_benchmark/main_kernel.py

@@ -9,7 +9,7 @@ def main():
 
     # Larger datasets using LIBLINEAR.
     results = []
-    num_reps= 3
+    num_reps= 10
 
     # all_matrices = []
     # gm = kb.compute_graphlet_sparse(dataset, use_labels, use_edge_labels)
@@ -107,65 +107,30 @@ def main():
     #     results.append(d + " " + "SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
     #
     # ####################################################################################################################
-    # Larger datasets using LIBLINEAR.
 
-    # num_reps= 3
-    # results  = []
-    #
-    # dataset = [["Yeast", True, True]]
-    #
-    # # dataset = [["MOLT-4", True, True], ["TRIANGLES", False, False], ["MCF-7", True, True],
-    # #              ["github_stargazers", False, False],
-    # #              ["reddit_threads", False, False]]
-    #
-    # for d, use_labels, use_edge_labels in dataset:
-    #     print(d)
-    #     dataset = d
-    #     classes = dp.get_dataset(dataset)
-    #
-    #     all_matrices = []
-    #     for i in range(1, 6):
-    #         gm = kb.compute_wl_1_sparse(dataset, i, use_labels, use_edge_labels)
-    #         gm_n = aux.normalize_feature_vector(gm)
-    #         all_matrices.append(gm_n)
-    #
-    #     acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=num_reps, all_std=True)
-    #     print(d + " " + "WL1SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #     results.append(d + " " + "WL1SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #
-    #     # all_matrices = []
-    #     # for i in range(1, 6):
-    #     #     gm = kb.compute_lwl_2_sparse(dataset, i, use_labels, use_edge_labels, False)
-    #     #     gm_n = aux.normalize_feature_vector(gm)
-    #     #     all_matrices.append(gm_n)
-    #     # acc, s_1, s_2 = linear_svm_evaluation(all_matrices, classes, num_repetitions=10, all_std=True)
-    #     # print(d + " " + "LWL2SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
[…]

### 2020-06-07 main.tex
MC.

@@
 
-\icmltitlerunning{TUDatasets}
+\icmltitlerunning{Anon}
 
@@
 \twocolumn[
-\icmltitle{TUDataset: A collection of benchmark datasets for learning with graphs}
+\icmltitle{\texttt{Anon}Dataset: A collection of benchmark datasets for learning with graphs}
 \icmlsetsymbol{equal}{*}
@@
 That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area.
-To address this, we introduce the \textsc{TuDataset} for graph classification and regression.
+To address this, we introduce the \textsc{\texttt{Anon}} for graph classification and regression.
 The dataset consists of over 120 datasets from a wide range of applications and varying sizes.
@@
 Here, we give an overview of the datasets, standardized evaluation procedures, and provide baseline experiments.
-All datasets are available at \url{www.graphlearning.io}.
-The experiments are fully reproducible from the code available at \url{www.github.com/chrsmrrs/tudatasets}.
+All datasets are available at \url{Anon}.
+The experiments are fully reproducible from the code available at \url{www.github.com/Anon}.
 \end{abstract}
@@
 \paragraph{Present work.} 
-Here, we give an overview of \textsc{TuDatasets}.
+Here, we give an overview of \textsc{\texttt{Anon}}.
 The benchmark collection consists of over 120 datasets from a wide range of domains for supervised learning with graphs, i.e., classification and regression.
-All datasets are provided in a standard dataset format at \url{graphlearning.io} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019} and \textsc{DGL}~\cite{Wan+2019}.
+All datasets are provided in a standard dataset format at \url{Anon} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019} and \textsc{DGL}~\cite{Wan+2019}.
 To facilitate standard comparison of kernel and neural approaches, we provide implementations of standard algorithms and easy-to-use evaluation procedures.
-Moreover, we report results on an experimental study comparing graph kernels and GNNs on a subset of the \textsc{TuDataset}.
+Moreover, we report results on an experimental study comparing graph kernels and GNNs on a subset of the \textsc{\texttt{Anon}}.
 
@@
 
-\section{The TUDataset collection}
+\section{The \texttt{Anon}Dataset collection}
 
-The \textsc{TuDataset} contains over 120 datasets provided at \url{graphlearning.io}.
-The data baseline methods and experimental evaluation tools can be installed by running \texttt{pip install tudatasets}.
+The \texttt{Anon} contains over 120 datasets provided at \texttt{Anon}.
+The data baseline methods and experimental evaluation tools can be installed by running \texttt{pip install Anon}.
 See the website for dataset statistics and documentation.
@@
 These datasets, the largest of which contain more than 79k graphs, are typically not balanced and contain far more small molecules that are identified as inactive against cancer cells.
-Moreover, our collection also contain large-scale molecular regression tasks such as \textsc{Alchemy}~\cite{Che+2020}, \textsc{Qm9}~\cite{Ram+2014}, and \textsc{ZINC}~\cite{Dwi+2020,Jin+2018a}.
+Moreover, our collection also contain large-scale molecular regression tasks such as \textsc{Alchemy}~\cite{Che+2020}, \textsc{Qm9}~\cite{Ram+2014}, and \textsc{Zinc}~\cite{Dwi+2020,Jin+2018a}.
 For the two formers, we also provide 3D coordinates, which are crucial to study rotation-invariant GNN architectures.
@@
 Graph-based methods are widely used in computer vision for various tasks using diverse graph models.
-Our collection provides several datasets originating from the \emph{IAM Graph Database}~\citep{Riesen2008} such as \textsc{Letter} and \textsc{Fingerprint}.
+Our collection provides several datasets originating from the \textsc{IAM Graph Database}~\citep{Riesen2008} such as \textsc{Letter} and \textsc{Fingerprint}.
 Other datasets represent \textsc{Cuneiform} signs~\citep{Kriege2018}, 3D point clouds for robot grasping tasks (\textsc{FirstMM\_DB}) and semantic image processing (\textsc{Msrc})~\cite{Neu+2016}.
@@
 \xhdr{Baselines methods.} To provide meaningful baselines, we provide implementations of common graph kernel as well as GNNs baselines.
-We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{TuDataset}.
+We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{\texttt{Anon}}.
 Moreover, all GNN architectures provided by \textsc{PyTorch Geometric} can be conveniently used as a baseline as well.
@@
 \end{table}		
-
 \section{Experimental evaluation}
 
-Our intent here is to provide baseline experiments and compare graph kernels and GNNs.
-See the appendix for detailed experimental protocal.
-We used the following datasets, graph kernels, and GNN baselines.
+Our intent here is to provide baseline experiments and compare graph kernels and GNNs. We used the following datasets, graph kernels, and GNN baselines.
 
@@
 
-\xhdr{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} \textsc{WL-OA}~\cite{Kri+2016} included in the \textsc{TUDataset} package.
+\xhdr{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} \textsc{WL-OA}~\cite{Kri+2016} included in the \textsc{\texttt{Anon}} package.
 The $C$-parameter was selected from $\{10^{-3}, 10^{-2}, \dotsc, 10^{2},$ $10^{3}\}$ from the validation set.
@@
 \xhdr{GNNs.} 
-For comparision with kernel methods, we used \textsc{Gin-$\varepsilon$}~\cite{Xu+2018b} and \textsc{Gin-$\varepsilon$-JK} with jumping knowledge networks as a neural baselines~\cite{Xu+2018}.
+For comparison with kernel methods, we used \textsc{Gin-$\varepsilon$}~\cite{Xu+2018b} and \textsc{Gin-$\varepsilon$-JK} with jumping knowledge networks as neural baselines~\cite{Xu+2018}.
 For data with (continuous) edge features, we used a $2$-layer MLP to map them to the same number of components as the node features and combined them using summation (\textsc{Gine-$\varepsilon$} and \textsc{Gine-$\varepsilon$}-JK).
@@
 \{ 32, 64, 128\}$, the number of layers from $ \{1, 2, 3, 4, 5\}$ using the validation set.
-Moreover, we use learning rate decay of $0.5$ with a patience parameter of $5$ with starting learning rate of $0.01$ and a minimum of $10^{-6}$.
-For both methods, we used the evaluation procedute described in~\cref{eval} to optimize hyperparameters and compute accuracies.
-See the appendix for details on the hyperparameter and evaluation protocols used for the larger molecular regression tasks, \textsc{Zinc} and \textsc{Alchemy}.
+Moreover, we use a learning rate decay of $0.5$ with a patience parameter of $5$ with a starting learning rate of $0.01$ and a minimum of $10^{-6}$.
+For both methods, we used the evaluation procedure described in~\cref{eval} to optimize hyperparameters and compute accuracies.
+See the appendix for details on the hyperparameter and evaluation protocols used for the larger molecular regression tasks, \textsc{Zinc}, \textsc{Alchemy},  \textsc{QM9}.
 
-All results can be reproduced using the scripts provided at \url{www.github.com/XXX/XXX}.
+All results can be are reproducable using the scripts provided at \url{www.github.com/Anon}.
 
@@
 
-We gave an overview of the \textsc{TuDataset}, and reported on the results of an experimental study comparing graph kernels and GNNs on a subset of the data.
-We believe that our dataset collection will spark further progress in the area of graph represention learning, are looking forward to adding more dataset, and are excited about contributions from the community, and reseachers and practitionors from other areas.
+We gave an overview of the \textsc{\texttt{Anon}}, and reported on the results of an experimental study comparing graph kernels and GNNs on a subset of the data.
+We believe that our dataset collection will spark further progress in graph representation learning.
+We are looking forward to adding more datasets and are excited about contributions from the community, researchers, and practitioners from other areas.
 
@@
 
-We thank everybody who provided datasets to the  \textsc{TuDataset} dataset collection.
+We thank everybody who provided datasets to the  \textsc{\texttt{Anon}} dataset collection.
 

### 2020-06-07 main.tex
MC.

@@
 
-The papers~\cite{Fey+2019,Che+2019,Err+2019,Dwi+2020} evaluate GNNs using a unified evaluation procedure, however, they only use small- or medium scale datasets.
+The papers~\cite{Fey+2019,Che+2019aa,Err+2019,Dwi+2020} evaluate GNNs using a unified evaluation procedure, however, they only use small- or medium scale datasets.
 Recently, \url{ogb.stanford.edu}~\cite{Hu+2020} launched, however, the provided datasets for graph classification focus on chemistry and bioinformatic applications, and the number is quite limited at this point.

### 2020-06-08 main.tex
MC.
New exp. for Yeast (replaces TRIANGLES)

--- 2020-06-07 main.tex
@@
 
-\paragraph{Present work.} 
+\xhdr{Present work.} 
 Here, we give an overview of \textsc{\texttt{Anon}}.
@@
 
-The papers~\cite{Fey+2019,Che+2019,Err+2019,Dwi+2020} evaluate GNNs using a unified evaluation procedure, however, they only use small- or medium scale datasets.
+The papers~\cite{Fey+2019,Che+2019new,Err+2019,Dwi+2020} evaluate GNNs using a unified evaluation procedure, however, they only use small- or medium scale datasets.
 Recently, \url{ogb.stanford.edu}~\cite{Hu+2020} launched, however, the provided datasets for graph classification focus on chemistry and bioinformatic applications, and the number is quite limited at this point.
@@
 			\cmidrule{2-8}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \textsc{Gin-$\varepsilon$}   &   \scriptsize $\pm \pm $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
-			& \textsc{Gin-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \textsc{Gin-$\varepsilon$}   &  39.5 \scriptsize $\pm 1.4 \pm 7.6 $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
+			& \textsc{Gin-$\varepsilon$-JK} &  d   \scriptsize $\pm \pm $       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
 			\bottomrule

### 2020-06-08 tud_benchmark/main_gnn.py

@@ -8,17 +8,19 @@ def main():
     num_reps = 10
 
     # Smaller datasets.
-    dataset = [["IMDB-BINARY", False], ["IMDB-MULTI", False], ["NCI1", True], ["PROTEINS", True],
-               ["REDDIT-BINARY", False], ["ENZYMES", True]]
+    # dataset = [["IMDB-BINARY", False], ["IMDB-MULTI", False], ["NCI1", True], ["PROTEINS", True],
+    #            ["REDDIT-BINARY", False], ["ENZYMES", True]]
+
+    dataset = [["ENZYMES", True]]
 
     results = []
     for d, use_labels in dataset:
         dp.get_dataset(d)
 
-        acc, s_1, s_2 = gnn_evaluation(GIN, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200, batch_size=128,
-                                       start_lr=0.01, num_repetitions=num_reps, all_std=True)
-        print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
-        results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
+        # acc, s_1, s_2 = gnn_evaluation(GIN, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200, batch_size=128,
+        #                                start_lr=0.01, num_repetitions=num_reps, all_std=True)
+        # print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
+        # results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
         acc, s_1, s_2 = gnn_evaluation(GINWithJK, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200, batch_size=128,
                                        start_lr=0.01, num_repetitions=num_reps, all_std=True)

### 2020-06-08 tud_benchmark/main_gnn.py
New exp. for Yeast (replaces TRIANGLES)

@@ -27,6 +27,8 @@ def main():
         print(d + " " + "GINWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GINWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
+    exit()
+
     # Midscale datasets.
     dataset = [["Yeast", True], ["YeastH", True], ["UACC257", True], ["UACC257H", True], ["OVCAR-8", True],
                ["OVCAR-8H", True]]
@@ -47,7 +49,6 @@ def main():
         results.append(d + " " + "GINE0 " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
 
-w
 
 if __name__ == "__main__":
     main()

### 2020-06-08 tud_benchmark/main_gnn.py
New exp. for Yeast (replaces TRIANGLES)

@@ -22,7 +22,7 @@ def main():
         # print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
         # results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
-        acc, s_1, s_2 = gnn_evaluation(GINWithJK, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200, batch_size=128,
+        acc, s_1, s_2 = gnn_evaluation_old(GINWithJK, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200, batch_size=128,
                                        start_lr=0.01, num_repetitions=num_reps, all_std=True)
         print(d + " " + "GINWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GINWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))

### 2020-06-08 main.tex
CM

@@
 Here, we give an overview of the datasets, standardized evaluation procedures, and provide baseline experiments.
-All datasets are available at \url{Anon}.
+All datasets are available at \url{www.anon.io}.
 The experiments are fully reproducible from the code available at \url{www.github.com/Anon}.
@@
 The benchmark collection consists of over 120 datasets from a wide range of domains for supervised learning with graphs, i.e., classification and regression.
-All datasets are provided in a standard dataset format at \url{Anon} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019} and \textsc{DGL}~\cite{Wan+2019}.
+All datasets are provided in a standard dataset format at \url{www.Anon.io} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019} and \textsc{DGL}~\cite{Wan+2019}.
 To facilitate standard comparison of kernel and neural approaches, we provide implementations of standard algorithms and easy-to-use evaluation procedures.
@@
 Moreover, the datasets proposed in~\cite{Fer+2019} focuses on instances from planning competitions.
-http://www.jmlr.org/papers/volume21/18-370/18-370.pdf
+Moreover, the \textsc{GraKeL} library~\cite{Sig+2018} provides an implemention of common graph kernels.
 
@@
 
-The \texttt{Anon} contains over 120 datasets provided at \texttt{Anon}.
+The \texttt{Anon} contains over 120 datasets provided at \texttt{www.anon.io}.
 The data baseline methods and experimental evaluation tools can be installed by running \texttt{pip install Anon}.

### 2020-06-08 main.tex
CM

@@
 See the website for dataset statistics.
+We
 
@@
 \subsection{Results and discussion}
-See~\cref{t2l,t2ll,neural_short_tt}.
+\cref{t2l,t2ll,neural_short_tt} summarize the results.
 On the small-scale datasets, see \cref{t2l}, the \textsc{WLOA} performs best overall, i.e., only on the \textsc{IMDB-Binary} and the \textsc{Reddit-Binary} dataset it is beaten by the $1$-\textsc{WL} or the neural baselines.
@@
 On the molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architecture such as \textsc{MPNN} result in signifcant gains over the generic \textsc{Gin-$\varepsilon$} baseline.
+For the neural baselines unlike the kernel baselines, we used one-hot degree features for datasets that do not provide node label.
 
@@
 We gave an overview of the \textsc{\texttt{Anon}}, and reported on the results of an experimental study comparing graph kernels and GNNs on a subset of the data.
-We believe that our dataset collection will spark further progress in graph representation learning.
+We believe that our dataset collection will spark further progress in graph representation learning, and that our unified evaluation procedures will lead to more comparable results.
 We are looking forward to adding more datasets and are excited about contributions from the community, researchers, and practitioners from other areas.

### 2020-06-08 main.tex
CM

@@
 See the website for dataset statistics.
-We
+We opted for not using the 3D-coordinates of the \textsc{Alchemy} dataset to solely provide baseline results based on graph structure.
 
@@
 \section{Experimental protocol and hyperparameters for \textsc{Zinc}, \textsc{Alchemy}, \textsc{QM9}}
-For the larger molecular regression tasks, \textsc{Zinc} and \textsc{Alchemy}, we closely followed the hyperparameters found in~\cite{Dwi+2020} and~\cite{Che+2020}, respectively, for the (\textsc{Gine-$\varepsilon$} layers.
+For the larger molecular regression tasks, \textsc{Zinc} and \textsc{Alchemy}\footnote{Note that the full dataset is different from the contest dataset, e.g., it does not provide normalized targets, see \url{https://alchemy.tencent.com/}.}, we closely followed the hyperparameters found in~\cite{Dwi+2020} and~\cite{Che+2020}, respectively, for the (\textsc{Gine-$\varepsilon$} layers.
 That is, for \textsc{Zinc}, we used four (\textsc{Gine-$\varepsilon$} layers with a hidden dimension of 256 followed by batch norm and a $4$-layer MLP for the joint regression of the twelve targets, after applying mean pooling.
@@
 Following~\cite{Kli+2020}, we report mean standardized MAE and mean standardized logMAE.
-We repeated each experiment five times (with different random splits in case of \textsc{Alchemy}) and report average scores and standard deviations.
-Moreover, we use learning rate decay of $0.5$ with a patience parameter of $5$ with starting learning rate of $0.001$ and a minimum of $10^{-6}$.
+We repeated each experiment five times (with different random splits in case of \textsc{Alchemy} and \textsc{QM9}) and report average scores and standard deviations.
+Moreover, we use a learning rate decay of $0.5$ with a patience parameter of $5$ with a starting learning rate of $0.001$ and a minimum of $10^{-6}$.
 

### 2020-06-08 main.tex
CM

@@
 \xhdr{Evaluation methods.}\label{eval} To ensure a fair and meaningful comparison between methods, we propose the following evaluation procedures for kernels and GNN approaches.
-All proposed methods and evaluation tools can be conveniently accessed from the Python interface, see the appendix for further details.
+All proposed methods and evaluation tools can be conveniently accessed from the Python interface, see~\cref{eval} for further details.
 First, for kernels we propose the established $C$-SVM implementation \textsc{LibSvm}~\cite{Cha+11} for kernels that compute a Gram matrix, and the linear $C$-SVM implementation \textsc{LibLinear}~\cite{Fan+2008} for kernels  that can be computed based on sparse, explicit feature maps.
@@
 To compute classification accuracies, we propose to use $10$-fold cross-validation, where we select a validation set uniformly at random from each training fold ($10\%$ of the training fold), to select hyperparameters, e.g., number of iterations, $C$ parameter, number of layers, feature dimension, \dots.
-Moreover, we repeat the above evaluation ten times and report standard deviations over all ten repetitions, and additionally across all one hundred runs (i.e., ten repetitions with ten folds each.).
+Moreover, we repeat the above evaluation ten times and report standard deviations over all ten repetitions, and additionally across all one hundred runs (i.e., ten repetitions with ten folds each).
 For the large-scale molecule learning tasks, we either use random splits (80\%/10\%/10\%) or provided, fixed splits and report MAE (mean std.
@@
 For data with (continuous) edge features, we used a $2$-layer MLP to map them to the same number of components as the node features and combined them using summation (\textsc{Gine-$\varepsilon$} and \textsc{Gine-$\varepsilon$}-JK).
-We used mean pooling to pool the learned node embeddings to a graph embedding and used $2$-layer MLP for the final classification, using a dropout layer with $p = 0.5$ after the first layer of the MLP.
+We used mean pooling to pool the learned node embeddings to a graph embedding and used a $2$-layer MLP for the final classification, using a dropout layer with $p = 0.5$ after the first layer of the MLP.
 We optimized the number of hidden units from $
@@
 On the small-scale datasets, see \cref{t2l}, the \textsc{WLOA} performs best overall, i.e., only on the \textsc{IMDB-Binary} and the \textsc{Reddit-Binary} dataset it is beaten by the $1$-\textsc{WL} or the neural baselines.
-However, it does not scale midscale datasets, \cref{t2l}, as it relies on Gram matrix computation.
-Here, the $1$-WL performs, excluding \textsc{github\_stargazers}, where the neural baseline perform best overall.
-On the molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architecture such as \textsc{MPNN} result in signifcant gains over the generic \textsc{Gin-$\varepsilon$} baseline.
-For the neural baselines unlike the kernel baselines, we used one-hot degree features for datasets that do not provide node label.
+However, it does not scale mid-scale datasets, \cref{t2l}, as it relies on Gram matrix computation.
+Here, the $1$-WL performs well on all datasets, excluding \textsc{github\_stargazers}, where the neural baseline perform best overall.\footnote{For the neural baselines unlike the kernel baselines, we used one-hot degree features for datasets that do not provide node labels.} On the molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architectures such as \textsc{MPNN} result in signifcant gains over the generic \textsc{Gin-$\varepsilon$} baseline.
 
@@
 
-\section{Experimental protocol and hyperparameters for \textsc{Zinc}, \textsc{Alchemy}, \textsc{QM9}}
+\section{Experimental protocol and hyperparameters for \textsc{Zinc}, \textsc{Alchemy}, \textsc{QM9}}\label{eval}
 For the larger molecular regression tasks, \textsc{Zinc} and \textsc{Alchemy}\footnote{Note that the full dataset is different from the contest dataset, e.g., it does not provide normalized targets, see \url{https://alchemy.tencent.com/}.}, we closely followed the hyperparameters found in~\cite{Dwi+2020} and~\cite{Che+2020}, respectively, for the (\textsc{Gine-$\varepsilon$} layers.

### 2020-06-08 main.tex
Small adjustments here and there, 4 pages.

@@
 We also provide several synthetic graph datasets to demonstrate the strengths or weaknesses of specific methods.
-The datasets \textsc{SyntheticNew} and \textsc{SyntheticNew} were created by \citet{Fer+2013} (see Erratum) and \citet{Mor+2016}, respectively, to demonstrate the ability of kernels to operate on graphs with continuous attributes.
+The datasets \textsc{Synthetic} and \textsc{SyntheticNew} were created by \citet{Fer+2013} (see Erratum) and \citet{Mor+2016}, respectively, to demonstrate the ability of kernels to operate on graphs with continuous attributes.
 \citet{Knyazev2019} introduced the datasets \textsc{Colors} and \textsc{Triangles}, where the task is to count the number of nodes with a given one-hot-encoded color and the number of triangles, respectively.
@@
 We repeated each experiment five times (with different random splits in case of \textsc{Alchemy} and \textsc{QM9}) and report average scores and standard deviations.
-Moreover, we use a learning rate decay of $0.5$ with a patience parameter of $5$ with a starting learning rate of $0.001$ and a minimum of $10^{-6}$.
+Moreover, we use a learning rate decay of $0.5$ with a patience parameter of $5$, and a starting learning rate of $0.001$ with a minimum of $10^{-6}$.
 

### 2020-06-08 main.tex
many minor changes and additions

@@
 That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area.
-To address this, we introduce the \textsc{\texttt{Anon}} for graph classification and regression.
-The dataset consists of over 120 datasets from a wide range of applications and varying sizes.
+To address this, we introduce the \textsc{\texttt{Anon}}Datasets for graph classification and regression.
+The collection consists of over 120 datasets of varying sizes from a wide range of applications, which have previously been used in the literature for evaluating graph learning approaches.
 We provide Python-based data loaders, kernel, and graph neural network baseline methods implementations, and evaluation tools.
@@
 To develop successful machine learning models in these domains, we need techniques that can exploit the rich information inherent in the graph structure, as well as the feature information contained within nodes and edges.
-In recent years, numerous approaches have been proposed for machine learning with graphs---most notably, approaches based on graph \new{kernels}~\cite{Kri+2019} or using \new{graph neural networks} (GNNs)~\cite{Gil+2017}.
+In recent years, numerous approaches have been proposed for machine learning with graphs---most notably, approaches based on \new{graph kernels}~\cite{Kri+2019} and \new{graph neural networks} (GNNs)~\cite{Gil+2017}.
 However, most papers, even recent ones, evaluate newly proposed architectures or methods on a fixed set of small-scale benchmark datasets leading to high standard deviations and hard to interpret results.
+Moreover, non-standardized experimental setups are used, which hinders the comparison of results from different publications.
 
@@
 Important approaches include random-walk and shortest paths based kernels~\cite{Gae+2003,Sugiyama2015,Bor+2005,Kri+2017b}, as well as the Weisfeiler-Lehman subtree kernel~\cite{She+2011,Mor+2017}.
-Further recent works focus on assignment-based approaches~\cite{Kri+2016,Nik+2017}, spectral approaches~\cite{Kon+2016}, and graph decomposition approaches~\cite{Nik+2018}, randomized binning approaches~\cite{Hei+2019}, and the extension of kernels based on the Weisfeiler-Leman algorithm~\cite{Tog+2019, Rie+2019}.
+Further recent works focus on approaches based on assignments~\cite{Kri+2016,Nik+2017}, spectral properties~\cite{Kon+2016}, graph decomposition~\cite{Nik+2018}, randomized binning~\cite{Hei+2019}, and the extension of kernels based on the Weisfeiler-Leman algorithm~\cite{Tog+2019, Rie+2019}.
 For a theoretical investigation of graph kernels, see~\cite{Kri+2018}.
@@
 Moreover, the datasets proposed in~\cite{Fer+2019} focuses on instances from planning competitions.
-Moreover, the \textsc{GraKeL} library~\cite{Sig+2018} provides an implemention of common graph kernels.
+Recent efforts to implement graph kernels in a common framework such as the \textsc{GraKeL} library~\cite{Sig+2018} foster comparability, but do not solve the dataset related issues discussed above.
 
@@
 
-The \texttt{Anon} contains over 120 datasets provided at \texttt{www.anon.io}.
-The data baseline methods and experimental evaluation tools can be installed by running \texttt{pip install Anon}.
-See the website for dataset statistics and documentation.
+The \texttt{Anon} collection contains over 120 datasets provided at \texttt{www.anon.io}.
+The datasets, baseline methods and experimental evaluation tools can be installed by running \texttt{pip install Anon} and are conveniently accessed from the Python interface, see~\cref{eval} for further details and example code.
+Dataset statistics and further documentation are provided on our website.
 
@@
 \xhdr{Small molecules.} 
-A common class of graph datasets consists of small molecules with class labels representing, e.g., toxicity or biological activity.
-Here, a graph encodes a molecule, i.e., nodes take the places of atoms and edges that of chemical bonds.
-Consequently, the labels encode atom and bond types, with possibly additional chemical attributes.
+A common class of graph datasets consists of small molecules with class labels representing, e.g., toxicity or biological activity determined in drug discovery projects.
+Here, a graph represents a molecule, i.e., nodes take the places of atoms and edges that of chemical bonds.
+Consequently, the labels encode atom and bond types, possibly with additional chemical attributes.
 The graph models differ, e.g., in whether hydrogen atoms are represented explicitly by nodes, and bonds in aromatic rings are annotated accordingly.
@@
 Moreover, our collection also contain large-scale molecular regression tasks such as \textsc{Alchemy}~\cite{Che+2020}, \textsc{Qm9}~\cite{Ram+2014}, and \textsc{Zinc}~\cite{Dwi+2020,Jin+2018a}.
-For the two formers, we also provide 3D coordinates, which are crucial to study rotation-invariant GNN architectures.
+The first two contain 3D coordinates of the nodes, which should be taken into account in a rotation-invariant manner to benefit from the geometrical information.
 
@@
 Using this approach, the dataset \textsc{Enzymes} was derived from the \textsc{Brenda} database~\cite{Schomburg2004}.
-Here, the task is to assign enzymes to one of the 6 EC top-level classes, which reflect the catalyze chemical reaction.
+Here, the task is to assign enzymes to one of the 6 EC top-level classes, which reflect the catalyzed chemical reaction.
 Similarly, the dataset \textsc{Proteins} was derived from \citep{Dob+2003}, and the task is to predict whether a protein is an enzyme.
-The dataset \textsc{DD} used by \citet{She+2011} is based on the same data but contains graphs, where nodes represent individual amino acids and edges their spatial proximity.
+The dataset \textsc{DD} used by \citet{She+2011} is based on the same data, but contains graphs, where nodes represent individual amino acids and edges their spatial proximity.
 
@@
 \textsc{Deezer\_Ego\_Nets} and \textsc{Twitch\_Egos} contain ego-networks derived from online services, and the task is to predict the gender and play behavior (single or multiple games) of the central user.
-\textsc{GitHub\_Stargazers} contains graphs representing the social networks of GitHub users divided into those who starred in popular machine learning and web development repositories.
+\textsc{GitHub\_Stargazers} contains graphs representing the social networks of GitHub users divided into those who starred popular machine learning and web development repositories.
 
@@
 \xhdr{Synthetic.}
-We also provide several synthetic graph datasets to demonstrate the strengths or weaknesses of specific methods.
-The datasets \textsc{Synthetic} and \textsc{SyntheticNew} were created by \citet{Fer+2013} (see Erratum) and \citet{Mor+2016}, respectively, to demonstrate the ability of kernels to operate on graphs with continuous attributes.
+Several graph datasets were generated to demonstrate the strengths or weaknesses of specific methods.
+The datasets \textsc{SyntheticNew} and \textsc{Synthie} were created by \citet{Fer+2013} (see Erratum) and \citet{Mor+2016}, respectively, to demonstrate the ability of kernels to operate on graphs with continuous attributes.
+% With the same goal, the dataset \textsc{Frankenstein} was obtained from a small molecule dataset by replacing the atom labels by MNIST digit images~\citep{Ors+2015}.
 \citet{Knyazev2019} introduced the datasets \textsc{Colors} and \textsc{Triangles}, where the task is to count the number of nodes with a given one-hot-encoded color and the number of triangles, respectively.
 
-\xhdr{Baselines methods.} To provide meaningful baselines, we provide implementations of common graph kernel as well as GNNs baselines.
-We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{\texttt{Anon}}.
+\subsection{Baselines methods} To provide meaningful baselines, we provide implementations of common graph kernel as well as GNN architectures.
+We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} (using labeled subgraphs with three nodes), \new{Weisfeiler-Lehman Optimal Assignment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{\texttt{Anon}}.
 Moreover, all GNN architectures provided by \textsc{PyTorch Geometric} can be conveniently used as a baseline as well.
-See~\cref{eval} for further details and example code.
 
-\xhdr{Evaluation methods.}\label{eval} To ensure a fair and meaningful comparison between methods, we propose the following evaluation procedures for kernels and GNN approaches.
-All proposed methods and evaluation tools can be conveniently accessed from the Python interface, see~\cref{eval} for further details.
+\subsection{Evaluation methods}\label{eval} To ensure a fair and meaningful comparison between methods, we propose the following evaluation procedures for kernels and GNNs.
 First, for kernels we propose the established $C$-SVM implementation \textsc{LibSvm}~\cite{Cha+11} for kernels that compute a Gram matrix, and the linear $C$-SVM implementation \textsc{LibLinear}~\cite{Fan+2008} for kernels  that can be computed based on sparse, explicit feature maps.
 We optimize GNNs end-to-end using \textsc{Adam}~\cite{Kin+2015}.
-To compute classification accuracies, we propose to use $10$-fold cross-validation, where we select a validation set uniformly at random from each training fold ($10\%$ of the training fold), to select hyperparameters, e.g., number of iterations, $C$ parameter, number of layers, feature dimension, \dots.
-Moreover, we repeat the above evaluation ten times and report standard deviations over all ten repetitions, and additionally across all one hundred runs (i.e., ten repetitions with ten folds each).
+To compute classification accuracies, we propose to use $10$-fold cross-validation, where we select $10\%$ of each training fold uniformly at random as validation set to optimize hyperparameters, e.g., the number of iterations, $C$ parameter, number of layers, feature dimension.
+We repeat the above evaluation ten times and report standard deviations over all ten repetitions, and additionally across all one hundred runs (i.e., ten repetitions with ten folds each).
 For the large-scale molecule learning tasks, we either use random splits (80\%/10\%/10\%) or provided, fixed splits and report MAE (mean std.
@@
 
-\xhdr{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} \textsc{WL-OA}~\cite{Kri+2016} included in the \textsc{\texttt{Anon}} package.
+\xhdr{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree} (\textsc{$1$-WL})~\cite{She+2011}, \new{Shortest-path} (\textsc{SP})~\cite{Bor+2005}, \new{Graphlet} (\textsc{GR})~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} (\textsc{WL-OA})~\cite{Kri+2016} included in the \textsc{\texttt{Anon}} package.
 The $C$-parameter was selected from $\{10^{-3}, 10^{-2}, \dotsc, 10^{2},$ $10^{3}\}$ from the validation set.
-For the larger datasets, we computed sparse feature vectors for each graph and used the linear $C$-SVM implementation of \text{Liblinear}~\cite{Fan+2008}.
+For the larger datasets, we computed sparse feature vectors for each graph and used the linear $C$-SVM implementation of \textsc{LibLinear}~\cite{Fan+2008}.
 The number of iterations of the \textsc{$1$-WL} and \textsc{WL-OA} were selected from $\{0,\dotsc,5\}$.\footnote{As already shown in~\cite{She+2011}, choosing the number of iterations too large will lead to overfitting.}
@@
 \{ 32, 64, 128\}$, the number of layers from $ \{1, 2, 3, 4, 5\}$ using the validation set.
-Moreover, we use a learning rate decay of $0.5$ with a patience parameter of $5$ with a starting learning rate of $0.01$ and a minimum of $10^{-6}$.
+Moreover, we use a learning rate decay of $0.5$ with a patience parameter of $5$, a starting learning rate of $0.01$ and a minimum of $10^{-6}$.
 For both methods, we used the evaluation procedure described in~\cref{eval} to optimize hyperparameters and compute accuracies.
@@
 
-All results can be are reproducable using the scripts provided at \url{www.github.com/Anon}.
+All results are reproducible using the scripts provided at \url{www.github.com/Anon}.
 
@@
 On the small-scale datasets, see \cref{t2l}, the \textsc{WLOA} performs best overall, i.e., only on the \textsc{IMDB-Binary} and the \textsc{Reddit-Binary} dataset it is beaten by the $1$-\textsc{WL} or the neural baselines.
-However, it does not scale mid-scale datasets, \cref{t2l}, as it relies on Gram matrix computation.
-Here, the $1$-WL performs well on all datasets, excluding \textsc{github\_stargazers}, where the neural baseline perform best overall.\footnote{For the neural baselines unlike the kernel baselines, we used one-hot degree features for datasets that do not provide node labels.} On the molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architectures such as \textsc{MPNN} result in signifcant gains over the generic \textsc{Gin-$\varepsilon$} baseline.
+However, it does not scale to large datasets, \cref{t2l}, as it relies on Gram matrix computation.
+Here, the $1$-WL performs well on all datasets, excluding \textsc{github\_stargazers}, where the neural baseline perform best overall.\footnote{For the neural baselines unlike the kernel baselines, we used one-hot degree features for datasets that do not provide node labels.}
+Our results show that despite the extensive research on GNNs in recent years, classical graph kernels in combination with SVMs are still highly competitive in graph classification tasks.
+
+On the large-scale molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architectures such as \textsc{MPNN} result in significant gains over the generic \textsc{Gin-$\varepsilon$} baseline.
+\nk{Koennte man das auch mit Kernel testen?
+Vielleicht noch ein Satz dazu?}
 
@@
 We gave an overview of the \textsc{\texttt{Anon}}, and reported on the results of an experimental study comparing graph kernels and GNNs on a subset of the data.
-We believe that our dataset collection will spark further progress in graph representation learning, and that our unified evaluation procedures will lead to more comparable results.
+We believe that our dataset collection will spark further progress in graph representation learning, and that our unified evaluation procedures will improve the comparability of results.
 We are looking forward to adding more datasets and are excited about contributions from the community, researchers, and practitioners from other areas.
@@
 
-\xhdr{Kernel with kernelized SVM}
+\xhdr{Kernelized SVM for graph kernels based on Gram matrices}
 \lstinputlisting[language=Python]{example.py}
 
-\xhdr{Sparse feature maps with linear SVM}
+\xhdr{Linear SVM for graph kernels based on sparse feature maps}
 \lstinputlisting[language=Python]{example_sparse.py}

### 2020-06-08 main.tex
MC.

@@
 \newcommand{\theHalgorithm}{\arabic{algorithm}}
+
+\usepackage[protrusion=true,expansion=false, activate={true,nocompatibility},final,kerning=true,spacing=true,shrink=60,stretch=10]{microtype}
 
@@
 \usepackage{setspace}
-\usepackage[protrusion=true,expansion=false, activate={true,nocompatibility},final,kerning=true,spacing=true]{microtype}
+\usepackage[protrusion=true,expansion=false,final,kerning=true,spacing=true]{microtype}
 
@@
 			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \textsc{Gin-$\varepsilon$}   &  39.5 \scriptsize $\pm 1.4 \pm 7.6 $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
-			& \textsc{Gin-$\varepsilon$-JK} &  d   \scriptsize $\pm \pm $       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
+			& \textsc{Gin-$\varepsilon$-JK} &  41.3 \scriptsize $\pm 1.8 \pm 6.7$       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
 			\bottomrule
@@
 \xhdr{Datasets.} We used the \textsc{deezer\_ego\_nets}, \textsc{github\_stargazers}, \textsc{Enymes}, \textsc{Imdb-Binary}, \textsc{Imdb-Multi}, \textsc{Mcf-7}, \textsc{Molt-4},    \textsc{NCI1}, \textsc{Proteins},
-\textsc{Reddit-Binary},    \textsc{reddit\_threads}, \textsc{twitch\_egos}, \textsc{Uacc257} graph classification datasets, and the \textsc{Alchemy}, \textsc{QM9}, \textsc{Zinc} (multi-target) regression datasets.
+\textsc{Reddit-Binary}, \textsc{reddit\_threads}, \textsc{twitch\_egos}, \textsc{Uacc257} graph classification datasets.
+Moreover, we used the \textsc{Alchemy}, \textsc{QM9}, \textsc{Zinc} (multi-target) regression datasets.
 See the website for dataset statistics.
-We opted for not using the 3D-coordinates of the \textsc{Alchemy} dataset to solely provide baseline results based on graph structure.
+We opted for not using continuous node features of the small datasets (if available) and the 3D-coordinates of the \textsc{Alchemy} dataset to solely provide baseline results based on graph structure.
+In case of the \textsc{QM9} dataset, we closely replicated the (continuous) node and edge features of~\citet{Gil+2017}.
 
@@
 On the large-scale molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architectures such as \textsc{MPNN} result in significant gains over the generic \textsc{Gin-$\varepsilon$} baseline.
-\nk{Koennte man das auch mit Kernel testen?
-Vielleicht noch ein Satz dazu?}
 
@@
 We are looking forward to adding more datasets and are excited about contributions from the community, researchers, and practitioners from other areas.
+Future work includes a more extensive comparision of kernel and neural approaches on large-scale molecular regression tasks with continuous node and edge features.
 

### 2020-06-08 main.tex
MC.

@@
 Moreover, the datasets proposed in~\cite{Fer+2019} focuses on instances from planning competitions.
-Recent efforts to implement graph kernels in a common framework such as the \textsc{GraKeL} library~\cite{Sig+2018} foster comparability, but do not solve the dataset related issues discussed above.
+Recent efforts to implement graph kernels in a common framework such as the \textsc{GraKeL} library~\cite{Sig+2018} foster comparability, but do not solve the dataset related issues discussed above, and only focus on kernel approaches.
 
@@
 	\label{t2l}	
-	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
+	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.0}
 		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule
@@
 			%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-			& \text{WLOA} & $58.4$ \scriptsize $\pm 2.0 \pm 7.4$   &  $73.2$ \scriptsize $\pm 0.8 \pm 3.8$ & $49.4$ \scriptsize $\pm 0.3 \pm 3.6 $ & $85.4$ \scriptsize $\pm  0.2 \pm 1.4$ & $73.2$ \scriptsize $\pm 0.6 \pm 3.5$ & $88.4$ \scriptsize $\pm 0.4 \pm 2.1 $   \\
+			& \text{WL-OA} & $58.4$ \scriptsize $\pm 2.0 \pm 7.4$   &  $73.2$ \scriptsize $\pm 0.8 \pm 3.8$ & $49.4$ \scriptsize $\pm 0.3 \pm 3.6 $ & $85.4$ \scriptsize $\pm  0.2 \pm 1.4$ & $73.2$ \scriptsize $\pm 0.6 \pm 3.5$ & $88.4$ \scriptsize $\pm 0.4 \pm 2.1 $   \\
 			& \text{GR}            &    $30.1$ \scriptsize $\pm 0.8 \pm 6.0$       & $59.0$ \scriptsize $\pm 0.9 \pm 5.7$ & $39.6$ \scriptsize $\pm 0.5 \pm 3.6  $ & $66.2$ \scriptsize $\pm 0.2\pm 2.2$ & $71.4$ \scriptsize $\pm 0.6\pm 4.4 $ & $60.0$ \scriptsize $\pm 0.2 \pm  2.7$   \\
@@
 	\label{t2ll}	
-	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
+	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.0}
 		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
@@
 The datasets \textsc{SyntheticNew} and \textsc{Synthie} were created by \citet{Fer+2013} (see Erratum) and \citet{Mor+2016}, respectively, to demonstrate the ability of kernels to operate on graphs with continuous attributes.
-% With the same goal, the dataset \textsc{Frankenstein} was obtained from a small molecule dataset by replacing the atom labels by MNIST digit images~\citep{Ors+2015}.
 \citet{Knyazev2019} introduced the datasets \textsc{Colors} and \textsc{Triangles}, where the task is to count the number of nodes with a given one-hot-encoded color and the number of triangles, respectively.
@@
 
-\subsection{Evaluation methods}\label{eval} To ensure a fair and meaningful comparison between methods, we propose the following evaluation procedures for kernels and GNNs.
+\subsection{Evaluation methods}\label{evalm} To ensure a fair and meaningful comparison between methods, we propose the following evaluation procedures for kernels and GNNs.
 First, for kernels we propose the established $C$-SVM implementation \textsc{LibSvm}~\cite{Cha+11} for kernels that compute a Gram matrix, and the linear $C$-SVM implementation \textsc{LibLinear}~\cite{Fan+2008} for kernels  that can be computed based on sparse, explicit feature maps.
@@
 Moreover, we use a learning rate decay of $0.5$ with a patience parameter of $5$, a starting learning rate of $0.01$ and a minimum of $10^{-6}$.
-For both methods, we used the evaluation procedure described in~\cref{eval} to optimize hyperparameters and compute accuracies.
-See the appendix for details on the hyperparameter and evaluation protocols used for the larger molecular regression tasks, \textsc{Zinc}, \textsc{Alchemy},  \textsc{QM9}.
+For both methods, we used the evaluation procedure described in~\cref{evalm} to optimize hyperparameters and compute accuracies.
+See the appendix for details on the hyperparameter and evaluation protocols used for the larger molecular regression tasks (\textsc{Zinc}, and \textsc{Alchemy},  \textsc{QM9}).
 

### 2020-06-08 main.tex
abstract
minor

@@
 That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area.
-To address this, we introduce the \textsc{\texttt{Anon}}Datasets for graph classification and regression.
+To address this, we introduce the \textsc{\texttt{Anon}}Dataset for graph classification and regression.
 The collection consists of over 120 datasets of varying sizes from a wide range of applications, which have previously been used in the literature for evaluating graph learning approaches.
@@
 
-\subsection{Baselines methods} To provide meaningful baselines, we provide implementations of common graph kernel as well as GNN architectures.
+\subsection{Baselines methods} To provide meaningful baselines, we provide implementations of common graph kernels as well as GNN architectures.
 We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} (using labeled subgraphs with three nodes), \new{Weisfeiler-Lehman Optimal Assignment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{\texttt{Anon}}.

### 2020-06-08 main.tex
minor

@@
 These datasets, the largest of which contain more than 79k graphs, are typically not balanced and contain far more small molecules that are identified as inactive against cancer cells.
-Moreover, our collection also contain large-scale molecular regression tasks such as \textsc{Alchemy}~\cite{Che+2020}, \textsc{Qm9}~\cite{Ram+2014}, and \textsc{Zinc}~\cite{Dwi+2020,Jin+2018a}.
+Moreover, our collection also contains large-scale molecular regression tasks such as \textsc{Alchemy}~\cite{Che+2020}, \textsc{Qm9}~\cite{Ram+2014}, and \textsc{Zinc}~\cite{Dwi+2020,Jin+2018a}.
 The first two contain 3D coordinates of the nodes, which should be taken into account in a rotation-invariant manner to benefit from the geometrical information.

### 2020-06-08 main.tex
MC.

@@
 
-\usepackage[protrusion=true,expansion=false, activate={true,nocompatibility},final,kerning=true,spacing=true,shrink=60,stretch=10]{microtype}
+\usepackage[protrusion=true,expansion=false, activate={true,nocompatibility},final,kerning=true,spacing=true,shrink=50,stretch=]{microtype}
 
@@
 
-\subsection{Datasets}
-
-\begin{table*}[ht]\centering		
-	\caption{Classification accuracies in percent and standard deviations on small-scale datasets.}
-	\label{t2l}	
-	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.0}
-		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule
-
-			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
-			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule
-
-			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &   $52.3$ \scriptsize $\pm 0.7 \pm 6.7 $       & $72.6$ \scriptsize $\pm  0.6 \pm 4.1$ &  $50.3$ \scriptsize $\pm 0.8 \pm  3.8 $ & $84.5$ \scriptsize $\pm 0.3 \pm 1.7$ & $72.8$ \scriptsize $\pm 0.8 \pm  3.9 $ & $73.9$ \scriptsize $\pm 0.6 \pm 3.2$  \\
-			%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-			%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-			& \text{WL-OA} & $58.4$ \scriptsize $\pm 2.0 \pm 7.4$   &  $73.2$ \scriptsize $\pm 0.8 \pm 3.8$ & $49.4$ \scriptsize $\pm 0.3 \pm 3.6 $ & $85.4$ \scriptsize $\pm  0.2 \pm 1.4$ & $73.2$ \scriptsize $\pm 0.6 \pm 3.5$ & $88.4$ \scriptsize $\pm 0.4 \pm 2.1 $   \\
-			& \text{GR}            &    $30.1$ \scriptsize $\pm 0.8 \pm 6.0$       & $59.0$ \scriptsize $\pm 0.9 \pm 5.7$ & $39.6$ \scriptsize $\pm 0.5 \pm 3.6  $ & $66.2$ \scriptsize $\pm 0.2\pm 2.2$ & $71.4$ \scriptsize $\pm 0.6\pm 4.4 $ & $60.0$ \scriptsize $\pm 0.2 \pm  2.7$   \\
-			& \text{SP}            & $40.5$  \scriptsize $\pm 1.6 \pm 6.2$       & $58.7$ \scriptsize $\pm 0.9 \pm 4.6 $ & $39.5$ \scriptsize $\pm 0.9 \pm 4.2$ & $74.5$ \scriptsize $\pm 0.4\pm 2.2 $  &$75.9$ \scriptsize $\pm 0.6 \pm 4.0$ & $84.6$ \scriptsize $\pm0.2\pm 0.4 $  \\
-			\cmidrule{2-8}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \textsc{Gin-$\varepsilon$}   &  39.5 \scriptsize $\pm 1.4 \pm 7.6 $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
-			& \textsc{Gin-$\varepsilon$-JK} &  41.3 \scriptsize $\pm 1.8 \pm 6.7$       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
-			\bottomrule
-	\end{tabular}}
-\end{table*}		
-\begin{table*}[t]\centering		
-	\caption{Classification accuracies in percent and standard deviations on mid-scale datasets.}
-	\label{t2ll}	
-	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.0}
-		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
-			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
-			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Yeast}}           & {\textsc{github\_star.}}       & {\textsc{reddit\_threads}}      \\	\toprule
-			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
-			$94.5$ \scriptsize $<0.1 \pm 0.4$  &$94.6$ \scriptsize $\pm 0.1  \pm 0.3$ & $89.2$ \scriptsize $\pm 0.1 \pm 0.4$ &  $63.9$ \scriptsize $\pm 0.1\pm 1.3$ &$77.0$ \scriptsize $<0.1 \pm 0.3$  \\
-
-			& \text{GR}            & $91.7$  \scriptsize $<0.1  \pm 0.5 $       & $92.1$ \scriptsize $<0.1 \pm 0.4$ & $88.2$ \scriptsize $<0.1  \pm 0.4$ &  $53.5$ \scriptsize $<0.1 \pm 1.3$ & $51.2$ \scriptsize $<0.1 \pm 0.4$  \\
-			& \text{SP}             &  $91.7$  \scriptsize $<0.1 \pm 0.4 $       &$92.1$  \scriptsize $<0.1 \pm 0.4 $ & $88.2$ \scriptsize $<0.1  \pm 0.4$ & $64.1$ \scriptsize $\pm 0.1\pm 1.4$ & $77.3$ \scriptsize $<0.1 \pm 0.3$  \\
-			\cmidrule{2-7}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \textsc{Gine-$\varepsilon$}         &  $92.0$ \scriptsize $\pm  0.1 \pm 0.6$       & $92.3$ \scriptsize $\pm 0.1 \pm 0.6$ & 88.3 \scriptsize $<0.1 \pm 0.3$ &  $67.1$ \scriptsize $\pm 0.5 \pm 1.6  $ & $77.2$ \scriptsize $<0.1  \pm 0.3$ \\
-			& \textsc{Gine-$\varepsilon$-JK}   &   $91.8$ \scriptsize $<0.1 \pm 0.5$       & $92.2$ \scriptsize $<0.1 \pm 0.5$ & 88.2  \scriptsize $<0.1 \pm 0.3$ & $67.2$ \scriptsize $\pm 0.4 \pm 1.3$ &  $77.3$  \scriptsize $<0.1 \pm 0.3 $  \\
-			\bottomrule
-	\end{tabular}}
-\end{table*}
-
 Our collection of datasets covers graphs from various domains, contributed by different authors.
@@
 This includes the eleven datasets from anticancer screen tests with different cancer cell lines used by~\citet{Yan2008} to demonstrate the efficacy of classifiers based on significant graph patterns.
-These datasets, the largest of which contain more than 79k graphs, are typically not balanced and contain far more small molecules that are identified as inactive against cancer cells.
+These datasets, the largest of which contains more than 79k graphs, are typically not balanced and contain far more small molecules that are identified as inactive against cancer cells.
 Moreover, our collection also contains large-scale molecular regression tasks such as \textsc{Alchemy}~\cite{Che+2020}, \textsc{Qm9}~\cite{Ram+2014}, and \textsc{Zinc}~\cite{Dwi+2020,Jin+2018a}.
@@
 
-\begin{table}[]\centering	
-	\caption{Mean MAE (mean std. MAE, logMAE) on large-scale (multi-target) molecular regression tasks.\label{neural_short_tt}}
-	\resizebox{1.0\columnwidth}{!}{\renewcommand{\arraystretch}{1.2}
-		\begin{tabular}{lccc}	\toprule
-			\multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{2}{c}{\textbf{Dataset}}\\\cmidrule{2-4}
-			& {\textsc{Zinc}}     & {\textsc{alchemy}}   & {\textsc{Qm9}}   \\	\toprule
-			\textsc{Gine-$\varepsilon$}    & 0.084                                                                                                                                                                                                                                     \scriptsize $\pm 0.004$   &                                                                                                                                                                                                                                0.103 {\scriptsize $\pm 0.001$} -2.956 {\scriptsize $\pm 0.029$} &  0.081 {\scriptsize $\pm 0.003$} -3.400 {\scriptsize $\pm  0.094 $}   \\
-			\textsc{MPNN}    & ---                                                                                                                                                                                                                                    & --- & 0.034 {\scriptsize $\pm 0.001$} {-4.156}{\scriptsize $\pm 0.030$}  \\
+%\subsection{Datasets}
+
+\begin{table*}[ht]\centering		
+	\caption{Classification accuracies in percent and standard deviations on small-scale datasets.}
+	\label{t2l}	
+	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
+		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule
+
+			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
+			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule
+
+			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &   $52.3$ \scriptsize $\pm 0.7 \pm 6.7 $       & $72.6$ \scriptsize $\pm  0.6 \pm 4.1$ &  $50.3$ \scriptsize $\pm 0.8 \pm  3.8 $ & $84.5$ \scriptsize $\pm 0.3 \pm 1.7$ & $72.8$ \scriptsize $\pm 0.8 \pm  3.9 $ & $73.9$ \scriptsize $\pm 0.6 \pm 3.2$  \\
+			%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+			%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
+			& \text{WL-OA} & $58.4$ \scriptsize $\pm 2.0 \pm 7.4$   &  $73.2$ \scriptsize $\pm 0.8 \pm 3.8$ & $49.4$ \scriptsize $\pm 0.3 \pm 3.6 $ & $85.4$ \scriptsize $\pm  0.2 \pm 1.4$ & $73.2$ \scriptsize $\pm 0.6 \pm 3.5$ & $88.4$ \scriptsize $\pm 0.4 \pm 2.1 $   \\
+			& \text{GR}            &    $30.1$ \scriptsize $\pm 0.8 \pm 6.0$       & $59.0$ \scriptsize $\pm 0.9 \pm 5.7$ & $39.6$ \scriptsize $\pm 0.5 \pm 3.6  $ & $66.2$ \scriptsize $\pm 0.2\pm 2.2$ & $71.4$ \scriptsize $\pm 0.6\pm 4.4 $ & $60.0$ \scriptsize $\pm 0.2 \pm  2.7$   \\
+			& \text{SP}            & $40.5$  \scriptsize $\pm 1.6 \pm 6.2$       & $58.7$ \scriptsize $\pm 0.9 \pm 4.6 $ & $39.5$ \scriptsize $\pm 0.9 \pm 4.2$ & $74.5$ \scriptsize $\pm 0.4\pm 2.2 $  &$75.9$ \scriptsize $\pm 0.6 \pm 4.0$ & $84.6$ \scriptsize $\pm0.2\pm 0.4 $  \\
+			\cmidrule{2-8}	
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \textsc{Gin-$\varepsilon$}   &  39.5 \scriptsize $\pm 1.4 \pm 7.6 $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
+			& \textsc{Gin-$\varepsilon$-JK} &  41.3 \scriptsize $\pm 1.8 \pm 6.7$       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
 			\bottomrule
 	\end{tabular}}
-\end{table}		
+\end{table*}		
+\begin{table*}[t]\centering		
+	\caption{Classification accuracies in percent and standard deviations on mid-scale datasets.}
+	\label{t2ll}	
+	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
+		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
+			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
+			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Yeast}}           & {\textsc{github\_star.}}       & {\textsc{reddit\_threads}}      \\	\toprule
+			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
+			$94.5$ \scriptsize $<0.1 \pm 0.4$  &$94.6$ \scriptsize $\pm 0.1  \pm 0.3$ & $89.2$ \scriptsize $\pm 0.1 \pm 0.4$ &  $63.9$ \scriptsize $\pm 0.1\pm 1.3$ &$77.0$ \scriptsize $<0.1 \pm 0.3$  \\
+
+			& \text{GR}            & $91.7$  \scriptsize $<0.1  \pm 0.5 $       & $92.1$ \scriptsize $<0.1 \pm 0.4$ & $88.2$ \scriptsize $<0.1  \pm 0.4$ &  $53.5$ \scriptsize $<0.1 \pm 1.3$ & $51.2$ \scriptsize $<0.1 \pm 0.4$  \\
+			& \text{SP}             &  $91.7$  \scriptsize $<0.1 \pm 0.4 $       &$92.1$  \scriptsize $<0.1 \pm 0.4 $ & $88.2$ \scriptsize $<0.1  \pm 0.4$ & $64.1$ \scriptsize $\pm 0.1\pm 1.4$ & $77.3$ \scriptsize $<0.1 \pm 0.3$  \\
+			\cmidrule{2-7}	
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \textsc{Gine-$\varepsilon$}         &  $92.0$ \scriptsize $\pm  0.1 \pm 0.6$       & $92.3$ \scriptsize $\pm 0.1 \pm 0.6$ & 88.3 \scriptsize $<0.1 \pm 0.3$ &  $67.1$ \scriptsize $\pm 0.5 \pm 1.6  $ & $77.2$ \scriptsize $<0.1  \pm 0.3$ \\
+			& \textsc{Gine-$\varepsilon$-JK}   &   $91.8$ \scriptsize $<0.1 \pm 0.5$       & $92.2$ \scriptsize $<0.1 \pm 0.5$ & 88.2  \scriptsize $<0.1 \pm 0.3$ & $67.2$ \scriptsize $\pm 0.4 \pm 1.3$ &  $77.3$  \scriptsize $<0.1 \pm 0.3 $  \\
+			\bottomrule
+	\end{tabular}}
+\end{table*}
+
 \section{Experimental evaluation}
@@
 
-\subsection{Results and discussion}
+\xhdr{Results and discussion}
 \cref{t2l,t2ll,neural_short_tt} summarize the results.
@@
 Our results show that despite the extensive research on GNNs in recent years, classical graph kernels in combination with SVMs are still highly competitive in graph classification tasks.
-
+\begin{table}[]\centering	
+	\caption{Mean MAE (mean std. MAE, logMAE) on large-scale (multi-target) molecular regression tasks.\label{neural_short_tt}}
+	\resizebox{1.0\columnwidth}{!}{\renewcommand{\arraystretch}{1.1}
+		\begin{tabular}{lccc}	\toprule
+			\multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{2}{c}{\textbf{Dataset}}\\\cmidrule{2-4}
+			& {\textsc{Zinc}}     & {\textsc{alchemy}}   & {\textsc{Qm9}}   \\	\toprule
+			\textsc{Gine-$\varepsilon$}    & 0.084                                                                                                                                                                                                                                     \scriptsize $\pm 0.004$   &                                                                                                                                                                                                                                0.103 {\scriptsize $\pm 0.001$} -2.956 {\scriptsize $\pm 0.029$} &  0.081 {\scriptsize $\pm 0.003$} -3.400 {\scriptsize $\pm  0.094 $}   \\
+			\textsc{MPNN}    & ---                                                                                                                                                                                                                                    & --- & 0.034 {\scriptsize $\pm 0.001$} {-4.156}{\scriptsize $\pm 0.030$}  \\
+			\bottomrule
+	\end{tabular}}
+\end{table}		
 On the large-scale molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architectures such as \textsc{MPNN} result in significant gains over the generic \textsc{Gin-$\varepsilon$} baseline.

### 2020-06-09 main.tex
MC.

@@
 
-\usepackage[protrusion=true,expansion=false, activate={true,nocompatibility},final,kerning=true,spacing=true,shrink=50,stretch=]{microtype}
+\usepackage[protrusion=true,expansion=false, activate={true,nocompatibility},final,kerning=true,spacing=true,shrink=30]{microtype}
 
@@
 \icmlauthor{N.\,M.\,Kriege}{vie}
-\icmlauthor{Franka Bause}{vie}
+\icmlauthor{F. Bause}{vie}
 \icmlauthor{K. Kersting}{darm}
-\icmlauthor{P. Mutzw}{bonn}
+\icmlauthor{P. Mutzel}{bonn}
 \icmlauthor{N. Neumann}{wustl}
@@
 To address this, we introduce the \textsc{\texttt{Anon}}Dataset for graph classification and regression.
-The collection consists of over 120 datasets of varying sizes from a wide range of applications, which have previously been used in the literature for evaluating graph learning approaches.
+The collection consists of over 120 datasets of varying sizes from a wide range of applications.
 We provide Python-based data loaders, kernel, and graph neural network baseline methods implementations, and evaluation tools.
@@
 	\label{t2l}	
-	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
+	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.2}
 		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule
@@
 	\label{t2ll}	
-	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
+	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.2}
 		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
@@
 \end{table}		
-On the large-scale molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architectures such as \textsc{MPNN} result in significant gains over the generic \textsc{Gin-$\varepsilon$} baseline.
+On the large-scale molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architectures such as \textsc{MPNN} result in significant gains over the generic \textsc{Gine-$\varepsilon$} baseline.
 
@@
 We thank everybody who provided datasets to the  \textsc{\texttt{Anon}} dataset collection.
-
+\newpage
 \bibliography{bibliography}
@@
 \section{Experimental protocol and hyperparameters for \textsc{Zinc}, \textsc{Alchemy}, \textsc{QM9}}\label{eval}
-For the larger molecular regression tasks, \textsc{Zinc} and \textsc{Alchemy}\footnote{Note that the full dataset is different from the contest dataset, e.g., it does not provide normalized targets, see \url{https://alchemy.tencent.com/}.}, we closely followed the hyperparameters found in~\cite{Dwi+2020} and~\cite{Che+2020}, respectively, for the (\textsc{Gine-$\varepsilon$} layers.
-That is, for \textsc{Zinc}, we used four (\textsc{Gine-$\varepsilon$} layers with a hidden dimension of 256 followed by batch norm and a $4$-layer MLP for the joint regression of the twelve targets, after applying mean pooling.
+For the larger molecular regression tasks, \textsc{Zinc} and \textsc{Alchemy}\footnote{Note that the full dataset is different from the contest dataset, e.g., it does not provide normalized targets, see \url{https://alchemy.tencent.com/}.}, we closely followed the hyperparameters found in~\cite{Dwi+2020} and~\cite{Che+2020}, respectively, for the \textsc{Gine-$\varepsilon$} layers.
+That is, for \textsc{Zinc}, we used four \textsc{Gine-$\varepsilon$} layers with a hidden dimension of 256 followed by batch norm and a $4$-layer MLP for the joint regression of the twelve targets, after applying mean pooling.
 For \textsc{Alchemy} and \textsc{QM9}, we used six layers with 64 (hidden) node features and a set2seq layer~\cite{Vin+2016} for graph-level pooling, followed by a $2$-layer MLP for the joint regression of the twelve targets.

### 2020-06-09 main.tex
MC.

@@
 		\begin{tabular}{lccc}	\toprule
-			\multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{2}{c}{\textbf{Dataset}}\\\cmidrule{2-4}
+			\multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{3}{c}{\textbf{Dataset}}\\\cmidrule{2-4}
 			& {\textsc{Zinc}}     & {\textsc{alchemy}}   & {\textsc{Qm9}}   \\	\toprule

### 2020-06-28 tud_benchmark/auxiliarymethods/reader.py
Cleanup.

@@ -1,0 +1,118 @@
+import networkx as nx
+import os.path as path
+
+def read_txt(ds_name):
+    pre = ""
+
+    with open("datasets/" + pre + ds_name + "/" + ds_name + "_graph_indicator.txt", "r") as f:
+        graph_indicator = [int(i) - 1 for i in list(f)]
+    f.closed
+
+    # Nodes
+    num_graphs = max(graph_indicator)
+    node_indices = []
+    offset = []
+    c = 0
+
+    for i in range(num_graphs + 1):
+        offset.append(c)
+        c_i = graph_indicator.count(i)
+        node_indices.append((c, c + c_i - 1))
+        c += c_i
+
+    graph_db = []
+    for i in node_indices:
+        g = nx.Graph()
+        for j in range(i[1] - i[0]):
+            g.add_node(j+1)
+
+        graph_db.append(g)
+
+    # Edges
+    with open("datasets/" + pre + ds_name + "/" + ds_name + "_A.txt", "r") as f:
+        edges = [i.split(',') for i in list(f)]
+    f.closed
+
+    edges = [(int(e[0].strip()) - 1, int(e[1].strip()) - 1) for e in edges]
+    edge_list = []
+    for e in edges:
+        g_id = graph_indicator[e[0]]
+        g = graph_db[g_id]
+        off = offset[g_id]
+
+        # Avoid multigraph (for edge_list)
+        if ((e[0] - off, e[1] - off) not in list(g.edges())) and ((e[1] - off, e[0] - off) not in list(g.edges())):
+            g.add_edge(e[0] - off, e[1] - off)
+            edge_list.append((e[0] - off, e[1] - off))
+
+    # Node labels
+    if path.exists("datasets/" + pre + ds_name + "/" + ds_name + "_node_labels.txt"):
+        with open("datasets/" + pre + ds_name + "/" + ds_name + "_node_labels.txt", "r") as f:
+            node_labels = [map(int, i.split(',')) for i in list(f)] #[int(i) for i in list(f)]
+        f.closed
+
+        i = 0
+        for g in graph_db:
+            for v in range(g.number_of_nodes()):
+                g.nodes[v]['labels']= node_labels[i]
+                i += 1
+
+
+    # Node Attributes
+    if path.exists("datasets/" + pre + ds_name + "/" + ds_name + "_node_attributes.txt"):
[…]

### 2020-06-28 tud_benchmark/large_scale_molecules/mpnn_qm9.py

@@ -78,13 +78,11 @@ for _ in range(5):
     dataset = dataset.shuffle()
 
     tenpercent = int(len(dataset) * 0.1)
-    print("###")
     mean = dataset.data.y.mean(dim=0, keepdim=True)
     std = dataset.data.y.std(dim=0, keepdim=True)
     dataset.data.y = (dataset.data.y - mean) / std
     mean, std = mean.to(device), std.to(device)
 
-    print("###")
     test_dataset = dataset[:tenpercent].shuffle()
     val_dataset = dataset[tenpercent:2 * tenpercent].shuffle()
     train_dataset = dataset[2 * tenpercent:].shuffle()

### 2020-06-29 paper/main.tex
Cleanup.

--- 2020-06-09 main.tex
@@
 
-\usepackage[protrusion=true,expansion=false, activate={true,nocompatibility},final,kerning=true,spacing=true,shrink=30]{microtype}
+\usepackage[protrusion=true,expansion=false, activate={true,nocompatibility},final,kerning=true,spacing=true,shrink=40]{microtype}
 
@@
 
-\newcommand{\nk}[1]{{{\textcolor{brown}{\textbf{[NK:} {#1}\textbf{]}}}}}
-\newcommand{\cm}[1]{{{\textcolor{red}{\textbf{[CM:} {#1}\textbf{]}}}}}
-
 \usepackage{ifthen}
@@
 
-%\renewcommand*{\familydefault}{ttdefault}
 \usepackage{listings}
@@
 }
-\usepackage{icml2020}
+\usepackage[accepted]{icml2020}
 
-\icmltitlerunning{Anon}
+\icmltitlerunning{TUDataset}
 
@@
 \twocolumn[
-\icmltitle{\texttt{Anon}Dataset: A collection of benchmark datasets for learning with graphs}
+\icmltitle{TUDataset: A collection of benchmark datasets for learning with graphs}
 \icmlsetsymbol{equal}{*}
@@
 \begin{icmlauthorlist}
-\icmlauthor{C. Morris}{p}
-\icmlauthor{N.\,M.\,Kriege}{vie}
-\icmlauthor{F. Bause}{vie}
-\icmlauthor{K. Kersting}{darm}
-\icmlauthor{P. Mutzel}{bonn}
-\icmlauthor{N. Neumann}{wustl}
+\icmlauthor{Christopher Morris}{p}
+\icmlauthor{Nils \,M.\,Kriege}{vie}
+\icmlauthor{Franka Bause}{vie}
+\icmlauthor{Kristian Kersting}{darm}
+\icmlauthor{Petra Mutzel}{bonn}
+\icmlauthor{Marion Neumann}{wustl}
 \end{icmlauthorlist}
@@
 \icmlaffiliation{p}{CERC in Data Science for Real-Time Decision-Making, Polytechnique Montréal}
-\icmlaffiliation{vie}{University of Vienna}
+\icmlaffiliation{vie}{Data Mining Group, Faculty of Computer Science, University of Vienna}
 \icmlaffiliation{darm}{Machine Learning Group, TU Darmstadt}
@@
 That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area.
-To address this, we introduce the \textsc{\texttt{Anon}}Dataset for graph classification and regression.
+To address this, we introduce the \textsc{TUDataset} for graph classification and regression.
 The collection consists of over 120 datasets of varying sizes from a wide range of applications.
@@
 Here, we give an overview of the datasets, standardized evaluation procedures, and provide baseline experiments.
-All datasets are available at \url{www.anon.io}.
-The experiments are fully reproducible from the code available at \url{www.github.com/Anon}.
+All datasets are available at \url{www.graphlearning.io}.
+The experiments are fully reproducible from the code available at \url{www.github.com/chrsmrrs/tudatasets}.
 \end{abstract}
@@
 The benchmark collection consists of over 120 datasets from a wide range of domains for supervised learning with graphs, i.e., classification and regression.
-All datasets are provided in a standard dataset format at \url{www.Anon.io} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019} and \textsc{DGL}~\cite{Wan+2019}.
+All datasets are provided in a standard dataset format at \url{www.graphlearning.io} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019}\footnote{\url{https://pytorch-geometric.readthedocs.io/en/latest/modules/datasets.html}} and \textsc{DGL}~\cite{Wan+2019}\footnote{\url{https://docs.dgl.ai/en/0.4.x/api/python/data.html}}.
 To facilitate standard comparison of kernel and neural approaches, we provide implementations of standard algorithms and easy-to-use evaluation procedures.
-Moreover, we report results on an experimental study comparing graph kernels and GNNs on a subset of the \textsc{\texttt{Anon}}.
+Moreover, we report results on an experimental study comparing graph kernels and GNNs on a subset of the \textsc{TUDataset}.
 
@@
 
-\section{The \texttt{Anon}Dataset collection}
+\section{The TUDataset collection}
 
-The \texttt{Anon} collection contains over 120 datasets provided at \texttt{www.anon.io}.
-The datasets, baseline methods and experimental evaluation tools can be installed by running \texttt{pip install Anon} and are conveniently accessed from the Python interface, see~\cref{eval} for further details and example code.
-Dataset statistics and further documentation are provided on our website.
+The \textsc{TUDataset} collection contains over 120 datasets provided at \texttt{www.graphlearning.io}.
+The datasets, baseline methods and experimental evaluation tools can be conveniently accessed from the Python interface, see \cref{evalcode} for further details.
+Moreover, see the website for dataset statistics, further documentation.
 
@@
 \subsection{Baselines methods} To provide meaningful baselines, we provide implementations of common graph kernels as well as GNN architectures.
-We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} (using labeled subgraphs with three nodes), \new{Weisfeiler-Lehman Optimal Assignment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{\texttt{Anon}}.
+We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} (using labeled subgraphs with three nodes), \new{Weisfeiler-Lehman Optimal Assignment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{TUDatasets}.
 Moreover, all GNN architectures provided by \textsc{PyTorch Geometric} can be conveniently used as a baseline as well.
@@
 	\label{t2l}	
-	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.2}
+	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.05}
 		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule
@@
 	\label{t2ll}	
-	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.2}
+	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.05}
 		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
@@
 
-All results are reproducible using the scripts provided at \url{www.github.com/Anon}.
+All results are reproducible using the scripts provided at \url{https://github.com/chrsmrrs/tudatasets}.
 
@@
 	\caption{Mean MAE (mean std. MAE, logMAE) on large-scale (multi-target) molecular regression tasks.\label{neural_short_tt}}
-	\resizebox{1.0\columnwidth}{!}{\renewcommand{\arraystretch}{1.2}
+	\resizebox{1.0\columnwidth}{!}{\renewcommand{\arraystretch}{1.05}
 		\begin{tabular}{lccc}	\toprule
@@
 
-We gave an overview of the \textsc{\texttt{Anon}}, and reported on the results of an experimental study comparing graph kernels and GNNs on a subset of the data.
+We gave an overview of the \textsc{TUDataset} collection, and reported on the results of an experimental study comparing graph kernels and GNNs on a subset of the data.
 We believe that our dataset collection will spark further progress in graph representation learning, and that our unified evaluation procedures will improve the comparability of results.
@@
 
-We thank everybody who provided datasets to the  \textsc{\texttt{Anon}} dataset collection.
-\newpage
+We thank evefrybody who provided datasets to the  \textsc{TUDataset} collection.
+%\newpage
 \bibliography{bibliography}
@@
 
-\section{Evaluation examples}
+\section{Evaluation examples}\label{evalcode}
 
@@
 \lstinputlisting[language=Python]{example_gnn.py}
+
+\xhdr{Loading graphs as NetworkX graphs}
+\lstinputlisting[language=Python]{networkx.py}
 

### 2020-06-29 paper/example.py

@@ -3,11 +3,12 @@ import auxiliarymethods.datasets as dp
 import kernel_baselines as kb
 from auxiliarymethods.kernel_evaluation import kernel_svm_evaluation
 
-# Download datasets.
+# Download dataset.
 classes = dp.get_dataset("ENZYMES")
 use_labels, use_edge_labels = True, False
 
 all_matrices = []
+# Compute 1-WL kernel for 1 to 5 iterations.
 for i in range(1, 6):
     # Use node labels and no edge labels.
     gm = kb.compute_wl_1_dense("ENZYMES", i, use_labels, use_edge_labels)

### 2020-06-29 paper/example_gnn.py

@@ -1,10 +1,19 @@
 import auxiliarymethods.datasets as dp
 from auxiliarymethods.gnn_evaluation import gnn_evaluation
 from gnn_baselines.gnn_architectures import GIN
+from auxiliarymethods.reader import tud_to_networkx
 
 dataset = "PROTEINS"
 use_labels = True
+
+# Download datasets.
 dp.get_dataset(dataset)
 
-print(gnn_evaluation(GIN, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200,
-                     batch_size=128, start_lr=0.01, num_repetitions=10, all_std=True))
+# Optimize the number of layers ({1,2,3,4,5}) and
+# the number of hidden features ({32,64,128}),
+# set the maximum nummber of epochs to 200,
+# batch size to 64,
+# start learning rate to 0.01, and
+# number of repetitions for 10-CV to 10.
+print(gnn_evaluation(GIN, dataset, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200,
+                     batch_size=64, start_lr=0.01, num_repetitions=10, all_std=True))

### 2020-06-29 paper/example_sparse.py

@@ -3,10 +3,12 @@ import auxiliarymethods.datasets as dp
 import kernel_baselines as kb
 from auxiliarymethods.kernel_evaluation import linear_svm_evaluation
 
+# Download datasets.
 classes = dp.get_dataset("MOLT-4")
 use_labels, use_edge_labels = True, True
 
 all_matrices = []
+# Compute 1-WL kernel for 1 to 5 iterations.
 for i in range(1, 6):
     # Use node labels and edge labels.
     gm = kb.compute_wl_1_sparse(dataset, i, use_labels, use_edge_labels)

### 2020-06-29 paper/networkx.py

@@ -1,0 +1,10 @@
+import auxiliarymethods.datasets as dp
+from auxiliarymethods.gnn_evaluation import gnn_evaluation
+
+dataset = "PROTEINS"
+
+# Download datasets.
+dp.get_dataset(dataset)
+# Output datasets as a list of graphs.
+graph_db = tud_to_networkx(dataset)
+

### 2020-06-29 tud_benchmark/main_kernel.py

@@ -6,8 +6,21 @@ from auxiliarymethods.kernel_evaluation import linear_svm_evaluation
 from auxiliarymethods.reader import tud_to_networkx
 
 
-
 def main():
+    dataset = "ENZYMES"
+
+    # Download datasets.
+    dp.get_dataset(dataset)
+    # Output datasets as a list of graphs.
+    graph_db = tud_to_networkx(dataset)
+
+    for g in graph_db:
+        for v in g.nodes(data=True):
+            print(g.nodes[v]['labels'])
+
+    exit()
+
+
     classes = dp.get_dataset("ZINC_test", regression=True)
     graph_db = tud_to_networkx("ZINC_test")
 
@@ -19,7 +32,6 @@ def main():
     num_reps = 10
 
     results = []
-
     for dataset, use_labels in dataset:
         classes = dp.get_dataset(dataset)
 

### 2020-07-03 paper/main.tex
minor changes

@@
 \icmlauthor{Nils \,M.\,Kriege}{vie}
-\icmlauthor{Franka Bause}{vie}
+\icmlauthor{Franka Bause}{tud}
 \icmlauthor{Kristian Kersting}{darm}
@@
 \icmlaffiliation{p}{CERC in Data Science for Real-Time Decision-Making, Polytechnique Montréal}
-\icmlaffiliation{vie}{Data Mining Group, Faculty of Computer Science, University of Vienna}
+\icmlaffiliation{tud}{Department of Computer Science, TU Dortmund University}
+\icmlaffiliation{vie}{Faculty of Computer Science, University of Vienna}
 \icmlaffiliation{darm}{Machine Learning Group, TU Darmstadt}
 \icmlaffiliation{bonn}{Department of Computer Science, University of Bonn}
-\icmlaffiliation{wustl}{Washington University in St. Louis}
+\icmlaffiliation{wustl}{Department of Computer Science and Engineering, Washington University in St. Louis}
 \icmlcorrespondingauthor{Christopher Morris}{christopher.morris@tu-dortmund.de}
@@
 The collection consists of over 120 datasets of varying sizes from a wide range of applications.
-We provide Python-based data loaders, kernel, and graph neural network baseline methods implementations, and evaluation tools.
+We provide Python-based data loaders, kernel, and graph neural network baseline implementations, and evaluation tools.
 Here, we give an overview of the datasets, standardized evaluation procedures, and provide baseline experiments.
@@
 \xhdr{Present work.} 
-Here, we give an overview of \textsc{\texttt{Anon}}.
+Here, we give an overview of \textsc{TUDataset}.
 The benchmark collection consists of over 120 datasets from a wide range of domains for supervised learning with graphs, i.e., classification and regression.
@@
 
-The \textsc{TUDataset} collection contains over 120 datasets provided at \texttt{www.graphlearning.io}.
+The \textsc{TUDataset} collection contains over 120 datasets provided at \url{www.graphlearning.io}.
 The datasets, baseline methods and experimental evaluation tools can be conveniently accessed from the Python interface, see \cref{evalcode} for further details.
-Moreover, see the website for dataset statistics, further documentation.
+Dataset statistics and further documentation is available at our website.
 
+\subsection{Datasets}
 Our collection of datasets covers graphs from various domains, contributed by different authors.
@@
 
-Our collection contains small datasets commonly used in the early graph kernel literature such as \textsc{Mutag}~\cite{Deb+1991} and \textsc{Ptc}~\cite{Helma2001}, medium-sized datasets, e.g., \textsc{Nci1} and \textsc{Nci109}~\cite{Wal+2008,She+2011}, as well as several large datasets derived from the \textsc{Tox21 Challenge 2014} or \textsc{PubChem}~\cite{Kim2018}.
+Our collection contains small datasets commonly used in the early graph kernel literature such as \textsc{Mutag}~\cite{Deb+1991} and \textsc{Ptc}~\cite{Helma2001}, medium-sized datasets, e.g., \textsc{Nci1} and \textsc{Nci109}~\cite{Wal+2008,She+2011}, as well as several large datasets derived from the \textsc{Tox21} challenge 2014 or \textsc{PubChem}~\cite{Kim2018}.
 This includes the eleven datasets from anticancer screen tests with different cancer cell lines used by~\citet{Yan2008} to demonstrate the efficacy of classifiers based on significant graph patterns.
@@
 We repeat the above evaluation ten times and report standard deviations over all ten repetitions, and additionally across all one hundred runs (i.e., ten repetitions with ten folds each).
-For the large-scale molecule learning tasks, we either use random splits (80\%/10\%/10\%) or provided, fixed splits and report MAE (mean std.
+For the large-scale molecule learning tasks, we either use random splits (80\%/10\%/10\%) or the provided, fixed splits and report MAE (mean std.
 MAE, mean std.
@@
 See the website for dataset statistics.
-We opted for not using continuous node features of the small datasets (if available) and the 3D-coordinates of the \textsc{Alchemy} dataset to solely provide baseline results based on graph structure.
+We opted for not using continuous node features of the small datasets (if available) and the 3D-coordinates of the \textsc{Alchemy} dataset to solely provide baseline results based on graph structure and discrete labels.
 In case of the \textsc{QM9} dataset, we closely replicated the (continuous) node and edge features of~\citet{Gil+2017}.
 
-\xhdr{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree} (\textsc{$1$-WL})~\cite{She+2011}, \new{Shortest-path} (\textsc{SP})~\cite{Bor+2005}, \new{Graphlet} (\textsc{GR})~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} (\textsc{WL-OA})~\cite{Kri+2016} included in the \textsc{\texttt{Anon}} package.
+\xhdr{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree} (\textsc{$1$-WL})~\cite{She+2011}, \new{Shortest-path} (\textsc{SP})~\cite{Bor+2005}, \new{Graphlet} (\textsc{GR})~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} (\textsc{WL-OA})~\cite{Kri+2016} included in the \textsc{TUDataset} package.
 The $C$-parameter was selected from $\{10^{-3}, 10^{-2}, \dotsc, 10^{2},$ $10^{3}\}$ from the validation set.
@@
 
-\xhdr{Results and discussion}
+\xhdr{Results and discussion.}
 \cref{t2l,t2ll,neural_short_tt} summarize the results.
@@
 However, it does not scale to large datasets, \cref{t2l}, as it relies on Gram matrix computation.
-Here, the $1$-WL performs well on all datasets, excluding \textsc{github\_stargazers}, where the neural baseline perform best overall.\footnote{For the neural baselines unlike the kernel baselines, we used one-hot degree features for datasets that do not provide node labels.}
+Here, the $1$-WL performs well on all datasets, excluding \textsc{github\_stargazers}, where the neural baselines perform best overall.\footnote{For the neural baselines unlike the kernel baselines, we used one-hot degree features for datasets that do not provide node labels.}
 Our results show that despite the extensive research on GNNs in recent years, classical graph kernels in combination with SVMs are still highly competitive in graph classification tasks.
@@
 
-We thank evefrybody who provided datasets to the  \textsc{TUDataset} collection.
+We thank everybody who provided datasets for the  \textsc{TUDataset} collection.
+
+This work has been partially funded by the Deutsche Forschungsgemeinschaft (DFG) within 
+the Collaborative Research Center SFB 876 ``Providing Information by 
+Resource-Constrained Data Analysis'', project A6 ``Resource-efficient Graph Mining''.
+Nils Kriege has been supported by the Vienna Science and Technology Fund (WWTF) 
+through project VRG19-009.
+
 %\newpage
@@
 \section{Experimental protocol and hyperparameters for \textsc{Zinc}, \textsc{Alchemy}, \textsc{QM9}}\label{eval}
-For the larger molecular regression tasks, \textsc{Zinc} and \textsc{Alchemy}\footnote{Note that the full dataset is different from the contest dataset, e.g., it does not provide normalized targets, see \url{https://alchemy.tencent.com/}.}, we closely followed the hyperparameters found in~\cite{Dwi+2020} and~\cite{Che+2020}, respectively, for the \textsc{Gine-$\varepsilon$} layers.
+For the larger molecular regression tasks, \textsc{Zinc} and \textsc{Alchemy},\footnote{Note that the full dataset is different from the contest dataset, e.g., it does not provide normalized targets, see \url{https://alchemy.tencent.com/}.} we closely followed the hyperparameters found in~\cite{Dwi+2020} and~\cite{Che+2020}, respectively, for the \textsc{Gine-$\varepsilon$} layers.
 That is, for \textsc{Zinc}, we used four \textsc{Gine-$\varepsilon$} layers with a hidden dimension of 256 followed by batch norm and a $4$-layer MLP for the joint regression of the twelve targets, after applying mean pooling.
@@
 For the \textsc{Gine-$\varepsilon$}  and the \textsc{MPNN} architecture, following~\citeauthor{Gil+2017}~\cite{Gil+2017}, we used a complete graph, computed pairwise $\ell_2$ distances based on the 3D-coordinates, and concatenated them to the edge features.
-We note here that our intent is not the beat state-of-the-art, physical knowledge-incorporating architectures, e.g., \textsc{DimeNet}~\cite{Kli+2020} or \textsc{Cormorant}~\cite{And+2019}, but to solely provide baseline scores.
+We note here that our intent is not to beat the state-of-the-art, physical knowledge-incorporating architectures, e.g., \textsc{DimeNet}~\cite{Kli+2020} or \textsc{Cormorant}~\cite{And+2019}, but to solely provide baseline scores.
 

### 2020-07-04 paper/main.tex
MC.

@@
 All datasets are available at \url{www.graphlearning.io}.
-The experiments are fully reproducible from the code available at \url{www.github.com/chrsmrrs/tudatasets}.
+The experiments are fully reproducible from the code available at \url{www.github.com/chrsmrrs/tudataset}.
 \end{abstract}
@@
 To develop successful machine learning models in these domains, we need techniques that can exploit the rich information inherent in the graph structure, as well as the feature information contained within nodes and edges.
-In recent years, numerous approaches have been proposed for machine learning with graphs---most notably, approaches based on \new{graph kernels}~\cite{Kri+2019} and \new{graph neural networks} (GNNs)~\cite{Gil+2017}.
+In recent years, numerous approaches have been proposed for machine learning with graphs---most notably, approaches based on \new{graph kernels}~\cite{Kri+2019} and \new{graph neural networks} (GNNs)~\cite{Sca+2009,Gil+2017}.
 However, most papers, even recent ones, evaluate newly proposed architectures or methods on a fixed set of small-scale benchmark datasets leading to high standard deviations and hard to interpret results.
@@
 All datasets are provided in a standard dataset format at \url{www.graphlearning.io} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019}\footnote{\url{https://pytorch-geometric.readthedocs.io/en/latest/modules/datasets.html}} and \textsc{DGL}~\cite{Wan+2019}\footnote{\url{https://docs.dgl.ai/en/0.4.x/api/python/data.html}}.
-To facilitate standard comparison of kernel and neural approaches, we provide implementations of standard algorithms and easy-to-use evaluation procedures.
+To facilitate a standard comparison of kernel and neural approaches, we provide implementations of standard algorithms and easy-to-use evaluation procedures.
 Moreover, we report results on an experimental study comparing graph kernels and GNNs on a subset of the \textsc{TUDataset}.
@@
 \textsc{Collab} are datasets derived from scientific collaboration networks.
-Each graph is the ego-network of a researcher, and the task is to predict his research field, i.e., high energy, condensed matter, or astrophysics.
+Each graph is the ego-network of a researcher, and the task is to predict their research field, i.e., high energy, condensed matter, or astrophysics.
 Similarly, the \textsc{Imdb} datasets consist of ego-networks derived from actor collaborations, and the task is to predict the genre, e.g.,  Action vs.\@ Romance.
@@
 \subsection{Baselines methods} To provide meaningful baselines, we provide implementations of common graph kernels as well as GNN architectures.
-We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} (using labeled subgraphs with three nodes), \new{Weisfeiler-Lehman Optimal Assignment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{TUDatasets}.
+We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} (using labeled subgraphs with three nodes), \new{Weisfeiler-Lehman Optimal Assignment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{TUDataset}.
 Moreover, all GNN architectures provided by \textsc{PyTorch Geometric} can be conveniently used as a baseline as well.
@@
 \subsection{Evaluation methods}\label{evalm} To ensure a fair and meaningful comparison between methods, we propose the following evaluation procedures for kernels and GNNs.
-First, for kernels we propose the established $C$-SVM implementation \textsc{LibSvm}~\cite{Cha+11} for kernels that compute a Gram matrix, and the linear $C$-SVM implementation \textsc{LibLinear}~\cite{Fan+2008} for kernels  that can be computed based on sparse, explicit feature maps.
+First, for kernels, we propose the established $C$-SVM implementation \textsc{LibSvm}~\cite{Cha+11} for kernels that compute a Gram matrix, and the linear $C$-SVM implementation \textsc{LibLinear}~\cite{Fan+2008} for kernels  that can be computed based on sparse, explicit feature maps.
 We optimize GNNs end-to-end using \textsc{Adam}~\cite{Kin+2015}.
@@
 	\label{t2l}	
-	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.05}
+	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{.95}
 		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule
@@
 	\label{t2ll}	
-	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.05}
+	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{.95}
 		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
 			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
-			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Yeast}}           & {\textsc{github\_star.}}       & {\textsc{reddit\_threads}}      \\	\toprule
+			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Yeast}}           & {\textsc{github\_star}}       & {\textsc{reddit\_threads}}      \\	\toprule
 			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
@@
 We used mean pooling to pool the learned node embeddings to a graph embedding and used a $2$-layer MLP for the final classification, using a dropout layer with $p = 0.5$ after the first layer of the MLP.
-We optimized the number of hidden units from $
+For the smaller datasets of~\cref{t2l}, we optimized the number of hidden units from $
 \{ 32, 64, 128\}$, the number of layers from $ \{1, 2, 3, 4, 5\}$ using the validation set.
-Moreover, we use a learning rate decay of $0.5$ with a patience parameter of $5$, a starting learning rate of $0.01$ and a minimum of $10^{-6}$.
+For the mid-scale datasets, due to computation time constraints, we set the number of hidden units to $64$ and the number of layers to $3$.
+Moreover, we use a learning rate decay of $0.5$ with a patience parameter of $5$, a starting learning rate of $0.01$ and a minimum of $10^{-6}$, a maximum epoch number of $200$.
 For both methods, we used the evaluation procedure described in~\cref{evalm} to optimize hyperparameters and compute accuracies.
 See the appendix for details on the hyperparameter and evaluation protocols used for the larger molecular regression tasks (\textsc{Zinc}, and \textsc{Alchemy}, \textsc{QM9}).
-
 All results are reproducible using the scripts provided at \url{https://github.com/chrsmrrs/tudatasets}.
@@
 \cref{t2l,t2ll,neural_short_tt} summarize the results.
-On the small-scale datasets, see \cref{t2l}, the \textsc{WLOA} performs best overall, i.e., only on the \textsc{IMDB-Binary} and the \textsc{Reddit-Binary} dataset it is beaten by the $1$-\textsc{WL} or the neural baselines.
-However, it does not scale to large datasets, \cref{t2l}, as it relies on Gram matrix computation.
+On the small-scale datasets, see \cref{t2l}, the \textsc{WL-OA} performs best overall, i.e., only on the \textsc{IMDB-Binary} and the \textsc{Reddit-Binary} dataset it is beaten by the $1$-\textsc{WL} or the neural baselines.
+However, it does not scale to large datasets, \cref{t2ll}, as it relies on Gram matrix computation.
 Here, the $1$-WL performs well on all datasets, excluding \textsc{github\_stargazers}, where the neural baselines perform best overall.\footnote{For the neural baselines unlike the kernel baselines, we used one-hot degree features for datasets that do not provide node labels.}
@@
 
+\section{Dataset statistics}
+
 \end{document}

### 2020-07-04 tud_benchmark/main_gnn.py

@@ -37,7 +37,7 @@ def main():
     dataset = [["MOLT-4", True, True], ["Yeast", True, True], ["MCF-7", True, True],
                  ["github_stargazers", False, False],
                  ["reddit_threads", False, False]]
-    
+
     for d, use_labels, _ in dataset:
         dp.get_dataset(d)
 

### 2020-07-04 paper/main.tex
New exp. for Yeast (replaces TRIANGLES)

@@
 For the mid-scale datasets, due to computation time constraints, we set the number of hidden units to $64$ and the number of layers to $3$.
-Moreover, we use a learning rate decay of $0.5$ with a patience parameter of $5$, a starting learning rate of $0.01$ and a minimum of $10^{-6}$, a maximum epoch number of $200$.
+Moreover, for both, we use a learning rate decay of $0.5$ with a patience parameter of $5$, a starting learning rate of $0.01$ and a minimum of $10^{-6}$, a maximum epoch number of $200$.
 For both methods, we used the evaluation procedure described in~\cref{evalm} to optimize hyperparameters and compute accuracies.
@@
 \section{Dataset statistics}
+\begin{table}[h]
+	\begin{center}
+		\caption{Dataset statistics and properties, $^\dagger$---Continuous vertex labels following~\cite{Gil+2017}, the last three components encode 3D coordinates.}
+		\resizebox{1.0\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.05}
+			\begin{tabular}{@{}lcccccc@{}}\toprule
+				\multirow{3}{*}{\vspace*{4pt}\textbf{Dataset}}&\multicolumn{6}{c}{\textbf{Properties}}\\
+				\cmidrule{2-7}
+				& Number of  graphs & Number of classes/targets & $\varnothing$ Number of vertices & $\varnothing$ Number of edges & Vertex labels & Edge labels \\ \midrule
+				$\textsc{Enzymes}$       & 600               & 6                 & 32.6                             & 62.1                          & \cmark  & \xmark           \\
+				$\textsc{IMDB-Binary}$   & 1\,000              & 2                 & 19.8                             & 96.5                          & \xmark   & \xmark          \\
+				$\textsc{IMDB-Multi}$         & 1\,500               & 3                & 13.0                             & 65.9                          & \xmark    & \xmark         \\
+				$\textsc{NCI1}$          & 4\,110              & 2                 & 29.9                             & 32.3                          & \cmark   & \xmark          \\
+				$\textsc{NCI109}$        & 4\,127              & 2                 & 29.7                             & 32.1                          & \cmark    & \xmark         \\
+				$\textsc{PTC\_FM}$       & 349               & 2                 & 14.1                             & 14.5                          & \cmark    & \xmark         \\
+				$\textsc{Proteins}$      & 1\,113              & 2                 & 39.1                             & 72.8                          & \cmark    & \xmark         \\
+				$\textsc{Reddit-Binary}$ & 2\,000              & 2                 & 429.6                            & 497.8                         & \xmark     & \xmark        \\ \midrule
+
+				$\textsc{Yeast}$       &   79\,601&	2&	21.5&	22.8                & \cmark  & \cmark           \\
+				$\textsc{YeastH}$       &  79\,601&	2&	39.4&	40.7                  & \cmark  & \cmark           \\
+				$\textsc{UACC257}$       &      39\,988&	2&	26.1&	28.1                      & \cmark  & \cmark           \\
+				$\textsc{UACC257H}$       &  39\,988&	2&	46.7&	48.7      & \cmark  & \cmark           \\
+				$\textsc{OVCAR-8}$       &      	40\,516&	2&	26.1&	28.1             & \cmark  & \cmark           \\
+				$\textsc{OVCAR-8H}$       &        40\,516	&2&	46.7&	48.7              & \cmark  & \cmark           \\
+				\midrule        
+				%$\textsc{Zinc (10k)}$       & 12\,000 & 12	&&	     & \cmark  & \cmark           \\
+				%$\textsc{Zinc (50k)} $       & 60\,000  & 12	&&	     & \cmark  & \cmark           \\
+				$\textsc{Zinc}$       &  249\,456 &12	&23.1 &	24.9     & \cmark  & \cmark           \\
+
+				%$\textsc{Alchemy (10k)}$       & 12\,000 &12	& &	     & \cmark  & \cmark           \\
+				%$\textsc{Alchemy (50k)} $       &60\,000 &12	&&	     & \cmark  & \cmark           \\
+				$\textsc{Alchemy}$       & 202\,579 &12	& 10.1 &	10.4 	     & \cmark  & \cmark           \\
+				$\textsc{QM9}$       &129\,433  &12	& 18.0 &	18.6     & \cmark (13+3D)$^\dagger$  & \cmark (4)          \\
+				\bottomrule
+		\end{tabular}}
+		\label{ds}
+	\end{center}
+\end{table}
 

### 2020-07-04 tud_benchmark/kernel_baselines/src/AuxiliaryMethods.h

@@ -37,13 +37,6 @@ namespace AuxiliaryMethods {
     vector<int> read_classes(string data_set_name);
        vector<float> read_targets(string data_set_name);
 
-    // Write Gram matrix to file.
-    void write_gram_matrix(const GramMatrix &gram_matrix, string file_name);
-
-    void write_sparse_gram_matrix(const GramMatrix &gram_matrix, string file_name);
-
-    void write_libsvm(const GramMatrix &gram_matrix, const vector<int> classes, std::string filename);
-
     // Pairing function to map a pair of Labels to a single label.
     Label pairing(const Label a, const Label b);
     

### 2020-07-04 tud_benchmark/main_gnn.py

@@ -11,29 +11,28 @@ def main():
                ["REDDIT-BINARY", False], ["ENZYMES", True]]
 
     results = []
-    # for d, use_labels in dataset:
-    #     # Download dataset.
-    #     dp.get_dataset(d)
-    #
-    #     # GIN, dataset d, layers in [1:5], hidden dimension in {32,64,128}.
-    #     acc, s_1, s_2 = gnn_evaluation(GIN, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200, batch_size=64,
-    #                                    start_lr=0.01, num_repetitions=num_reps, all_std=True)
-    #     print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #     results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #
-    #     # GIN with jumping knowledge, dataset d, layers in [1:5], hidden dimension in {32,64,128}.
-    #     acc, s_1, s_2 = gnn_evaluation(GINWithJK, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200,
-    #                                        batch_size=64,
-    #                                        start_lr=0.01, num_repetitions=num_reps, all_std=True)
-    #     print(d + " " + "GINWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #     results.append(d + " " + "GINWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
+    for d, use_labels in dataset:
+        # Download dataset.
+        dp.get_dataset(d)
+
+        # GIN, dataset d, layers in [1:5], hidden dimension in {32,64,128}.
+        acc, s_1, s_2 = gnn_evaluation(GIN, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200, batch_size=64,
+                                       start_lr=0.01, num_repetitions=num_reps, all_std=True)
+        print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
+        results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
+
+        # GIN with jumping knowledge, dataset d, layers in [1:5], hidden dimension in {32,64,128}.
+        acc, s_1, s_2 = gnn_evaluation(GINWithJK, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200,
+                                           batch_size=64,
[…]

### 2020-07-06 paper/main.tex
added more motivation and removed critical sentence

--- 2020-07-03 paper/main.tex
@@
 Recently, there has been an increasing interest in (supervised) learning with graph data, especially using graph neural networks.
-However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging.
-That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area.
+However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging, consequently hindering advancements in this area.
+% That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results
 To address this, we introduce the \textsc{TUDataset} for graph classification and regression.
@@
 In recent years, numerous approaches have been proposed for machine learning with graphs---most notably, approaches based on \new{graph kernels}~\cite{Kri+2019} and \new{graph neural networks} (GNNs)~\cite{Gil+2017}.
-However, most papers, even recent ones, evaluate newly proposed architectures or methods on a fixed set of small-scale benchmark datasets leading to high standard deviations and hard to interpret results.
-Moreover, non-standardized experimental setups are used, which hinders the comparison of results from different publications.
+Therefore, authoritative experimental evaluations are becoming increasingly important.
+However, these are complicated by the fact that (i) graph models are non standardized leading to different versions derived from the same source, and (ii) the experimental setup is not standardized.
+This hinders the comparison of results from different publications.
+Moreover, strong baseline methods are not used throughout the literature and the considered benchmark data sets are often too small, too easy to solve or insufficiently diverse.
 

### 2020-07-06 paper/main.tex

--- 2020-07-04 paper/main.tex
@@
 All datasets are available at \url{www.graphlearning.io}.
-The experiments are fully reproducible from the code available at \url{www.github.com/chrsmrrs/tudataset}.
+The experiments are fully reproducible from the code available at \url{www.github.com/chrsmrrs/tudatasets}.
 \end{abstract}
@@
 In recent years, numerous approaches have been proposed for machine learning with graphs---most notably, approaches based on \new{graph kernels}~\cite{Kri+2019} and \new{graph neural networks} (GNNs)~\cite{Sca+2009,Gil+2017}.
-However, most papers, even recent ones, evaluate newly proposed architectures or methods on a fixed set of small-scale benchmark datasets leading to high standard deviations and hard to interpret results.
-Moreover, non-standardized experimental setups are used, which hinders the comparison of results from different publications.
+Therefore, authoritative experimental evaluations are becoming increasingly important.
+However, these are complicated by the fact that (i) graph models are non standardized leading to different versions derived from the same source, and (ii) the experimental setup is not standardized.
+This hinders the comparison of results from different publications.
+Moreover, strong baseline methods are not used throughout the literature and the considered benchmark data sets are often too small, too easy to solve or insufficiently diverse.
 

### 2020-07-06 paper/main.tex
fixed tudatasets -> tudataset

@@
 See the appendix for details on the hyperparameter and evaluation protocols used for the larger molecular regression tasks (\textsc{Zinc}, and \textsc{Alchemy}, \textsc{QM9}).
-All results are reproducible using the scripts provided at \url{https://github.com/chrsmrrs/tudatasets}.
+All results are reproducible using the scripts provided at \url{https://github.com/chrsmrrs/tudataset}.
 

### 2020-07-06 paper/main.tex
New results.

@@
 Recently, there has been an increasing interest in (supervised) learning with graph data, especially using graph neural networks.
-However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging, consequently hindering advancements in this area.
-% That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results
+However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging.
+That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area.
 To address this, we introduce the \textsc{TUDataset} for graph classification and regression.
@@
 In recent years, numerous approaches have been proposed for machine learning with graphs---most notably, approaches based on \new{graph kernels}~\cite{Kri+2019} and \new{graph neural networks} (GNNs)~\cite{Sca+2009,Gil+2017}.
-Therefore, authoritative experimental evaluations are becoming increasingly important.
-However, these are complicated by the fact that (i) graph models are non standardized leading to different versions derived from the same source, and (ii) the experimental setup is not standardized.
-This hinders the comparison of results from different publications.
-Moreover, strong baseline methods are not used throughout the literature and the considered benchmark data sets are often too small, too easy to solve or insufficiently diverse.
+However, most papers, even recent ones, evaluate newly proposed architectures or methods on a fixed set of small-scale benchmark datasets leading to high standard deviations and hard to interpret results.
+Moreover, non-standardized experimental setups are used, which hinders the comparison of results from different publications.
 
@@
 
-%\subsection{Datasets}
-
 \begin{table*}[ht]\centering		
@@
 
-			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &   $52.3$ \scriptsize $\pm 0.7 \pm 6.7 $       & $72.6$ \scriptsize $\pm  0.6 \pm 4.1$ &  $50.3$ \scriptsize $\pm 0.8 \pm  3.8 $ & $84.5$ \scriptsize $\pm 0.3 \pm 1.7$ & $72.8$ \scriptsize $\pm 0.8 \pm  3.9 $ & $73.9$ \scriptsize $\pm 0.6 \pm 3.2$  \\
-			%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-			%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
-			& \text{WL-OA} & $58.4$ \scriptsize $\pm 2.0 \pm 7.4$   &  $73.2$ \scriptsize $\pm 0.8 \pm 3.8$ & $49.4$ \scriptsize $\pm 0.3 \pm 3.6 $ & $85.4$ \scriptsize $\pm  0.2 \pm 1.4$ & $73.2$ \scriptsize $\pm 0.6 \pm 3.5$ & $88.4$ \scriptsize $\pm 0.4 \pm 2.1 $   \\
-			& \text{GR}            &    $30.1$ \scriptsize $\pm 0.8 \pm 6.0$       & $59.0$ \scriptsize $\pm 0.9 \pm 5.7$ & $39.6$ \scriptsize $\pm 0.5 \pm 3.6  $ & $66.2$ \scriptsize $\pm 0.2\pm 2.2$ & $71.4$ \scriptsize $\pm 0.6\pm 4.4 $ & $60.0$ \scriptsize $\pm 0.2 \pm  2.7$   \\
-			& \text{SP}            & $40.5$  \scriptsize $\pm 1.6 \pm 6.2$       & $58.7$ \scriptsize $\pm 0.9 \pm 4.6 $ & $39.5$ \scriptsize $\pm 0.9 \pm 4.2$ & $74.5$ \scriptsize $\pm 0.4\pm 2.2 $  &$75.9$ \scriptsize $\pm 0.6 \pm 4.0$ & $84.6$ \scriptsize $\pm0.2\pm 0.4 $  \\
+			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &  50.8 \scriptsize $\pm1.4 \pm 7.1$  & 72.4 \scriptsize $\pm 0.7 \pm 4.4$ & 50.5 \scriptsize $\pm 0.8 \pm 3.6$  &  84.2 \scriptsize $\pm 0.3 \pm 1.8$  & 72.6 \scriptsize $\pm 0.7 \pm 3.4$ & 73.3 \scriptsize $\pm 0.7 \pm 3.0$    \\
+			& \text{WL-OA} &  56.4 \scriptsize $\pm 1.1 \pm 6.6$ & 73.3 \scriptsize $\pm 0.6 \pm 4.2$  & 49.9 \scriptsize $\pm 0.6 \pm 3.8$ & 85.0 \scriptsize $\pm 0.3 \pm 1.8$  & 73.4 \scriptsize $\pm 0.9 \pm 4.3$ &   88.3 \scriptsize $\pm 0.4 \pm 2.3$    \\
+			& \text{GR} & 29.5 \scriptsize $\pm 0.7 \pm 5.4$  &  59.8 \scriptsize $\pm 1.1 \pm 4.9$ & 39.5 \scriptsize $\pm 0.7 \pm 4.0$ & 66.0 \scriptsize $\pm 0.4 \pm 2.4$  & 71.6 \scriptsize $\pm 0.6 \pm 4.0$ &  59.7 \scriptsize $\pm 0.5 \pm 3.8$          \\
+			& \text{SP} & 39.3 \scriptsize $\pm 1.8 \pm 7.1$ & 58.4 \scriptsize $\pm 1.7 \pm 5.3$  & 39.4 \scriptsize $\pm 0.8 \pm 4.4$ &74.2 \scriptsize $\pm 0.3 \pm 2.1$  & 75.6 \scriptsize $\pm 0.7 \pm 4.0$ &     84.5 \scriptsize $\pm 0.2 \pm 2.5$      \\
 			\cmidrule{2-8}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \textsc{Gin-$\varepsilon$}   &  39.5 \scriptsize $\pm 1.4 \pm 7.6 $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
-			& \textsc{Gin-$\varepsilon$-JK} &  41.3 \scriptsize $\pm 1.8 \pm 6.7$       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \textsc{Gin-$\varepsilon$}   & 38.7  \scriptsize $\pm 1.5 \pm 7.6$  &72.9  \scriptsize $\pm 0.7 \pm 4.7$ & 49.7  \scriptsize $\pm0.7 \pm 4.4$ & 77.7 \scriptsize $\pm 0.8 \pm 2.3$ & 72.2  \scriptsize $\pm 0.6 \pm 4.8$ &  89.8  \scriptsize $\pm 0.4 \pm 2.2$ \\
+			& \textsc{Gin-$\varepsilon$-JK} &  39.3  \scriptsize $\pm 1.6 \pm 6.7$ & 73.0  \scriptsize $\pm 1.1 \pm 4.5$  & 49.6  \scriptsize $\pm 0.7 \pm 4.0$ & 78.3  \scriptsize $\pm 0.3 \pm 2.0$ & 72.2  \scriptsize $\pm 0.7 \pm 4.6$ & 90.4  \scriptsize $\pm 0.4 \pm 2.2$ \\
 			\bottomrule
@@
 \end{table*}
+
 \begin{table*}[t]\centering		
@@
 			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
-			$94.5$ \scriptsize $<0.1 \pm 0.4$  &$94.6$ \scriptsize $\pm 0.1  \pm 0.3$ & $89.2$ \scriptsize $\pm 0.1 \pm 0.4$ &  $63.9$ \scriptsize $\pm 0.1\pm 1.3$ &$77.0$ \scriptsize $<0.1 \pm 0.3$  \\
-
-			& \text{GR}            & $91.7$  \scriptsize $<0.1  \pm 0.5 $       & $92.1$ \scriptsize $<0.1 \pm 0.4$ & $88.2$ \scriptsize $<0.1  \pm 0.4$ &  $53.5$ \scriptsize $<0.1 \pm 1.3$ & $51.2$ \scriptsize $<0.1 \pm 0.4$  \\
-			& \text{SP}             &  $91.7$  \scriptsize $<0.1 \pm 0.4 $       &$92.1$  \scriptsize $<0.1 \pm 0.4 $ & $88.2$ \scriptsize $<0.1  \pm 0.4$ & $64.1$ \scriptsize $\pm 0.1\pm 1.4$ & $77.3$ \scriptsize $<0.1 \pm 0.3$  \\
+			    94.5 \scriptsize $\pm 0.02 \pm 0.3$      & 94.6 \scriptsize $\pm 0.04 \pm 0.4$ & 89.2 \scriptsize $\pm 0.01 \pm 0.4$ & 64.0 \scriptsize $\pm 0.22 \pm 1.4$ &77.0 \scriptsize $\pm 0.01 \pm 0.3$  \\
+			& \text{GR} & 91.7 \scriptsize $<0.01 \pm 0.5$ &92.1 \scriptsize $\pm 0.01 \pm 0.4$ &  88.2 \scriptsize $\pm 0.01 \pm 0.3$ &53.6 \scriptsize $\pm 0.20 \pm 1.6$ &  51.2 \scriptsize $< 0.01 \pm 0.3$ \\
+			& \text{SP}  & 91.7 \scriptsize $\pm 0.02 \pm 0.6$ & 92.1 \scriptsize $<0.01 \pm 0.4$ &88.2 \scriptsize $\pm 0.01 \pm 0.4$ & 64.2 \scriptsize $\pm 0.01 \pm 1.3$ &   77.3 \scriptsize $\pm 0.01 \pm 0.2$\\
 			\cmidrule{2-7}	
-			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \textsc{Gine-$\varepsilon$}         &  $92.0$ \scriptsize $\pm  0.1 \pm 0.6$       & $92.3$ \scriptsize $\pm 0.1 \pm 0.6$ & 88.3 \scriptsize $<0.1 \pm 0.3$ &  $67.1$ \scriptsize $\pm 0.5 \pm 1.6  $ & $77.2$ \scriptsize $<0.1  \pm 0.3$ \\
-			& \textsc{Gine-$\varepsilon$-JK}   &   $91.8$ \scriptsize $<0.1 \pm 0.5$       & $92.2$ \scriptsize $<0.1 \pm 0.5$ & 88.2  \scriptsize $<0.1 \pm 0.3$ & $67.2$ \scriptsize $\pm 0.4 \pm 1.3$ &  $77.3$  \scriptsize $<0.1 \pm 0.3 $  \\
+			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \textsc{Gine-$\varepsilon$}  & 92.0 \scriptsize $\pm 0.03 \pm 0.6$ & 92.4 \scriptsize $\pm 0.07 \pm 0.6$ & 88.3 \scriptsize $\pm 0.02 \pm 0.4$ & 66.8 \scriptsize $\pm 0.17 \pm 1.4$  &  77.2 \scriptsize $\pm 0.03  \pm 0.3$\\
+			& \textsc{Gine-$\varepsilon$-JK}   &  91.8 \scriptsize $\pm 0.03 \pm 0.6$ & 92.2 \scriptsize $\pm 0.03 \pm 0.4$ & 88.2 \scriptsize $\pm 0.02 \pm 0.3$ & 67.1 \scriptsize $\pm 0.34 \pm 1.1$ & 77.2 \scriptsize $\pm 0.04  \pm 0.3$ \\
 			\bottomrule
@@
 See the appendix for details on the hyperparameter and evaluation protocols used for the larger molecular regression tasks (\textsc{Zinc}, and \textsc{Alchemy}, \textsc{QM9}).
-All results are reproducible using the scripts provided at \url{https://github.com/chrsmrrs/tudataset}.
+All results are reproducible using the scripts provided at \url{https://github.com/chrsmrrs/tudatasets}.
 

### 2020-07-06 paper/main.tex
New results.
MC.

@@
 \icmlauthor{Christopher Morris}{p}
-\icmlauthor{Nils \,M.\,Kriege}{vie}
+\icmlauthor{Nils M.\,Kriege}{vie}
 \icmlauthor{Franka Bause}{tud}
@@
 Graph-structured data is ubiquitous across application domains ranging from chemo- and bioinformatics~\cite{Barabasi2004,Sto+2020} to image~\cite{Sim+2017} and social network analysis~\cite{Eas+2010}.
-To develop successful machine learning models in these domains, we need techniques that can exploit the rich information inherent in the graph structure, as well as the feature information contained within nodes and edges.
+To develop successful machine learning models in these domains, we need techniques that can exploit the rich information inherent in the graph structure and the feature information contained within nodes and edges.
 In recent years, numerous approaches have been proposed for machine learning with graphs---most notably, approaches based on \new{graph kernels}~\cite{Kri+2019} and \new{graph neural networks} (GNNs)~\cite{Sca+2009,Gil+2017}.
-Therefore, authoritative experimental evaluations are becoming increasingly important.
-However, these are complicated by the fact that (i) graph models are non standardized leading to different versions derived from the same source, and (ii) the experimental setup is not standardized.
-This hinders the comparison of results from different publications.
-Moreover, strong baseline methods are not used throughout the literature and the considered benchmark data sets are often too small, too easy to solve or insufficiently diverse.
+However, most papers, even recent ones, evaluate newly proposed architectures or methods on a fixed set of small-scale, non-diverse benchmarks, using non-standardized experimental protocols and baselines, hindering the comparison of results from different publications.
 
@@
 For a theoretical investigation of graph kernels, see~\cite{Kri+2018}.
-Recently, graph neural networks (GNNs)~\cite{Gil+2017,Sca+2009} emerged as an alternative to graph kernels.
+Recently, graph neural networks~\cite{Gil+2017,Sca+2009} emerged as an alternative to graph kernels.
 Notable instances of this architecture include, e.g.,~\cite{Duv+2015,Ham+2017,Vel+2018}, and the spectral approaches proposed in, e.g.,~\cite{Bru+2014,Def+2015,Kip+2017,Mon+2017}---all of which descend from early work in~\cite{Kir+1995,Mer+2005,Spe+1997,Sca+2009}.
@@
 
-The papers~\cite{Fey+2019,Che+2019new,Err+2019,Dwi+2020} evaluate GNNs using a unified evaluation procedure, however, they only use small- or medium scale datasets.
+The papers~\cite{Fey+2019,Che+2019new,Err+2019,Dwi+2020} evaluate GNNs using a unified evaluation procedure, however, they only use small- or medium-scale datasets.
 Recently, \url{ogb.stanford.edu}~\cite{Hu+2020} launched, however, the provided datasets for graph classification focus on chemistry and bioinformatic applications, and the number is quite limited at this point.
@@
 \citet{Rozemberczki2020} used similar approaches to obtain more massive social network datasets.
-\textsc{Reddit\_Threads} contains more than 200k graphs with the task to predict whether a thread is discussion-based.
-\textsc{Deezer\_Ego\_Nets} and \textsc{Twitch\_Egos} contain ego-networks derived from online services, and the task is to predict the gender and play behavior (single or multiple games) of the central user.
-\textsc{GitHub\_Stargazers} contains graphs representing the social networks of GitHub users divided into those who starred popular machine learning and web development repositories.
+\textsc{reddit\_threads} contains more than 200k graphs with the task to predict whether a thread is discussion-based.
+\textsc{deezer\_ego\_nets} and \textsc{twitch\_egos} contain ego-networks derived from online services, and the task is to predict the gender and play behavior (single or multiple games) of the central user.
+\textsc{github\_stargazers} contains graphs representing the social networks of GitHub users divided into those who starred popular machine learning and web development repositories.
 
@@
 We repeat the above evaluation ten times and report standard deviations over all ten repetitions, and additionally across all one hundred runs (i.e., ten repetitions with ten folds each).
+See \cref{eval} in the appendix for examples.
 For the large-scale molecule learning tasks, we either use random splits (80\%/10\%/10\%) or the provided, fixed splits and report MAE (mean std.
 MAE, mean std.
-logMAE for multi-target regression, see \cite{Kli+2020}) over five runs.
+logMAE for multi-target regression, see \cite{Kli+2020}), over five runs.
 
@@
 Moreover, we used the \textsc{Alchemy}, \textsc{QM9}, \textsc{Zinc} (multi-target) regression datasets.
-See the website for dataset statistics.
+See the website and \cref{ds} in the appendix for dataset statistics.
 We opted for not using continuous node features of the small datasets (if available) and the 3D-coordinates of the \textsc{Alchemy} dataset to solely provide baseline results based on graph structure and discrete labels.
@@
 For the mid-scale datasets, due to computation time constraints, we set the number of hidden units to $64$ and the number of layers to $3$.
-Moreover, for both, we use a learning rate decay of $0.5$ with a patience parameter of $5$, a starting learning rate of $0.01$ and a minimum of $10^{-6}$, a maximum epoch number of $200$.
+Moreover, for both, we use a learning rate decay of $0.5$ with a patience parameter of $5$, a starting learning rate of $0.01$ and a minimum of $10^{-6}$, and a maximum epoch number of $200$.
 For both methods, we used the evaluation procedure described in~\cref{evalm} to optimize hyperparameters and compute accuracies.
 See the appendix for details on the hyperparameter and evaluation protocols used for the larger molecular regression tasks (\textsc{Zinc}, and \textsc{Alchemy}, \textsc{QM9}).
-All results are reproducible using the scripts provided at \url{https://github.com/chrsmrrs/tudataset}.
 
@@
 \cref{t2l,t2ll,neural_short_tt} summarize the results.
-On the small-scale datasets, see \cref{t2l}, the \textsc{WL-OA} performs best overall, i.e., only on the \textsc{IMDB-Binary} and the \textsc{Reddit-Binary} dataset it is beaten by the $1$-\textsc{WL} or the neural baselines.
+On the small-scale datasets, see \cref{t2l}, the \textsc{WL-OA} performs best overall.
 However, it does not scale to large datasets, \cref{t2ll}, as it relies on Gram matrix computation.
@@
 
+See \url{www.graphlearning.io} for further documentation.
+
 \xhdr{Kernelized SVM for graph kernels based on Gram matrices}
@@
 All neural experiments were conducted on a workstation with four Nvidia Tesla V100 GPU cards with 32GB of GPU memory running Oracle Linux Server 7.7.
-
+\newpage
 \section{Dataset statistics}
@@
 
+				$\textsc{MCF-7}$       & 27\,770  & 2	&	26.4	&	 28.5               & \cmark  & \cmark           \\
+
+				$\textsc{Molt-7}$       & 39\,765  &	2	&	26.1	&	     	28.1          & \cmark  & \cmark           \\
 				$\textsc{Yeast}$       &   79\,601&	2&	21.5&	22.8                & \cmark  & \cmark           \\
-				$\textsc{YeastH}$       &  79\,601&	2&	39.4&	40.7                  & \cmark  & \cmark           \\
-				$\textsc{UACC257}$       &      39\,988&	2&	26.1&	28.1                      & \cmark  & \cmark           \\
-				$\textsc{UACC257H}$       &  39\,988&	2&	46.7&	48.7      & \cmark  & \cmark           \\
-				$\textsc{OVCAR-8}$       &      	40\,516&	2&	26.1&	28.1             & \cmark  & \cmark           \\
-				$\textsc{OVCAR-8H}$       &        40\,516	&2&	46.7&	48.7              & \cmark  & \cmark           \\
+				$\textsc{github\_star}$       &  12\,725 & 2	& 	113.8		&	234.6               & \xmark  & \xmark           \\
+				$\textsc{reddit\_threads}$   &	203\,088	  & 2  &	23.9 &	25.0  		               & \xmark  & \xmark           \\
 				\midrule        
-				%$\textsc{Zinc (10k)}$       & 12\,000 & 12	&&	     & \cmark  & \cmark           \\
-				%$\textsc{Zinc (50k)} $       & 60\,000  & 12	&&	     & \cmark  & \cmark           \\
 				$\textsc{Zinc}$       &  249\,456 &12	&23.1 &	24.9     & \cmark  & \cmark           \\
-
-				%$\textsc{Alchemy (10k)}$       & 12\,000 &12	& &	     & \cmark  & \cmark           \\
-				%$\textsc{Alchemy (50k)} $       &60\,000 &12	&&	     & \cmark  & \cmark           \\
 				$\textsc{Alchemy}$       & 202\,579 &12	& 10.1 &	10.4 	     & \cmark  & \cmark           \\

### 2020-07-09 paper/main.tex
Cleanup.

@@
 
-\usepackage[protrusion=true,expansion=false, activate={true,nocompatibility},final,kerning=true,spacing=true,shrink=40]{microtype}
+\usepackage[protrusion=true,expansion=false, activate={true,nocompatibility},final,kerning=true,spacing=true,stretch=10, shrink=65]{microtype}
 
@@
 \usepackage{pifont}
-\newcommand{\cmark}{\ding{51}}%
-\newcommand{\xmark}{\ding{55}}%
+\newcommand{\cmark}{\ding{51}}
+\newcommand{\xmark}{\ding{55}}
 
@@
 
-\icmlkeywords{Machine Learning, ICML}
+\icmlkeywords{graph learning, graph kernel, weisfeiler, leman, gnn, graph neural network, benchmark datasets}
 
@@
 
-\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
-%\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.
+\printAffiliationsAndNotice{}
 
@@
 However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging, consequently hindering advancements in this area.
-% That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results
 To address this, we introduce the \textsc{TUDataset} for graph classification and regression.
 The collection consists of over 120 datasets of varying sizes from a wide range of applications.
-We provide Python-based data loaders, kernel, and graph neural network baseline implementations, and evaluation tools.
+We provide Python-based data loaders, kernel and graph neural network baseline implementations, and evaluation tools.
 Here, we give an overview of the datasets, standardized evaluation procedures, and provide baseline experiments.
@@
 	\label{t2l}	
-	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{.95}
+	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{.9}
 		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule
@@
 	\label{t2ll}	
-	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{.95}
+	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{.9}
 		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
@@
 
-%\newpage
 \bibliography{bibliography}
@@
 
-\xhdr{Loading graphs as NetworkX graphs}
+\xhdr{Loading graphs in NetworkX format}
 \lstinputlisting[language=Python]{networkx.py}

### 2020-07-09 paper/example_gnn.py

@@ -6,7 +6,7 @@ from auxiliarymethods.reader import tud_to_networkx
 dataset = "PROTEINS"
 use_labels = True
 
-# Download datasets.
+# Download dataset.
 dp.get_dataset(dataset)
 
 # Optimize the number of layers ({1,2,3,4,5}) and

### 2020-07-09 paper/example_sparse.py

@@ -3,7 +3,7 @@ import auxiliarymethods.datasets as dp
 import kernel_baselines as kb
 from auxiliarymethods.kernel_evaluation import linear_svm_evaluation
 
-# Download datasets.
+# Download dataset.
 classes = dp.get_dataset("MOLT-4")
 use_labels, use_edge_labels = True, True
 

### 2020-07-09 paper/networkx.py

@@ -3,8 +3,8 @@ from auxiliarymethods.gnn_evaluation import gnn_evaluation
 
 dataset = "PROTEINS"
 
-# Download datasets.
+# Download dataset.
 dp.get_dataset(dataset)
-# Output datasets as a list of graphs.
+# Output dataset as a list of graphs.
 graph_db = tud_to_networkx(dataset)
 

### 2020-07-09 tud_benchmark/main_gnn.py

@@ -1,6 +1,6 @@
 import auxiliarymethods.datasets as dp
 from auxiliarymethods.gnn_evaluation import gnn_evaluation
-from gnn_baselines.gnn_architectures import GIN, GINWithJK
+from gnn_baselines.gnn_architectures import GIN, GINE, GINEWithJK, GINWithJK
 
 
 def main():
@@ -11,23 +11,22 @@ def main():
                ["REDDIT-BINARY", False], ["ENZYMES", True]]
 
     results = []
-    # for d, use_labels in dataset:
-    #     # Download dataset.
-    #     dp.get_dataset(d)
-    #
-    #     # GIN, dataset d, layers in [1:5], hidden dimension in {32,64,128}.
-    #     acc, s_1, s_2 = gnn_evaluation(GIN, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200, batch_size=64,
-    #                                    start_lr=0.01, num_repetitions=num_reps, all_std=True)
-    #     print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #     results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #
-    #     # GIN with jumping knowledge, dataset d, layers in [1:5], hidden dimension in {32,64,128}.
-    #     acc, s_1, s_2 = gnn_evaluation(GINWithJK, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200,
-    #                                        batch_size=64,
-    #                                        start_lr=0.01, num_repetitions=num_reps, all_std=True)
-    #     print(d + " " + "GINWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
-    #     results.append(d + " " + "GINWithJK " + str(acc) + " " + str(s_1) + " " + str(s_2))
+    for d, use_labels in dataset:
+        # Download dataset.
+        dp.get_dataset(d)
 
+        # GIN, dataset d, layers in [1:5], hidden dimension in {32,64,128}.
+        acc, s_1, s_2 = gnn_evaluation(GIN, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200, batch_size=64,
+                                       start_lr=0.01, num_repetitions=num_reps, all_std=True)
+        print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
[…]

### 2020-07-09 tud_benchmark/main_kernel.py

@@ -4,6 +4,7 @@ import kernel_baselines as kb
 from auxiliarymethods.kernel_evaluation import kernel_svm_evaluation
 from auxiliarymethods.kernel_evaluation import linear_svm_evaluation
 
+
 def main():
     ### Smaller datasets using LIBSVM.
     dataset = [["ENZYMES", True], ["IMDB-BINARY", False], ["IMDB-MULTI", False], ["NCI1", True], ["PROTEINS", True],
@@ -54,14 +55,13 @@ def main():
         print(dataset + " " + "SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(dataset + " " + "SP " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
-
     # Number of repetitions of 10-CV.
     num_reps = 3
 
     ### Larger datasets using LIBLINEAR with edge labels.
     dataset = [["MOLT-4", True, True], ["Yeast", True, True], ["MCF-7", True, True],
-                 ["github_stargazers", False, False],
-                 ["reddit_threads", False, False]]
+               ["github_stargazers", False, False],
+               ["reddit_threads", False, False]]
 
     for d, use_labels, use_edge_labels in dataset:
         dataset = d

### 2020-07-11 tud_benchmark/main_kernel.py
MC.

@@ -17,6 +17,8 @@ def main():
     for dataset, use_labels in dataset:
         classes = dp.get_dataset(dataset)
 
+        print()
+
         # 1-WL kernel, number of iterations in [1:6].
         all_matrices = []
         for i in range(1, 6):

### 2020-07-16 paper/example_gnn.py
MC>

@@ -1,7 +1,6 @@
 import auxiliarymethods.datasets as dp
 from auxiliarymethods.gnn_evaluation import gnn_evaluation
 from gnn_baselines.gnn_architectures import GIN
-from auxiliarymethods.reader import tud_to_networkx
 
 dataset = "PROTEINS"
 use_labels = True
@@ -9,11 +8,11 @@ use_labels = True
 # Download dataset.
 dp.get_dataset(dataset)
 
-# Optimize the number of layers ({1,2,3,4,5}) and
+# Optimize the number of layers ({1,2,3,4,5} and
 # the number of hidden features ({32,64,128}),
 # set the maximum nummber of epochs to 200,
 # batch size to 64,
-# start learning rate to 0.01, and
+# starting learning rate to 0.01, and
 # number of repetitions for 10-CV to 10.
 print(gnn_evaluation(GIN, dataset, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200,
                      batch_size=64, start_lr=0.01, num_repetitions=10, all_std=True))

### 2020-07-16 paper/networkx.py

@@ -1,5 +1,5 @@
 import auxiliarymethods.datasets as dp
-from auxiliarymethods.gnn_evaluation import gnn_evaluation
+from auxiliarymethods.reader import tud_to_networkx
 
 dataset = "PROTEINS"
 

### 2020-07-16 tud_benchmark/kernel_baselines/kernel_baselines.cpp

@@ -63,73 +63,6 @@ MatrixXd compute_wloa_dense(string ds, int num_iterations,  bool use_labels,  bo
     return MatrixXd(gm);
 }
 
-MatrixXd compute_lwl_2_dense(string ds, int num_iterations,  bool use_labels,  bool use_edge_labels,  bool simple) {
-    GraphDatabase gdb = AuxiliaryMethods::read_graph_txt_file(ds);
-    gdb.erase(gdb.begin() + 0);
-
-    GenerateTwo::GenerateTwo wl(gdb);
-    GramMatrix gm;
-    gm = wl.compute_gram_matrix(num_iterations, use_labels, use_edge_labels, "local", simple, true, false);
-
-    return MatrixXd(gm);
-}
-
-MatrixXd compute_lwlp_2_dense(string ds, int num_iterations,  bool use_labels,  bool use_edge_labels,  bool simple) {
-    GraphDatabase gdb = AuxiliaryMethods::read_graph_txt_file(ds);
-    gdb.erase(gdb.begin() + 0);
-
-    GenerateTwo::GenerateTwo wl(gdb);
-    GramMatrix gm;
-    gm = wl.compute_gram_matrix(num_iterations, use_labels, use_edge_labels, "localp", simple, true, false);
-
-    return MatrixXd(gm);
-}
-
-
-MatrixXd compute_lwl_2_wloa_dense(string ds, int num_iterations,  bool use_labels,  bool use_edge_labels, bool simple) {
-    GraphDatabase gdb = AuxiliaryMethods::read_graph_txt_file(ds);
-    gdb.erase(gdb.begin() + 0);
-
-    GenerateTwo::GenerateTwo wl(gdb);
-    GramMatrix gm;
-    gm = wl.compute_gram_matrix(num_iterations, use_labels, use_edge_labels, "local", simple, true, true);
-
-    return MatrixXd(gm);
-}
-
-MatrixXd compute_lwlp_2_wloa_dense(string ds, int num_iterations,  bool use_labels,  bool use_edge_labels,  bool simple) {
-    GraphDatabase gdb = AuxiliaryMethods::read_graph_txt_file(ds);
-    gdb.erase(gdb.begin() + 0);
-
-    GenerateTwo::GenerateTwo wl(gdb);
-    GramMatrix gm;
-    gm = wl.compute_gram_matrix(num_iterations, use_labels, use_edge_labels, "localp", simple, true, true);
-
[…]

### 2020-07-16 tud_benchmark/main_gnn.py

@@ -15,13 +15,13 @@ def main():
         # Download dataset.
         dp.get_dataset(d)
 
-        # GIN, dataset d, layers in [1:5], hidden dimension in {32,64,128}.
+        # GIN, dataset d, layers in [1:6], hidden dimension in {32,64,128}.
         acc, s_1, s_2 = gnn_evaluation(GIN, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200, batch_size=64,
                                        start_lr=0.01, num_repetitions=num_reps, all_std=True)
         print(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
         results.append(d + " " + "GIN " + str(acc) + " " + str(s_1) + " " + str(s_2))
 
-        # GIN with jumping knowledge, dataset d, layers in [1:5], hidden dimension in {32,64,128}.
+        # GIN with jumping knowledge, dataset d, layers in [1:6], hidden dimension in {32,64,128}.
         acc, s_1, s_2 = gnn_evaluation(GINWithJK, d, [1, 2, 3, 4, 5], [32, 64, 128], max_num_epochs=200,
                                        batch_size=64,
                                        start_lr=0.01, num_repetitions=num_reps, all_std=True)
